\subsubsection{Re-incarnation/Re-inclicknilson}\label{re-incarnationre-inclicknilson}

\textbf{\href{nilson-click}{Click~Nilson}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{keynote-3}{\textbf{Keynote: Click
  Nilson \& Closing Words}\\
  Friday, April 21st, 14:00, \emph{VOGELFREI}}
\end{itemize}

\textbf{\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=9084s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=9084s}{https://www.youtube.com/watch?v=FSBtvtxP008\&t=9084s}

\paragraph{Abstract}\label{abstract}

We are sorry to announce to the live coding community that the insidious
Click Nilson has been found alive, floating in a canoe bought from a
life insurance payout off Finland or somesuch fraudulent state. Many of
us thought he was gone for good, but he has returned for evil.

Rumours to the contrary, his obituary included, Click Nilson is then
resolutely still around, though he has stayed hidden these past years,
and may have died more than once. In one unlikely turn of events, Click
Nilson was reincarnated as himself. This was the outcome thought most
ironic by the powers that be, in the light of CN\textquotesingle s
stated desire for change.

In this keynote talk, Click Nilson will appear via video link to
impress, berate, confuse, enlighten, disappoint and recharge the live
coding community, through an intensely boring and overly quiet 59 minute
monologue followed by one minute to ignore your questions. All of that
could change, however.

\subsubsection{Live Coding as (Dis)placement: Artists, Programming and the
Dancing
In-Between}\label{live-coding-as-displacement-artists-programming-and-the-dancing-in-between}

\textbf{\href{sicchio-kate}{Kate~Sicchio}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{keynote-1}{\textbf{Opening \&
  Keynote: Kate Sicchio}\\
  Wednesday, April 19th, 13:45, \emph{VOGELFREI}}
\end{itemize}

\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=15945s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=15945s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=15945s}

\paragraph{Abstract}\label{abstract-1}

Our current technology hype cycle has much to say on the displacement of
human labor. However, live coding can be seen as a methodology for
centrally placing the artist and their process in new media artwork. How
might live coding challenge the displacement of humans and give people
agency in a world of technical systems and algorithms that consistently
make choices for us? Live coding asks us to find humanity in
computational practices and how to highlight the performers. And perhaps
by putting a real-time computational process into a discipline, we may
even find new ways of making through forms of displacement, introducing
new vocabularies and practices, beyond the technical and reflecting the
social, cultural or expressive.

\subsubsection{Thinking Inside the Box: Instant Composition, Folded
Structures and Beyond the
Screen}\label{thinking-inside-the-box-instant-composition-folded-structures-and-beyond-the-screen}

\textbf{\href{baalman-marije}{Marije~Baalman}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{keynote-2}{\textbf{Keynote: Marije
  Baalman}\\
  Thursday, April 20th, 14:00, \emph{VOGELFREI}}
\end{itemize}

\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=10044s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=10044s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=10044s}

\paragraph{Abstract}\label{abstract-2}

Livecoding is an act of rebellion against the fixed idea software as
immutable, impenetrable, but yet advertised as neutral, systems that are
humanity\textquotesingle s future -- it inspires democratisation of the
human/machine entanglement of our current society, by showing that code
is mutable, alive, accessible, and above all an expression of concepts
-- which are personal and political.

Ca. 20 years after the start of the
\href{https://toplap.org/wiki/HistoricalPerformances}{projection era} of
livecoding, perhaps it is time to make up the balance of how the
entanglement between humans and machines within the livecoding community
has evolved.

Marije Baalman will present a keynote presentation on the topic of
human/machine entanglement.

Her past livecoding works,
\emph{\href{https://marijebaalman.eu/projects/code-livecode-live.html}{Code
LiveCode Live}},
\emph{\href{https://marijebaalman.eu/projects/wezen-gewording.html}{Wezen-Gewording}},
\emph{\href{https://marijebaalman.eu/projects/etudes-pour-le-livecoding-a-une-main.html}{Etudes
pour le Livecoding à une Main}}, and
\emph{\href{https://marijebaalman.eu/projects/the-machine-is-learning.html}{the
machine is learning}} all address different aspects of human/machine
entanglement. In her presentation she will come back to topics she
addressed in her paper
\emph{\href{https://iclc.toplap.org/2015/html/72.html}{Embodiment of
Code}} at the first ICLC in 2015, her article ``Interplay between
Composition, Instrument Design and Performance'' (2016) and her book
\emph{\href{https://composinginteractions.art/}{``Composing Interactions
-- an Artist's Guide to Building Expressive Interactive Systems''}}
(2022).

\begin{itemize}
\tightlist
\item
  \url{https://marijebaalman.eu}
\item
  \url{https://composinginteractions.art}
\end{itemize}
