\subsubsection{Addressing Accessibility for Blind and Visually Impaired Live Coders}\label{addressing-accessibility-for-blind-and-visually-impaired-live-coders}

\textbf{\href{/2023/catalogue/person/kaney-matthew.html}{Matthew~Kaney},
\href{/2023/catalogue/person/payne-william-christopher.html}{William~Christopher~Payne},
\href{/2023/catalogue/person/hurst-amy.html}{Amy~Hurst}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-3.html}{\textbf{Paper
  Session 3}\\
  Wednesday, April 19th, 15:15, \emph{VOGELFREI}}
\end{itemize}

\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=26344s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=26344s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=26344s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843872}{\textbf{https://doi.org/10.5281/zenodo.7843872}}

\paragraph{Abstract}\label{abstract}

Live coding environments that use text input and audio output have the
potential to be accessible and expressive for Blind and Visually
Impaired (BVI) people. However, little is known about their
compatibility with the assistive technologies BVI people use, including
screen readers and braille displays, or the experiences of BVI live
coders. To address this gap, we formed FiLOrk, a live coding ensemble
made up of five BVI high school students at the Filomen M.
D\textquotesingle Agostino Greenberg Music School (aka the
Fil\textquotesingle). We introduce the goals and open questions guiding
FiLOrk and report initial findings from our experiences designing a
learning environment and building a custom, collaborative text editor,
text.management.

\subsubsection{Asymmetric Performance in Virtual Reality and
Code}\label{asymmetric-performance-in-virtual-reality-and-code}

\textbf{\href{/2023/catalogue/person/geier-leonard.html}{Leonard~Geier},
\href{/2023/catalogue/person/methfessel-paul.html}{Paul~Methfessel},
\href{/2023/catalogue/person/beckmann-tom.html}{Tom~Beckmann},
\href{/2023/catalogue/person/hirschfeld-robert.html}{Robert~Hirschfeld}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-4.html}{\textbf{Paper
  Session 4}\\
  Thursday, April 19th, 10:00, \emph{VOGELFREI}}
\end{itemize}

\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=65s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=65s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=65s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843896}{\textbf{https://doi.org/10.5281/zenodo.7843896}}

\paragraph{Abstract}\label{abstract-1}

Virtual reality enables a rich 3D user experience where immediate
feedback can yield lively interactions. For live coding, however, the
rigid, text-based nature of source code is still a serious impediment to
achieving such experience, as text input in virtual reality is
significantly slower than on a physical keyboard. We present an
asymmetric live-coding environment, in which a performance can benefit
from both the fluid and flexible direct manipulation capabilities of
virtual reality and the expressive power of text-based code.Here, one
performer interacts with parameters and code blocks of the system using
their hands in virtual reality, but is ultimately constrained by the
code defined by another performer immersed in a dedicate programming and
runtime environment with full access to the source of the system. We
present a proof-of-concept implementation of such a system and describe
future directions for its development.


\subsubsection{Be Brief: Convergences and Possibilities of Live Coding And
sctweeting}\label{be-brief-convergences-and-possibilities-of-live-coding-and-sctweeting}

\textbf{\href{/2023/catalogue/person/m-martins-fellipe.html}{Fellipe~M.~Martins},
\href{/2023/catalogue/person/padovani-jose-henrique.html}{José~Henrique~Padovani}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-2.html}{\textbf{Paper
  Session 2}\\
  Wednesday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=9752s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=9752s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=9752s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843864}{\textbf{https://doi.org/10.5281/zenodo.7843864}}

\paragraph{Abstract}\label{abstract-2}

With the advent of real-time computer music programming languages,
specialized practices have arisen. Live coding (LC) and SCTweeting (SCT)
are significant examples of creative constraint-coding approaches to
computer music. The former consists of improvised live-electronic music
in which performers project their coding screen. The latter is the
practice of code golfing for creating (and sharing on social media)
140-character codes that generate complex sounds. In this paper we seek
to approximate these two, drawing a comparative conceptualization and
outlining possible artistic and contextual bonds between them. We
analyze how both scenes, being new forms of artistic practices, propose
radical and non-traditional approaches to coding. For that, LC and SCT
are associated with the concepts and theoretical elaborations of
cybernetics and mechanology, such as \emph{feedback loops} as well as
the \emph{isodynamism} between technical behavior and human thought.
Thereupon, we discuss how constraints play an important role in LC and
SCT to develop ideas and achieve idiosyncratic artistic results.
Finally, we outline some possible interweaving and didactic potential
that have been latent in both practices.


\subsubsection{Floating Gold: an International Collaboration through
Estuary.}\label{floating-gold-an-international-collaboration-through-estuary.}

\textbf{\href{/2023/catalogue/person/candra-rini-peni.html}{Peni~Candra~Rini},
\href{/2023/catalogue/person/purnama-aji-rangga.html}{Rangga~Purnama~Aji},
\href{/2023/catalogue/person/sewell-sen.html}{Sen~Sewell},
\href{/2023/catalogue/person/strohschein-heather.html}{Heather~Strohschein},
\href{/2023/catalogue/person/van-der-walt-j-simon.html}{J.~Simon~van~der~Walt},
\href{/2023/catalogue/person/whitmer-bill.html}{Bill~Whitmer}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-2.html}{\textbf{Paper
  Session 2}\\
  Wednesday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=7236s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=7236s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=7236s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843575}{\textbf{https://doi.org/10.5281/zenodo.7843575}}

\paragraph{Abstract}\label{abstract-3}

Between December 2020 and November 2022 the Glasgow-based community
group Gamelan Naga Mas worked remotely with two Indonesian musicians,
Peni Candra Rini and Rangga Purnama Aji. This musical collaboration was
made possible by the Estuary platform, which allowed for real-time
livecoded improvisations between locations in Scotland, Indonesia, and
the USA. In this paper we discuss and reflect upon the technical,
musical, and human factors that have made this project a success and
indicate some directions for future exploration.


\subsubsection{Genny: Designing and Exploring a Live Coding Interface for
Generative
Models}\label{genny-designing-and-exploring-a-live-coding-interface-for-generative-models}

\textbf{\href{/2023/catalogue/person/shimizu-junichi.html}{Junichi~Shimizu},
\href{/2023/catalogue/person/fiebrink-rebecca.html}{Rebecca~Fiebrink}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-3.html}{\textbf{Paper
  Session 3}\\
  Wednesday, April 19th, 15:15, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=24240s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=24240s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=24240s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843500}{\textbf{https://doi.org/10.5281/zenodo.7843500}}

\paragraph{Abstract}\label{abstract-4}

We present Genny, a live coding interface for interacting with
generative models. By implementing a streamlined generative model API
within a Web-based live coding environment, we explore possibilities for
how generative models can support live coding. We describe the
implementation of our interface components and the backend system for
working with generative models, show several design patterns with
template code, and describe use of a practical generation method for
live coding performance. The system currently enables the generation of
two-bar rhythm patterns using lightweight models that support
near-instantaneous inference, which are able to suggest and display
alternative rhythm patterns based on live coders\textquotesingle{} own
inputs. Finally, we discuss reflections on this implementation approach,
its current limitations, and further possibilities.

\subsubsection{LambDAW: Towards a Generative Audio
Workstation}\label{lambdaw-towards-a-generative-audio-workstation}

\textbf{\href{/2023/catalogue/person/clester-ian.html}{Ian~Clester},
\href{/2023/catalogue/person/freeman-jason.html}{Jason~Freeman}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-4.html}{\textbf{Paper
  Session 4}\\
  Thursday, April 19th, 10:00, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=1270s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=1270s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=1270s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842002}{\textbf{https://doi.org/10.5281/zenodo.7842002}}

\paragraph{Abstract}\label{abstract-5}

We present LambDAW, a novel system for integrating computation and
composition that brings code directly into the digital audio workstation
(DAW). It allows the composer to freely mix static and dynamic materials
by embedding short expressions of code in the DAW timeline that generate
audio and MIDI on demand. LambDAW moves code out of the text editor and
computation out of the effects chain, bringing both into the timeline
where they can refer to and transform other items. We propose that this
move makes code more tangible and enables the composer to easily bring
generativity into their existing practices. Additionally, we discuss
LambDAW\textquotesingle s affordances and implications for live coding.
LambDAW takes the form of an open-source REAPER extension that executes
Python code embedded in projects, enabling the user to benefit from both
the existing REAPER and Python ecosystems.


\subsubsection{LivecoderA Community
Report}\label{livecodera-community-report}

\textbf{\href{/2023/catalogue/person/champlin-alicia.html}{Alicia~Champlin},
\href{/2023/catalogue/person/chicau-joana.html}{Joana~Chicau},
\href{/2023/catalogue/person/corfiel-miki.html}{Miki~Corfiel},
\href{/2023/catalogue/person/knotts-shelly.html}{Shelly~Knotts},
\href{/2023/catalogue/person/marie-mynah.html}{Mynah~Marie},
\href{/2023/catalogue/person/saladino-iris.html}{Iris~Saladino},
\href{/2023/catalogue/person/xambo-anna.html}{Anna~Xambó}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-2.html}{\textbf{Community
  Report Session 2}\\
  Friday, April 21st, 11:15, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=5493s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=5493s}{https://www.youtube.com/watch?v=FSBtvtxP008\&t=5493s}

Publication:
\href{https://doi.org/10.5281/zenodo.7845610}{\textbf{https://doi.org/10.5281/zenodo.7845610}}

\paragraph{Abstract}\label{abstract-6}

In March of 2022, LivecoderA, a new live coding community came into
being, coalescing around the need to recognize a specific cohort of live
coders who identify as women. The group is inherently feminist and
intersectional, and its creation was motivated by many desires. Among
them: solidarity and visibility, to be counted as sisters, and to
reflect to each other the strength of our numbers. A manifesto and
several events have since been produced, and the community is active
online while also making more in-person connections whenever possible
through the coordination of gigs, residencies and meetups. At the time
of publishing, the community connects through Telegram and Discord, with
channels consisting of 48 and 27 members respectively.

\begin{itemize}
\tightlist
\item
  LivecoderA manifesto: \url{https://livecodera.glitch.me/}
\item
  Invitation to join: \url{https://t.me/livecodera}
\end{itemize}


\subsubsection{Live Coding and Education. A Practical
Experience.}\label{live-coding-and-education.-a-practical-experience.}

\textbf{\href{/2023/catalogue/person/corvi-francesco.html}{Francesco~Corvi},
\href{/2023/catalogue/person/mori-giovanni.html}{Giovanni~Mori},
\href{/2023/catalogue/person/nulli-giovanni.html}{Giovanni~Nulli}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-5.html}{\textbf{Paper
  Session 5}\\
  Thursday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=4952s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=4952s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=4952s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843819}{\textbf{https://doi.org/10.5281/zenodo.7843819}}

\paragraph{Abstract}\label{abstract-7}

This paper presents an explorative research on the introduction of live
coding into the Italian music curriculum in middle school with the aim
to offer teachers a multidisciplinary didactic tool that can enhance the
learning experience of students. The research focuses on the challenges
that music teachers face when introducing live coding into their
curricular activity and the type of training that can prepare them for
it. The paper covers three main points: the training of teachers, the
pedagogical strategies employed in the classrooms, and an overview of
the results of the first year of experimentation. Overall, the paper
aims to offer insight into the potential benefits and challenges of
using live coding as a teaching tool in music education and highlights
its potential for multidisciplinary applications, while also showing
possible paths for future work and improvement.


\subsubsection{MosAIck: Staging Contemporary AI Performance - Reflections
on Connecting Live Coding, e-Textile and
Movement}\label{mosaick-staging-contemporary-ai-performance---reflections-on-connecting-live-coding-e-textile-and-movement}

\textbf{\href{/2023/catalogue/person/wilson-elizabeth.html}{Elizabeth~Wilson},
\href{/2023/catalogue/person/schubert-deva.html}{Deva~Schubert},
\href{/2023/catalogue/person/satomi-mika.html}{Mika~Satomi},
\href{/2023/catalogue/person/mclean-alex.html}{Alex~McLean},
\href{/2023/catalogue/person/felipe-amaya-gonzalez-juan.html}{Juan~Felipe~Amaya~Gonzalez}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-2.html}{\textbf{Paper
  Session 2}\\
  Wednesday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=8562s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=8562s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=8562s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843540}{\textbf{https://doi.org/10.5281/zenodo.7843540}}

\paragraph{Abstract}\label{abstract-8}

This paper introduces our collective work ``Patterns in Between
Intelligences\textquotesingle\textquotesingle, a performance piece that
builds an artistic practice between live coding sounds and coding
through dance, mediated and shaped through e-textile sensors. This
creates a networked system of which both live coded processes and human
bodies are part. The paper describes in detail the implementations of
technology used in the prototype performance performed at No Bounds
Festival in Sheffield UK, October 2022, as well as discussions and
concerns the team had related to the use of AI technology on stage. The
paper concludes with a narrative reflection on the Sheffield
performance, and reflections on it.

\subsubsection{NL\_CL Community Report}\label{nl_cl-community-report}

\textbf{\href{/2023/catalogue/person/hoogland-timo.html}{Timo~Hoogland},
\href{/2023/catalogue/person/chicau-joana.html}{Joana~Chicau},
\href{/2023/catalogue/person/reus-jonathan.html}{Jonathan~Reus},
\href{/2023/catalogue/person/andrade-rafaele.html}{Rafaele~Andrade},
\href{/2023/catalogue/person/corvi-francesco.html}{Francesco~Corvi},
\href{/2023/catalogue/person/van-sluijs-fabian.html}{Fabian~van~Sluijs},
\href{/2023/catalogue/person/noriega-alcaraz-felipe-ignacio.html}{Felipe~Ignacio~Noriega~Alcaraz},
\href{/2023/catalogue/person/van-de-zandschulp-klasien.html}{Klasien~van~de~Zandschulp},
\href{/2023/catalogue/person/freeke-saskia.html}{Saskia~Freeke},
\href{/2023/catalogue/person/verhage-sabrina.html}{Sabrina~Verhage},
\href{/2023/catalogue/person/paz-ivan.html}{Iván~Paz}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-1.html}{\textbf{Community
  Report Session 1}\\
  Friday, April 21st, 10:00, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=2683s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=2683s}{https://www.youtube.com/watch?v=FSBtvtxP008\&t=2683s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842288}{\textbf{https://doi.org/10.5281/zenodo.7842288}}

\paragraph{Abstract}\label{abstract-9}

The Netherlands Coding Live a.k.a. NL\_CL is a "pop-up" phygital space
for engaging with live coding through practice, experimentation,
openness, discussions and performance. Series of live coding sessions,
discussions, workshops and more have been organized by live coders based
in The Netherlands and hosted in various cities across the country. Many
members of NL\_CL are also employed or in close contact with other
platforms, foundations or institutes such as the instrument inventors
initiative (iii) in The Hague, Creative Coding Utrecht (CCU), Varia in
Rotterdam, Creative Coding Amsterdam (CCA), The Institute of Sonology in
The Hague, The HKU University of the Arts Utrecht and the Conservatory
of Amsterdam (CvA). By applying for subsidy at different funds like
Creative Industries Fund NL (SCI) and Fund Performing Arts (FPK) NL\_CL
has been able to organize many events such as concerts and workshops in
collaboration or via these parties. NL\_CL is an open community where
everyone with an interest in coding is welcome to join. The community
has a diverse practice of disciplines in which live coding is applied.
These disciplines range from programming music (in the broadest
definition possible) and visuals to working with choreography and
embodiment or building, augmenting and designing acoustic and physical
instruments. Much of the tools and research by the community are also
published and shared. Furthermore the community is quite diverse in
nationalities with members from for example Brazil, Argentina, Slovenia,
USA, Mexico, Portugal, Italy and of course The Netherlands.


\subsubsection{Reproducible Musical Analysis of Live Coding Performances
Using Information Retrieval: A Case Study on the Algorave 10th
Anniversary}\label{reproducible-musical-analysis-of-live-coding-performances-using-information-retrieval-a-case-study-on-the-algorave-10th-anniversary}

\textbf{\href{/2023/catalogue/person/diapoulis-georgios.html}{Georgios~Diapoulis},
\href{/2023/catalogue/person/carle-martin.html}{Martin~Carlé}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-3.html}{\textbf{Paper
  Session 3}\\
  Wednesday, April 19th, 15:15, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=20919s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=20919s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=20919s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843813}{\textbf{https://doi.org/10.5281/zenodo.7843813}}

\paragraph{Abstract}\label{abstract-10}

We present a reproducible music information retrieval (MIR) study on 133
performances from the 10th anniversary of Algorave. Our aim in this
paper is to provide a reproducible framework for computational analysis
of musical performances. Here, we present a tool for analysing
acoustical characteristics and for visualizing the musical structure
from performances of one algorave event. Our musical analysis of the
live coding performances highlights the musical diversity within the
live coding community to a broader scientific audience. At the same
time, we expect that the algoravers will gain insights on their own
musical practices through the computational analysis of the musical
structure of their performances. In concerning ourselves with
reproducibility, our intention is to motivate more researchers to
analyse musical practices of other under-represented music communities.
As a basic tool for reproducibility we construct a pipeline for
analysing performances using Python within a Jupyter notebook. To make
this reproducible on different computers we wrapped the whole workflow
setup into a docker image. We represent the results of our analysis as a
series of plots of different kinds. These plots present both overviews
of the entire repertory in compact form, and comparisons of individual
pieces in more detail. In learning one can use such visualization as a
means for raising awareness on one\textquotesingle s evolution of the
musical outcome. In performance this visualization can be developed to a
real-time and possibly an interactive tool which informs the coder about
the musical outcome of a live set on-the-fly. Finally, we reflect on how
and to what extent such MIR studies can provide valuable insights in
live coding performance practices, while also considering the
limitations faced when dealing with such large parameter spaces in human
machine musicianship.


\subsubsection{Sardine: A Modular Python Live Coding
Environment}\label{sardine-a-modular-python-live-coding-environment}

\textbf{\href{/2023/catalogue/person/forment-raphael-maurice.html}{Raphaël~Maurice~Forment},
\href{/2023/catalogue/person/armitage-jack.html}{Jack~Armitage}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-1.html}{\textbf{Welcome \&
  Paper Session 1}\\
  Wednesday, April 19th, 09:45, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=1548s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=1548s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=1548s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843817}{\textbf{https://doi.org/10.5281/zenodo.7843817}}

\paragraph{Abstract}\label{abstract-11}

\textbf{Sardine} is a live coding environment and library for Python
3.10+ focusing on the modularity and extensibility of several base
components (clocks, parsers, handlers). \textbf{Sardine} has been
designed to be easily integrated with existing live coding environments
as both a tool for experimentation, and a demonstration of various live
coding techniques: temporal recursion, patterning, integration in
various hardware and software setups. Although the tool is still in
active early development, it has already been used in multiple public
performances and algoraves, partly enabled by its support for MIDI
IN/Out, OSC IN/Out and \emph{SuperCollider/SuperDirt} one-way
communication through OSC.This paper is dedicated to the introduction of
the \textbf{Sardine} system, and the explanation of the main guidelines
currently followed by contributors to the project. It will also present
the preliminary results of our work through practical realisations that
served as experimental validation during the early stages of
development.


\subsubsection{Strudel: Live Coding Patterns on the
Web}\label{strudel-live-coding-patterns-on-the-web}

\textbf{\href{/2023/catalogue/person/roos-felix.html}{Felix~Roos},
\href{/2023/catalogue/person/mclean-alex.html}{Alex~McLean}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-1.html}{\textbf{Welcome \&
  Paper Session 1}\\
  Wednesday, April 19th, 09:45, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=2805s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=2805s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=2805s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842142}{\textbf{https://doi.org/10.5281/zenodo.7842142}}

\paragraph{Abstract}\label{abstract-12}

This paper introduces Strudel, which faithfully ports the TidalCycles
approach to live coding algorithmic patterns to native JavaScript and
the web. We begin by giving a little background of the first year of
development, before sharing some detail about its implementation and
examples of use. We go on to outline the wide range of synthesis and
other outputs available in Strudel, including WebAudio, MIDI, OSC (for
SuperDirt), WebSerial and CSound, and introduce
Strudel\textquotesingle s REPL live editor, including its built-in
visualisations. We then compare Strudel with Tidal, the trade-offs
involved between JavaScript and Haskell, and the unique capabilities
offered by Strudel for aligning patterns, before concluding with some
thoughts about the future.


\subsubsection{The Meaning of Live: From Art Without Audience to Programs
Without
Users}\label{the-meaning-of-live-from-art-without-audience-to-programs-without-users}

\textbf{\href{/2023/catalogue/person/mclean-alex.html}{Alex~McLean},
\href{/2023/catalogue/person/rohrhuber-julian.html}{Julian~Rohrhuber},
\href{/2023/catalogue/person/wieser-renate.html}{Renate~Wieser}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-5.html}{\textbf{Paper
  Session 5}\\
  Thursday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=7726s}{Live Stream Recording (YouTube)}} -- \\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=7726s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=7726s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843567}{\textbf{https://doi.org/10.5281/zenodo.7843567}}

\paragraph{Abstract}\label{abstract-13}

The concept of an \textquotesingle art without
audience\textquotesingle{} has informed live coding since its
beginnings. Live Coding concentrates on collective work and questions
the division between producers and consumers. This understanding of art
has enabled a parallel strategy in the understanding of programming:
just as an audience is not necessary for art, a user isn't necessary for
programming. In the same sense as we question the separation between
developer and user, we question the juxtaposition of artist and
audience. This gives us occasion to recall some aspects of live coding
which we have always found central to this practice: the displacement of
the relation between programmers and programs, and the emancipatory
potential of public thought.


\subsubsection{The Physical and Cultural Infrastructure Supporting
LiveCode.NYC: A Community
Report}\label{the-physical-and-cultural-infrastructure-supporting-livecode.nyc-a-community-report}

\textbf{\href{/2023/catalogue/person/srinivasan-sumanth.html}{Sumanth~Srinivasan}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-2.html}{\textbf{Community
  Report Session 2}\\
  Friday, April 21st, 11:15, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=4102s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=4102s}{https://www.youtube.com/watch?v=FSBtvtxP008\&t=4102s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842304}{\textbf{https://doi.org/10.5281/zenodo.7842304}}

\paragraph{Abstract}\label{abstract-14}

LivecodeNYC is New York City\textquotesingle s community of nerds and
artists writing software on stage to make music, visuals, games and
other live art in front of audiences. This community report offers a
look into the various factors that make up the ground reality of running
a live coding community in New York City, and how it influences our ways
of working, successes and challenges.


\subsubsection{TOPLAP Barcelona Community Report
2023}\label{toplap-barcelona-community-report-2023}

\textbf{\href{/2023/catalogue/person/fraser-glen.html}{Glen~Fraser},
\href{/2023/catalogue/person/paz-ivan.html}{Iván~Paz},
\href{/2023/catalogue/person/bautista-rodriguez-lina.html}{Lina~Bautista~Rodríguez},
\href{/2023/catalogue/person/reppel-niklas.html}{Niklas~Reppel},
\href{/2023/catalogue/person/pibernat-trias-roger.html}{Roger~Pibernat~Trias},
\href{/2023/catalogue/person/casamajo-ramon.html}{Ramon~Casamajó~(QBRNTHSS)}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-1.html}{\textbf{Community
  Report Session 1}\\
  Friday, April 21st, 10:00, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=2019s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=FSBtvtxP008&t=2019s}{https://www.youtube.com/watch?v=FSBtvtxP008\&t=2019s}

Publication:
\href{https://doi.org/10.5281/zenodo.7843519}{\textbf{https://doi.org/10.5281/zenodo.7843519}}

\paragraph{Abstract}\label{abstract-15}

Barcelona has developed an active community of live coders. This report
traces back the history and development of the TOPLAP Barcelona node,
from its predecessors and roots, through its founding as a collective,
to the present day. In addition, it presents its ongoing activities and
how they shape the character of the community as we can see it today.


\subsubsection{Towards Another Transdiscipline: Art, (Techno)Science and
Emancipation as Promise and Provocation for Live
Coding}\label{towards-another-transdiscipline-art-technoscience-and-emancipation-as-promise-and-provocation-for-live-coding}

\textbf{\href{/2023/catalogue/person/franco-briones-alejandro.html}{Alejandro~Franco~Briones}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-5.html}{\textbf{Paper
  Session 5}\\
  Thursday, April 19th, 11:30, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=6404s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=6404s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=6404s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842097}{\textbf{https://doi.org/10.5281/zenodo.7842097}}

\paragraph{Abstract}\label{abstract-16}

In this text I deploy Nancy Fraser\textquotesingle s theory of the
\textquotesingle triple movement\textquotesingle{} to analyse and
re-imagine the node of techno-scientific art practice, paying attention
to the Mexican art context and the imagined (trans-national) community
of live coding. From Fraser\textquotesingle s ideas, I provide an
analysis of Actor-Network Theory and a general comment on technofeminism
as a set of theoretical frameworks insufficient for integrating
emancipation properly into artistic and scientific practices.


\subsubsection{uSEQ: A LISPy Modular Sequencer for Eurorack with a
Livecodable
Microcontroller}\label{useq-a-lispy-modular-sequencer-for-eurorack-with-a-livecodable-microcontroller}

\textbf{\href{/2023/catalogue/person/kyriakoudis-dimitris.html}{Dimitris~Kyriakoudis},
\href{/2023/catalogue/person/kiefer-chris.html}{Chris~Kiefer}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-4.html}{\textbf{Paper
  Session 4}\\
  Thursday, April 19th, 10:00, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=2548s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=_Z71KQtWpMk&t=2548s}{https://www.youtube.com/watch?v=\_Z71KQtWpMk\&t=2548s}
 
Publication:
\href{https://doi.org/10.5281/zenodo.7843874}{\textbf{https://doi.org/10.5281/zenodo.7843874}}

\paragraph{Abstract}\label{abstract-17}

\emph{uSEQ} is a new livecodable sequencer module for the Eurorack
modular synthesiser ecosystem. It draws inspiration from both the
practices of live coding and hardware modular synthesis, aiming to
examine and combine their respective ergodynamic strengths and
weaknesses into a new, hybrid practice. It embeds \emph{uLisp}, a tiny
interpreter for the general-purpose language with a small-enough
footprint to run even on inexpensive microcontrollers. The
interpreter\textquotesingle s REPL has been modified for the purposes of
live coding, and its reader has been "hacked" to the limited resources
of the sub-£5 microcontroller at the heart of the module. On top of the
Lisp general-purpose language, a minimal DSL layer has been designed to
take full advantage of the linguistic flexibility of the underlying
language. Simultaneously, the semantics of this DSL tries to stay close
to one of the central philosophies of modular synthesis: everything is a
signal, and sequences are no exception. Its open-source firmware and
design files (PCB and 3D-printable faceplate), with an approximate total
cost of £20 in parts, \emph{uSEQ} is highly DIY-friendly can be built as
a weekend project. It provides multiple input and output interfaces to
the rest of the Eurorack ecosystem, and can be controlled from a mobile
phone, tablet, or any (micro)computer with a USB port. The prototyping
of this module is a practical exploration into the ways in which the
ergonomic and ergodynamic tensions between the practices of livecoding
and modular synthesis can be successfully addressed when bridging the
two worlds, following a practice-led, research-through-design approach.


\subsubsection{Ziffers: Numbered Notation for Algorithmic
Composition}\label{ziffers-numbered-notation-for-algorithmic-composition}

\textbf{\href{/2023/catalogue/person/alonen-miika.html}{Miika~Alonen},
\href{/2023/catalogue/person/forment-raphael-maurice.html}{Raphaël~Maurice~Forment}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-3.html}{\textbf{Paper
  Session 3}\\
  Wednesday, April 19th, 15:15, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=22468s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=22468s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=22468s}

Publication:
\href{https://doi.org/10.5281/zenodo.7841945}{\textbf{https://doi.org/10.5281/zenodo.7841945}}

\paragraph{Abstract}\label{abstract-18}

Ziffers is an algorithmic number based musical notation for live coding.
It offers concise syntax to support composition and improvisation with
complex melodies and rhythms. Ziffers is the result of experiments in
unifying several types of musical notation centred around the use of
symbols and numbers. It is inspired by the older numbered musical
notations (\emph{Ziffersystem}, \emph{Jianpu}), contemporary music
theory (pitch-class sets, post-tonal music analysis, serialism) and
shorthand notations used in live-coding. Ziffers aims for a balance
between fixed media music notation and generative notations for live
coding performance. In this article, we propose an implementation
agnostic numbered notation for algorithmic composition and live coding.
As a proof of concept, this article will also present a live-coding
framework for Ziffers notation and an export plugin for a general
purpose scorewriter. In doing so, we hope to highlight the versatility
of our approach in using unified syntax for different contexts of
execution and interpretation.

\subsubsection{Živa: Easy Live Coding With
SuperCollider}\label{ux17eiva-easy-live-coding-with-supercollider}

\textbf{\href{/2023/catalogue/person/pibernat-trias-roger.html}{Roger~Pibernat~Trias}}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/paper-session-1.html}{\textbf{Welcome \&
  Paper Session 1}\\
  Wednesday, April 19th, 09:45, \emph{VOGELFREI}}
\end{itemize}


\textbf{\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=4019s}{Live Stream Recording (YouTube)}} --\\
\href{https://www.youtube.com/watch?v=ZzDSW08IAdU&t=4019s}{https://www.youtube.com/watch?v=ZzDSW08IAdU\&t=4019s}

Publication:
\href{https://doi.org/10.5281/zenodo.7842215}{\textbf{https://doi.org/10.5281/zenodo.7842215}}

\paragraph{Abstract}\label{abstract-19}

Živa is a quark aimed to simplify the live coding experience in
SuperCollider, both to quickly set up the environment and to code in a
sparse and clear syntax.

This paper describes the reasons that led the author to develop it and
his procedures in doing so. The paper introduces the problems
encountered when using other languages, and the solutions found in
SuperCollider to solve them. This is not a research paper, but a report
of the motivation, proceedings and achieved results of the
developer\textquotesingle s experience in creating this subset of tools
for SuperCollider.
