
\subsection{Iván~Abreu}\label{ivuxe1n-abreu}

Affiliation: \textbf{Toplap Mexico}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/live-cinema-coding-with-tidal-cycles-processing-and-unreal.html}{Live
      Cinema Coding with Tidal Cycles, Processing and Unreal Engine
      (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/performance/autoconstruccion.html}{AUTO\{\}Construcción
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography}

\emph{Artist, Programmer, Creative Technologist}

He explores the veracity and instrumental capacity of science and
technology in art contexts, and the possible poetic and/or political
value of the findings that emerge from these crossings, as a consequence
through processes like visualization, interaction design, industrial
design , software and web development, engineering and electronics,
expanding the possibilities of digital media, photography, sound art,
video, sculpture, and architectural and urban installation.

His work is included in public and private collections as FEMSA, CINTAS
Foundation Museo Extremeño e Iberoamericano de Arte Contemporáneo. He
has received grants like the Prix Ars Electronica (Linz, Austria); the
CINTAS Foundation Award in Visual Arts, the National System of Art
Creators of FONCA (2012--2014), 2011--2012 and 2021-2024.

\subsection{Miika~Alonen}\label{miika-alonen}

Affiliation: \textbf{Aalto University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/ziffers-numbered-notation-for-algorithmic-composition.html}{Ziffers:
      Numbered Notation for Algorithmic Composition (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-1}

Miika Alonen is a senior software architecture consultant from Finland
and a part-time doctoral student in the Computer Science Department of
Aalto University. He is passionate about information technology,
programming and art.

His main research field is linked data and semantic interoperability,
but for the past few years live coding has been his main research
interest and a hobby to escape from reality. He often finds himself lost
in the beauty and complexity of music and mathematics and enjoys
exploring and simplifying these concepts in his work and research.

Outside of his work and studies, Miika enjoys spending time with his
family and taking long walks with his dog. He finds joy at the little
things, such as the beauty and sounds of the nature, the symmetries,
patterns and chaos, as well as the urban noises of the Helsinki city.

\subsection{Florencia~Alonso~(Flor~de~Fuego)}\label{florencia-alonso-flor-de-fuego}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/code-must-go-on.html}{Code
      must go on! (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-2}

Florencia Alonso (a.k.a Flor de Fuego) is a digital-craft artist that
mainly works with programming and live coding in order to create
performative experiences. Her research rounds concepts like the body,
space, code and chaos. She has taken part in several international and
local festivals in collaboration with some other artists as well as
individually. She graduated as a teacher and bachelor in Arts at
National University of La Plata, Argentina. Education is a fundamental
part in her production. She has taken part in several festivals like
MUTEK Montreal/Spain/Argentina, Node Forum Digital Arts, Die Digitale
Düsseldorf, ICFP Ljubljana, Digital Art Zürich. She is also an alumni
from the Akademie für Theater und Digitalität from Dortmund Theater.
Florencia also collaborates with live coding communities like Hydra, a
live coding browser software developed by Olivia Jack.


\subsection{Riccardo~Ancona}\label{riccardo-ancona}

Affiliation: \textbf{Institute of Sonology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/commuta-a-cross-adaptive-laptop-ensemble.html}{Commuta:
      A Cross Adaptive Laptop Ensemble (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-3}

Riccardo Ancona is an improviser, composer, creative coder, and music
writer based in the Netherlands. He is involved in a set of practices
such as live coding, experimental theater, algorithmic improvisation,
and critical writing. He graduated at CREA (Research Centre for
Audiovisual Processing, Frosinone, Italy) with a thesis on the creative
potentialities of live coding, and he is currently completing a research
master at the Institute of Sonology of Den Haag, exploring the
perception of sonic materialities in algorithmic performance. He works
as a private teacher of music programming and he is an active
independent researcher in the field of history, divulgation, and
pedagogy of electroacoustic music.


\subsection{Rafaele~Andrade}\label{rafaele-andrade}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-4}


\subsection{Jack~Armitage}\label{jack-armitage}

Affiliation: \textbf{Intelligent Instruments Lab, Iceland University of
  the Arts}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/sardine-a-modular-python-live-coding-environment.html}{Sardine:
      A Modular Python Live Coding Environment (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-5}

Jack Armitage is a postdoctoral research fellow at the Intelligent
Instruments Lab. He has a doctorate in Media and Arts Technologies from
Queen Mary University of London, where he studied in Prof. Andrew
McPherson\textquotesingle s Augmented Instruments Lab. During my PhD he
was a Visiting Scholar at Georgia Tech under Prof. Jason Freeman. Before
then, he was a Research Engineer at ROLI after graduating with a BSc in
Music, Multimedia \& Electronics from the University of Leeds. His
research interests include embodied interaction, craft practice and
design cognition. He also produces, performs and live codes music as Lil
Data, as part of the PC Music record label.


\subsection{Marije~Baalman}\label{marije-baalman}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/keynote/keynote-marije-baalman.html}{Thinking
      Inside the Box: Instant Composition, Folded Structures and Beyond the
      Screen (Keynote)}}
\end{itemize}

\paragraph{Biography}\label{biography-6}

Marije Baalman is an artist and researcher/developer working in the
field of interactive sound and light art, based in Amsterdam. She makes
music and music-theatre performances, worked with dancers and has made
several installations.

Topics that she addresses with her work are the nature of interaction
between and entanglement of humans and technology, the influence of
algorithms on society and the human experience, and environmental
change.

She uses tools such as physical computing (performance interfaces and/or
installations), livecoding (both as a skill, as well as a performance
interface), digital and analog sound processing, and improvisation. In
her work with light she uses methods from sound composition and
synthesis. To realise her works she mostly uses open source technology
(software and hardware) and she is an active contributor to the open
source community.

Marije is a contributor to ``The SuperCollider Book'' (MIT Press, 2011)
and in 2022 she published a book titled:
\href{https://composinginteractions.art/}{``Composing Interactions - An
  Artist's Guide to Building Expressive Interactive Systems''} with V2\_
in Rotterdam.


\subsection{Sojung~Bahng~(방소정)}\label{sojung-bahng-uxbc29uxc18cuxc815}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/we-all-begin-in-abstraction.html}{We
      All Begin in Abstraction (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-7}

Sojung Bahng (방소정) is an award-winning multidisciplinary artist,
filmmaker and researcher. She is an Assistant Professor in Media and
Performance Production at Queen's University in Canada. Since 2015, She
has been running and directing RE-NOMAD (formerly Artengine8), a
multidisciplinary research and art organisation mainly based in South
Korea. Sojung holds a PhD from SensiLab at Monash University, Australia,
and her doctoral thesis won the 2020 Mollie Holman award for the best
thesis of the year. Sojung explores cinematic media via digital
technologies to reflect aesthetic and narrative experiences in cultural
and philosophical contexts. Her works have been recognised at
prestigious festivals and symposiums worldwide. Her interactive VR
project Sleeping Eyes won the award of excellence in experience design
at the Festival of International Virtual \& Augmented Reality Stories.
Sojung's experimentations into expanded cinema, performance and digital
storytelling were shown and presented at many international venues and
academic conferences.


\subsection{Lina~Bautista~Rodríguez}\label{lina-bautista-rodruxedguez}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Performance
      Chair (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/crash-landing.html}{CRash
      Landing (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-8}

Lina Bautista aka Linalab is a musician from Bogotá, Colombia that lives
and works in Barcelona. She holds a degree in music composition, and
master degrees in Musical Composition and New Technologies and in Design
of Interactive Musical Systems and Sound Art. With her musical project
Linalab, she has produced several albums and performed on stages around
the world. She is a founding member of Toplap Barcelona. Also, she is
the former artistic director of the European project "on-the-fly",
focused on live coding. Currently, she works with the record labels
Synth Vicious and Aloud Music and teaches in several institutions in
Barcelona, including the master's degree in Sound Art at the UB and the
Sound Workshop of Fine Arts at the UOC, among others.


\subsection{Tom~Beckmann}\label{tom-beckmann}

Affiliation: \textbf{Hasso Plattner Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/asymmetric-performance-in-virtual-reality-and-code.html}{Asymmetric
      Performance in Virtual Reality and Code (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-9}

Tom Beckmann is a PhD student at the Software Architecture Group at the
Hasso Plattner Institute at the University of Potsdam. In his thesis, he
is investigating the use of structured editing for general-purpose
programming languages. Beyond that, he is investigating the use of
programming tools for virtual reality, games, and other domain-specific
use cases.


\subsection{Patrick~Borgeat}\label{patrick-borgeat}

Affiliation: \textbf{TOPLAP Karlsruhe}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Satellite
      Event Coordinator (Committee)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Performance
      Chair (Committee)}}
\end{itemize}

\paragraph{Biography}\label{biography-10}

Patrick Borgeat, born in 1985, is a German live coder, code-based
artist, and programmer. Already for many years he is involved in
Karlsruhe as a live coder, live visuals performer and organizer of live
coding events. Since 2010 he has been active throughout Europe with
performances, exhibitions, talks, and workshops. With the live coding
ensemble Benoît and the Mandelbrots Patrick received an Honorary Mention
at the Prix Ars Electronica (2012) in the Digital Music \& Sound Art
category; with the audiovisual band Ganzfeld he was awarded an Honorary
Mention at the Visual Music Live Competition (2015).


\subsection{Sara~Bouchard}\label{sara-bouchard}

Affiliation: \textbf{Virginia Commonwealth University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/listening-to-the-future-landscape.html}{Listening
      to the (Future) Landscape (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-11}

Sara Bouchard is a multidisciplinary artist and composer who uses sound,
installation and performance to interweave song, story and the
landscape. She has exhibited and performed internationally, including at
The Aldrich Contemporary Art Museum (CT, USA), The Center for Book Arts
(NYC, USA), the American Folk Art Museum (NYC, USA), the Berlin
Underground (Germany), Third Practice Electroacoustic Music Festival
(VA, USA), and Hybrid Live Coding Interfaces (international). Her work
is in a growing number of public collections, including the Princeton
University Library. Born in Stockton, CA, she received her BA from Yale
University in 2003 and was subsequently based in Brooklyn, NY, for 13
years. She relocated to Richmond, VA, to study with sound artist Stephen
Vitiello, earning her MFA from Virginia Commonwealth University in 2019.
She is currently Adjunct Faculty at VCUarts Department of Kinetic
Imaging.


\subsection{Ilze~Briede~(Kavi)}\label{ilze-briede-kavi}

Affiliation: \textbf{The Endemics}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/a-quad-entropic-conversation.html}{A
      Quad Entropic Conversation (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-12}

The Endemics is an ensemble initially formed online during the pandemic,
consisting of four live coders based in Tkaronto/Toronto. Ilze Briede
(Kavi) is a Latvian/Canadian artist working across multiple disciplines,
including visual art, interactive installation and live performance.
Kavi live codes in Atom-Hydra and is most fascinated by feedback loops.


\subsection{Peni~Candra~Rini}\label{peni-candra-rini}

Affiliation: \textbf{Institut Seni Indonesia Surakarta}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-13}

Peni Candra Rini is a composer, educator, and one of the few
contemporary female vocalists to perform \emph{sindhen}, a female
soloist singing style in a gamelan ensemble. Founder and director of the
Jagad Sentana Art Foundation. Strongly committed to preserving and
sharing the country\textquotesingle s musical traditions, Peni has
collaborated to create more than hundred musical compositions for music
concert, scoring movie, dance, theater, with renowned artists and
received several awards from inside and outside Indonesia, including the
Kronos Quartet for the program Fifty For The Future 2021 (USA), OneBeat
Accelerator 2020 by Found Sound Nation (USA), Recipient of Government
Assistance for Revitalization of Creative Space Infrastructure and
Facilities, from the Ministry of Tourism and Creative Economy, Indonesia
2021.


\subsection{Martin~Carlé}\label{martin-carluxe9}

Affiliation: \textbf{Ionian University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/reproducible-musical-analysis-of-live-coding-performances-using.html}{Reproducible
      Musical Analysis of Live Coding Performances Using Information
      Retrieval: A Case Study on the Algorave 10th Anniversary (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-14}

Dr. Martin Carlé lives as a musicologist, media theorist and Emacs
org-mode enthusiast. His cultural objective is to leverage Literate
Programming techniques as a performative methodology for experimental
media arts, reproducible research and a sustainable computer literacy.
While running a music recoding studio and an audio consultant company,
he studied systematic musicology, popular music and media history at the
Humboldt-University Berlin (HUB). There he received his doctoral degree
with a thesis on the epistemology of ancient Greek music theory and the
respective musical notation systems. Within the frame of the German
Research Society (DFG), he worked at the Helmholtz Institute for Culture
Techniques and taught as assistant professor at the department of Media
Studies (HUB). Ongoing international collaborations include the French
ANR project "PROGRAMme". He is currently working as a postdoctoral
researcher in the Hub of Arts Laboratories at the Audio \& Visual Arts
Department of the Ionian University.


\subsection{Ramon~Casamajó~(QBRNTHSS)}\label{ramon-casamajuxf3-qbrnthss}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/qbrnthss-hybrid-set.html}{QBRNTHSS
      hybrid set (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-15}

QBRNTHSS (pronounced "quebrantahuesos", meaning "bearded vulture" in
Spanish) is the alias that Ramon Casamajó, musician and educator, uses
for his solo works focused on electronics and live coding. As QBRNTHSS
he released a split LP (Harry Dean Stanton, \emph{Call It Anything
Records} 2019), and is actively involved in the TOPLAP Barcelona
collective. In 2023 he will release his first LP on the Sheffield-based
label \emph{Interworld Media}. He has played in international events and
venues like Ars Electronica 2020, Sónar, VIU 2021, Iklectik London,
Algorithmic Art Assembly 2022, as well as in online events hosted by the
international TOPLAP community. He is part of Turing Tarpit, a duet
focused on free improvisation with whom he has released several works
and played regularly in Barcelona\textquotesingle s experimental
underground circuit. He also runs the micro record label \emph{Call It
Anything Records}.


\subsection{Kirby~Casilli}\label{kirby-casilli}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/we-all-begin-in-abstraction.html}{We
      All Begin in Abstraction (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-16}

Kirby Casilli is a socio-spatial entity working within various channels
of durational performativity. Adopting movement and communication as a
methodology to underpin the points of tension and mundanity that arise
from the spectacle \& destruction of social order.

Casilli surveys their findings through discursive modes of drawing and
form-making, evoking the public, outside, metropolitan center by staging
various interventions. Casilli has held a consistent practice through
vocal, literary, drawing, and dance performance work and has performed
most recently at Discordia Gallery, Adult Contemporary and Crawl Space
Radio, as well as Mejia Gallery, Seventh Gallery, Tinning St, Sutton
Project Space, Milk Gallery, Womadelaide, Howler, MPavillion, Margaret
Lawrence.

Casilli has performed internationally in the MAYRIT Biennale for
Architecture and Design in Madrid and collaborated internationally for
the International Conference of Live Coding in both Madrid and New York
City.


\subsection{Alicia~Champlin}\label{alicia-champlin}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/workshop/easy-stochastic-live-coding-with-megra-3.html}{Easy
      Stochastic Live Coding with Mégra 3 (Workshop)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Performance
      Chair (Committee)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Video
      Chair (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/neowise-5-8-v-e.html}{Neowise
      5.8 V/E (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-17}

Alicia Champlin (USA, 1975) is an independent intermedial artist and
researcher based in Barcelona. Champlin's creative practices have come
to focus on feedback-driven, generative systems in pursuit of the
phenomenological intersection of networked communication and identity.
In installations, she applies systems theory to employ sound and
interaction in modeling complex and dynamic relationships to explore
cybernetic and post-structuralist issues of communication. She also has
performance practices both with live-coding (primarily TidalCycles) and
with the bow chime (a.k.a. steel cello), which sometimes intersect.
Champlin received her MFA from the University of Maine and has performed
or exhibited with Sònar Festival, Cabaret Voltaire, BEK, IEM, and
PIFcamp.

\url{https://aliciachamplin.cartographile.com}


\subsection{Lucy~Cheesman}\label{lucy-cheesman}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/epiploke.html}{Epiploke
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-18}

Lucy Cheesman is a sound artist, musician, producer and organiser whose
work can be placed within a number of different fields, often blurring
the boundary between the visual, the audible and the digital. Lucy is a
founder member of SONA (a network supporting women in Sheffield through
experimental sound and digital practices) and the Yorkshire Sound Women
Network. Along with her artistic practice she also makes music under the
name Heavy Lifting, using software such as TidalCycles and FoxDot --
open-sourced coding programmes aimed at opening up the processes of
experimental music production for the benefit of the wider public. She
also runs the record label Pickled Discs, which is dedicated to
promoting experimental electronic sounds.


\subsection{Joana~Chicau}\label{joana-chicau}

Affiliation: \textbf{Creative Computing Institute, University of the
  Arts London}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/human-computer-counter-choreographies-beta.html}{Human-Computer
      Counter-Choreographies (Beta) (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-19}

Joana Chicau (PT/UK) is a designer and researcher --- with a background
in dance. In her practice she researches the intersection of the body
with the constructed, designed, programmed environment, aiming at
widening the ways in which digital sciences is presented and made
accessible to the public. She has been actively participating and
organizing events with performances involving multi-location
collaborative coding, algorithmic improvisation, open discussions on
gender equality and activism.

Website: \href{/2023/joanachicau.com}{joanachicau.com}


\subsection{Andrew~Claes}\label{andrew-claes}

Affiliation: \textbf{Royal Conservatoire Antwerp}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/botbop-integers-strings.html}{Botbop:
      Integers \& Strings (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-20}

Andrew Claes plays mainly saxophone and windcontrollers. Pursuing his
PhD. in the Arts, a love for tinkering, programming and live coding
sparked. As a member of jazz fusion band STUFF and a lot of other
projects including Stellar Legions, BRZZVLL, Internal Sun and many more,
he had the opportunity to play an impressive number of concerts
throughout the world for a wide variety of audiences. Andrew has a keen
interest for live coding in Bespoke Synthesizer, an open source modular
DAW featuring a scripting interface using Python. His dream would be a
giant dynamic music system generating an endless stream of interactive
music to jam to.


\subsection{Ian~Clester}\label{ian-clester}

Affiliation: \textbf{Georgia Institute of Technology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/lambdaw-towards-a-generative-audio-workstation.html}{LambDAW:
      Towards a Generative Audio Workstation (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-21}

Ian Clester composes music and programs. His research interests include
the design of languages, environments, and tools for composing and
performing music with computational or generative aspects. His
performance practice includes electric guitar and live coding, and he is
a founding member of the MIT Laptop Ensemble. His work has been
recognized with best paper (Web Audio Conference 2022) and best poster
(Audio Mostly 2021) awards. He received his B.Sc. in EECS and music and
his M.Eng. in EECS from MIT, and he is currently pursuing a Ph.D. in
music technology at Georgia Tech.


\subsection{Monique~Copper}\label{monique-copper}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/variations-on-kandinsky.html}{Variations
      on Kandinsky (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-22}

Monique Copper received her musical education in Geneva, Rotterdam,
Utrecht and London. While living in London she made her debut at the
Purcell Room and performed worldwide as a soloist and with various
ensembles such as ASKO Ensemble. Monique gives masterclasses in piano
and is regularly invited as a guest lecturer on `Dutch Electronic Music'
at Dutch academies such as Hogeschool Inholland Haarlem. Monique Copper
established not only a reputation for her innovative programs but also
for her illustrated children\textquotesingle s programs, lecture
recitals and recitals with narration with a touch of theater. She
collaborates with composers, writers, actors and visual artists to
create new programs. Her most recent program is "Water'', a performance
on the theme of water: a multimedia piano recital in which Monique
combines classical and contemporary piano works with poetry and video.
With "Water" Monique has toured the Netherlands, India, Vietnam, Poland,
Switzerland, Singapore and Italy.

\href{http://www.moniquecopper.com}{www.moniquecopper.com}

\subsection{Miki~Corfiel}\label{miki-corfiel}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\end{itemize}

\subsection{Malitzin~Cortés~(CNDSD)}\label{malitzin-cortuxe9s-cndsd}

Affiliation: \textbf{Toplap Mexico}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/live-cinema-coding-with-tidal-cycles-processing-and-unreal.html}{Live
      Cinema Coding with Tidal Cycles, Processing and Unreal Engine
      (Workshop)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{/2023/catalogue/performance/autoconstruccion.html}{AUTO\{\}Construcción
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-24}

\emph{Musician, Speculative Architect, Creative Technologist.}

As an artist, she investigates the forms in which the sound, the
architecture, the technology and the science hold the ability to be
great diffusers of discoveries and devices of self-reflection that can
unleash speculative worlds. Through live coding processes, experimental
sound, CGI, game software, installation, virtual reality and enhancement
and performance, I seek to merge the physical and the digital through
new models of social interaction and politics capable of providing new
forms of relationship from the utopia and the fiction in this constant
state of crisis and also of hope.

She is a professor and researcher at the Universidad CENTRO \textbar{}
Design, Film and Television in the field of creative code, STEAM and new
sound and immersion technologies and in the CMMAS in the field of
algorithmic music composition and live coding.


\subsection{Francesco~Corvi}\label{francesco-corvi}

Affiliation: \textbf{Institute of Sonology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/live-coding-and-education-a-practical-experience.html}{Live
      Coding and Education. A Practical Experience. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/commuta-a-cross-adaptive-laptop-ensemble.html}{Commuta:
      A Cross Adaptive Laptop Ensemble (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-25}

Francesco Corvi (\href{https://nesso.xyz}{nesso.xyz}) is a performer,
musician, lecturer and multimedia artist based in the Netherlands. His
artistic work explores new technologies by developing unconventional
performance strategies, including live coding and adaptive systems,
raising philosophical questions concerning phenomenology, posthumanism,
and the study of complex systems. He graduated at CREA (Research Centre
for Audiovisual Processing, Frosinone, Italy) and he is currently doing
a master research project at the Institute of Sonology of Den Haag.
Between 2021 and 2022 he performed at ICFP2022, Blooming Festival,
Didacta, Punctum, Build Stuff, Spring Attitude, C(A)OSMO Festival and
more. He gave lectures for KABK, NABA, Umanesimo Artificiale, University
of Pisa and led a training project for music teachers together with
INDIRE and Tempo Reale. His work was exhibited at Creative Code
Festival, WeSa Seoul, Glitch Art Pixel Language, ArteScienza. He
released music for Superpang, Kaer\textquotesingle Uiks, Genot Centre,
Riforma, Mossa Records, Heel.zone.


\subsection{Amy~Cullis}\label{amy-cullis}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/the-cuckoo-s-nest.html}{The
      Cuckoo\textquotesingle s Nest (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-26}

Amy Ruth Cullis has been a Morris dancer for ten years and has recently
become \textquotesingle Squire\textquotesingle{} or leader of a new team
in St Leonards-on-Sea. She works in a health centre and is new to live
coding.


\subsection{Ted~Davis}\label{ted-davis}

Affiliation: \textbf{IDCE HGK FHNW}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/p5live-a-p5-js-collaborative-live-coding-vj-environment.html}{P5LIVE:
      A p5.js Collaborative Live Coding VJ Environment (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/performance/p5live-cocoding.html}{P5LIVE
      COCODING (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-27}

Ted Davis is a media educator / artist / designer originally from the
United States and based in Basel, Switzerland. Since 2010 he teaches
interaction design and coordinates the UIC/HGK International Master of
Design program within the Institute Digital Communication Environments
IDCE, HGK FHNW. His work and teachings explore the volatility of digital
media through glitch and reactivating older `new media' through newer
programming means.

His open source projects (basil.js, XYscope, P5LIVE, p5.glitch) enable
designers to program within Adobe InDesign, render vector graphics on
vector displays, collaboratively live code visuals with p5.js, and
glitch any media in real-time within the web browser. In 2021 he
received the Basel Media Art Prize (Basler Medienkunstpreis) for
p5.glitch and was a Processing Foundation Teaching Fellow. With
international exhibits, lectures and workshops, he empowers students to
take hold of the computer's ability to design possibilities beyond that
of the hand or mouse.

\url{https://teddavis.org}


\subsection{Georgios~Diapoulis}\label{georgios-diapoulis}

Affiliation: \textbf{Chalmers University of Technology, University of
  Gothenburg}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/reproducible-musical-analysis-of-live-coding-performances-using.html}{Reproducible
      Musical Analysis of Live Coding Performances Using Information
      Retrieval: A Case Study on the Algorave 10th Anniversary (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-28}

Georgios Diapoulis (b. 1981) is a PhD student in Interaction Design at
Chalmers University of Technology and University of Gothenburg,
Gothenburg, Sweden. He has a bachelor\textquotesingle s degree in
Materials, Science and Technology from the University of Crete,
Heraklion, Crete, and a master\textquotesingle s degree in Music
Psychology from the University of Jyväskylä, Jyväskylä, Finland. He is
also a Marie-Curie alumnus from the European project on Building
Acoustics, Acoutect. He has been teaching for several years in academic
and non-academic contexts. His doctoral studies focus on musical live
coding, with a particular focus on minimal languages. He has performed
with various bands for several years and sporadically performed as a
live coder during the last decade. He is also a proud member of the
TOPLAP Athens node!


\subsection{Drymonitis~Alexandros}\label{drymonitis-alexandros}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/livelily-workshop.html}{LiveLily
      Workshop (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-29}

Alexandros Drymonitis is a sound and new media artist. He is a PhD
candidate at the Royal Birmingham Conservatoire doing research on the
creation of musical works with the programming language Python. His
artistic practice focuses on new techniques utilizing new media such as
computer programming, AI, or even older practices, like modular
synthesis.

He has collaborated with various artists from different art disciplines,
plus several ensembles, either interdisciplinary or music ensembles.

He has taught the guitar at the Music School of Amsterdam and `Philippos
Nakas' Conservatory in Athens, and electronic music programming at
`Musical Praxis' Conservatory in Athens. He is currently a freelancer in
the field of electronic music and multimedia programming, teaching
several workshops in various venues and undertaking multimedia
programming in various events.

\subsection{Juan~Felipe~Amaya~Gonzalez}\label{juan-felipe-amaya-gonzalez}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/mosaik-staging-contemporary-ai-performance-reflections-on-live-e.html}{MosAIck:
      Staging Contemporary AI Performance - Reflections on Connecting Live
      Coding, e-Textile and Movement (Paper)}}
\end{itemize}

\subsection{Rebecca~Fiebrink}\label{rebecca-fiebrink}

Affiliation: \textbf{Creative Computing Institute, University of the
  Arts London}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/genny-designing-and-exploring-a-live-coding-interface-for-generative-models.html}{Genny:
      Designing and Exploring a Live Coding Interface for Generative Models
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-31}

I am a Professor of Creative Computing at the UAL Creative Computing
Institute. My students, research assistants, and I work on a variety of
projects developing new technologies to enable new forms of human
expression, creativity, and embodied interaction. Much of my current
research combines techniques from human-computer interaction, machine
learning, and signal processing to allow people to apply machine
learning more effectively to new problems, such as the design of new
digital musical instruments and gestural interfaces for gaming and
accessibility. I am also involved in projects developing rich
interactive technologies for digital humanities scholarship, exploring
ways that machine learning can be used and appropriated to reveal and
challenge patterns of bias and inequality, and advancing machine
learning education.


\subsection{Rodney~Folz~(haute.rod)}\label{rodney-folz-haute.rod}

Affiliation: \textbf{AV Club SF}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/av-club-sf-community-report.html}{AV
      Club SF Community Report (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-32}

Rodney Folz (haute.rod) is a founding member of AV Club is an algorave
visualist based in SF, focused on live creation of complex scenes
featuring organic forms and layered feedback that are even pleasant to
look at sometimes. He focuses on exploring the possibilities of Hydra
video synthesizer, extending the tool with custom functionality to
achieve new possibilities.


\subsection{Raphaël~Maurice~Forment~(Bubobubo)}\label{raphauxebl-maurice-forment-bubobubo}

Affiliation: \textbf{ECLLA, Université Jean Monnet}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/sardine-a-modular-python-live-coding-environment.html}{Sardine:
      A Modular Python Live Coding Environment (Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/ziffers-numbered-notation-for-algorithmic-composition.html}{Ziffers:
      Numbered Notation for Algorithmic Composition (Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/sardine-x-ziffers-new-tools-for-algorithmic-expression.html}{Sardine
      X Ziffers: New Tools for Algorithmic Expression (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-33}

Raphaël Maurice Forment is a contractual doctoral student at the
University Jean Monnet of Saint Etienne (ECLLA, ED 484 3LA), his thesis
being carried out in collaboration with the University Paris 8
Saint-Denis (MUSIDANSE). His doctoral work is directed by Laurent
Pottier (UJM, ECLLA) and Alain Bonardi (Paris 8, MUSIDANSE). Raphaël is
studying the links and tensions between techniques and aesthetic
discourses that cross the field of improvised computer music. He is
studying live coding both as an artistic practice and as a programming
technique. He is developing software for live coding performance both
for academic research and personal musical projects. Raphaël regularly
performs on stage in France with the Cookie Collective or with friends.
Raphaël is invested in live coding pedagogy. He teaches live coding both
at university and in informal settings (workshops, speeches, etc).


\subsection{Giulia~Francavilla~(Giulia~Rae)}\label{giulia-francavilla-giulia-rae}

Affiliation: \textbf{Institute of Sonology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/commuta-a-cross-adaptive-laptop-ensemble.html}{Commuta:
      A Cross Adaptive Laptop Ensemble (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-34}

Giulia Rae is an Italian composer, researcher, performer and sound
designer based in Turin (IT). In 2021 she obtained a Research Master
Degree at the Institute of Sonology (The Hague), where she is currently
a Research Associate. With a keen interest in creative coding and sound
design, semi-generative systems and live performance, she bases her
artistic practice and research on immersive sound and the listening
experience. Influenced by the theoretical discourse on human-machine
interaction, embodiment, deep listening and perception, she develops her
works in the field of algorithmic music, VR, multichannel and 3D audio.
In 2022 she worked as an artist in residency at CICM of Paris VIII and
at iMAL studios in Brussels. Her releases are on Søvn Records, Ovaal,
Light Item, Intersezioni, Solium Records, Guerrilla Bizarre.

In parallel, she works as a composer and sound designer for video,
theatre, dance and multidisciplinary projects.


\subsection{Alejandro~Franco~Briones}\label{alejandro-franco-briones}

Affiliation: \textbf{McMaster University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/towards-another-transdiscipline-art-techno-science-and-as-and.html}{Towards
      Another Transdiscipline: Art, (Techno)Science and Emancipation as
      Promise and Provocation for Live Coding (Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/piraran-algorithmic-acid-music.html}{Pirarán
      -- Algorithmic Acid Music (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-35}

Alejandro is a PhD Candidate in the Department of Communications Studies
and Media Arts at McMaster University. His research entails the
development of infrastructure, interfaces, and protocols for online
live-coded music and sound art creation. His research is related to the
fields of sound studies, time studies, and internet studies with a
perspective mediated by de-colonialism, anti-fascism, Marxism, and
feminism. He has presented multiple times at the International
Conference on Live Coding and the Electroacoustic Music Seminar in
Mexico City. Alejandro is currently a sessional professor at McMaster
University, teaching Spatial and Interactive Audio, and a Research
Assistant in the Networked Imagination Laboratory developing Estuary, a
software for networked live coding. Most recently, he published a
chapter in the book Music and Time: Psychology, Philosophy, Practice
(Boydell Press), titled `Live Coding as a Theatre of Agency and a
Factory of Time.


\subsection{Glen~Fraser}\label{glen-fraser}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/workshop/animatron-workshop-live-coding-visual-poetry.html}{Animatron
      Workshop: Live Coding Visual Poetry (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-36}

Glen Fraser (CA) is a Barcelona-based software engineer/artisan who has
worked in graphics, sound, interactive and immersive technology for
three decades. Most of his professional life has been spent creating
software tools for artists, collaborating directly with artists, and
wondering whether to call himself an artist. His first foray into live
coding was in 2013, and since 2019 he has been active with TOPLAP
Barcelona, exploring musical/visual live coding and performing with
tools of his own creation. Glen develops and uses Bacalao, his personal
collection of live-coding tools for SuperCollider, and co-created the
Animatron tool for live-coded ``visual poetry'' and animation.

\begin{itemize}
  \tightlist
\item
  \url{http://glenfraser.com/}
\item
  \url{https://github.com/totalgee/bacalao}
\item
  \url{https://github.com/loopier/animatron}
\end{itemize}


\subsection{Saskia~Freeke}\label{saskia-freeke}

Affiliation: \textbf{Live Coding Sessions}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Design
      (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/amalgam.html}{Amalgam
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-37}

Saskia Freeke is an artist, creative coder, interaction designer, visual
designer and educator. Her work addresses structure, geometry and
playfulness. A significant part of her artistic practice is the ongoing
daily art project she started in January 2015, in which she explores and
experiments with generative patterns and animations. Starting 2019 she
has extended her practice of expression by incorporating geometry and
playfulness in live coded visual performances on stage. Saskia has been
a lecturer in Physical Computing at Goldsmiths, University of London and
taught visual design at the University of the Arts Utrecht School for
Games and Interaction.


\subsection{Jason~Freeman}\label{jason-freeman}

Affiliation: \textbf{Georgia Institute of Technology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/lambdaw-towards-a-generative-audio-workstation.html}{LambDAW:
      Towards a Generative Audio Workstation (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-38}

Jason Freeman is Professor of Music at Georgia Tech and Chair of the
School of Music. His artistic practice and scholarly research focus on
using technology to engage diverse audiences in collaborative,
experimental, and accessible musical experiences. He also develops
educational interventions in K-12 and university environments that
broaden and increase engagement in STEM disciplines through authentic
integrations of music and computing. His music has been performed at
Carnegie Hall, exhibited at ACM SIGGRAPH, published by Universal
Edition, broadcast on public radio\textquotesingle s Performance Today,
and commissioned through support from the National Endowment for the
Arts. Freeman's wide-ranging work has attracted funding from sources
such as the National Science Foundation, Google, and Turbulence. It has
been disseminated through over 80 refereed book chapters, journal
articles, and conference publications. Freeman received his B.A. in
music from Yale University and his M.A. and D.M.A. in composition from
Columbia University.


\subsection{Luka~Frelih}\label{luka-frelih}

Affiliation: \textbf{Ljudmila Lab}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Workshop
      Chair (Committee)}}
\end{itemize}

\paragraph{Biography}\label{biography-39}


\subsection{Axel~Ganz~(Grimberg)}\label{axel-ganz-grimberg}

Affiliation: \textbf{Toplap Düsseldorf}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/grim-grim-grim.html}{Grim!
      Grim! Grim! (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-40}

Grimberg aka Axel Ganz was born in 1965 in Gelsenkirchen, Germany. He is
cofounder of Toplap Düsseldorf Node. Since 2018 he organizes together
with Markus van Well music concerts. He also conducts introductory
workshops to live coding, robotics, 3d-design and 3d-printing. Since
2019 he lives and works in both countries, Germany and Georgia,
Caucasia.


\subsection{Jessica~Garson~(Messica~Arson)}\label{jessica-garson-messica-arson}

Affiliation: \textbf{LiveCode.NYC}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/arrays-of-disarray.html}{Arrays
      of Disarray (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-41}

Messica Arson is a Brooklyn-based artist who creates unique and
electrifying computational noise music. Using live coding and live
sampling, she incorporates sampled screams into her beats to add a raw
and powerful element to her sound. Described by The Financial Times as
"gnarly cut-up sounds," her music is not afraid to push the boundaries
of traditional music.


\subsection{Leonard~Geier}\label{leonard-geier}

Affiliation: \textbf{Hasso Plattner Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/asymmetric-performance-in-virtual-reality-and-code.html}{Asymmetric
      Performance in Virtual Reality and Code (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-42}

Leonard Geier is a master\textquotesingle s student currently working on
his thesis at the Software Architecture Group of the Hasso Plattner
Institute at the University of Potsdam, in which he explores methods for
developing software from within virtual reality.


\subsection{Agata~Genissel}\label{agata-genissel}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/brickwork-destroy.html}{Brickwork:
      Destroy (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-43}

Agata Genissel uses audio-visual live coding to explore notionsof
world-building in the realm of live performance. Primarily using
TidalCycles and Hydra to build a stage, she seeks to key into the fun
and playful elements of musical improvisation. Relying on instinct and
on the force of the sounds and textures of these repeated patterns built
using TidalCycles, Agata delivers BRICKWORK as a moment in which people
are encouraged to dance and reflect.

Based in London, Agata's performances play around with spatial
characteristics. Whether this involves ripping down paper-built walls in
Venue MOT Unit 18, projecting a live feed of the audience back into the
space, or moving around to incorporate live drums and vocals into the
mix, Agata is always keen to interfere with the dimensions of live
coding as something that does not place the performer strictly behind
the screen.


\subsection{Rémi~Georges~(Ralt144MI)}\label{ruxe9mi-georges-ralt144mi}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/sardine-x-ziffers-new-tools-for-algorithmic-expression.html}{Sardine
      X Ziffers: New Tools for Algorithmic Expression (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-44}

Ralt144MI (Rémi Georges) is a sound engineer, music programmer and
visual artist based in Lyon. Combining old and new technologies in his
personal projects, he creates custom tools and compositions, with
particular interests in image-sound relationship, low-tech and
open-source creation, glitch art and circuit bending. Rémi is evolving
in the Algorave\textquotesingle s, acousmatic music and noise music
circles. He is involved in musical associative, self-managed and
counter-culture places. He founded the French live coding cassettes \&
prints label
\href{https://ordinateurdanslatete.bandcamp.com/}{Ordinateur Dans La
  Tête}.


\subsection{Kosmas~Giannoutakis}\label{kosmas-giannoutakis}

Affiliation: \textbf{Rensselaer Polytechnic Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/serendipitous-liquidators.html}{Serendipitous
      Liquidators (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-45}

Kosmas Giannoutakis studied piano and percussion performance,
composition, and computer music in Greece, Germany, and Austria.
Currently, he is attending the Ph.D. Electronic Arts program at the
Rensselaer Polytechnic Institute, with a focus on experimental,
post-capitalist political economies of music, which are supported by
Distributed Ledger Technology. His works have been presented and
received awards in various international festivals and conferences, such
as inSonic in ZKM Karlsruhe, ALIFE 2018 conference in Tokyo, Matera
Intermedia Festival, GRAME in Lyon, eviMus6 in Saarbrücker,
{[}sound{]}Spectrum New Music Seminar in Bydgoszcz, Multimedia Festival
Diffrazioni in Florence, Sound Campus at Kunstuniversität Linz, Junge
SIGNALE concert series in Graz, Soundislands Festival in Singapore,
Toronto International Electroacoustic Symposium, New York City
Electroacoustic Music Festival, Gaudeamus Muziekweek 2015 and ICMC 2016
in Utrecht, REAL/UNREAL BEAST FEaST 2016 in Birmingham, klingt gut! 2016
in Hamburg, 13th Athens Digital Arts Festival.


\subsection{Bruno~Gola}\label{bruno-gola}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/c0l1v3.html}{c0l1v3
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-46}

Bruno Gola is a sound and code artist from Brazil. He studied computer
science in São Paulo before moving to Berlin and studying Art and Media
at the Berlin University of the Arts. His work often embraces chance and
public interaction while navigating well defined possibility spaces. In
his sound performances he explores Live Coding and other algorithmic
techniques for improvisation.


\subsection{Marcus~Gordon~(magfoto)}\label{marcus-gordon-magfoto}

Affiliation: \textbf{The Endemics}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/a-quad-entropic-conversation.html}{A
      Quad Entropic Conversation (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-47}

The Endemics is an ensemble initially formed online during the pandemic,
consisting of four live coders based in Tkaronto/Toronto. magfoto
(Marcus Gordon) is a live coder, artist, and PhD candidate in
Computational Arts at York University. His practice explores live coding
archimusic, composition and improvisation with modular synthesis.


\subsection{Dan~Gorelick~(dan.dog)}\label{dan-gorelick-dan.dog}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{AV Club SF}
\item
  \textbf{LiveCode.NYC}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/the-craft-of-algorave-documentation.html}{The
      Craft of (Algorave) Documentation (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/video/av-club-sf-community-report.html}{AV
      Club SF Community Report (Community Report Video)}}
\item
  \textbf{Title to come post-performance (Performance)}
\end{itemize}

\paragraph{Biography}\label{biography-48}

Dan Gorelick (\href{https://dan.dog}{dan.dog}) is a Brooklyn and San
Francisco based artist, developer, and creative technologist. He blends
live-coding with acoustic and electronic instruments to create
improvisational performances. Dan is also an organizer of the
live-coding artist collectives AVClubSF and LiveCode.NYC. His work has
been featured at SXSW, Github Universe Conferences, and Gray Area.


\subsection{Sarah~Groff~Hennigh-Palermo}\label{sarah-groff-hennigh-palermo}

Affiliation: \textbf{Codie}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/visualists-meetup.html}{Visualists
      Meetup (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/performance/codie.html}{Codie
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-49}

Sarah Groff Hennigh-Palermo is the visualist for Codie, a live-code
collective that originated in NYC, but has spread around the world. She
performs with La Habra, her homemade Clojurescript--Electron library and
is particularly interested in rhythms, textures, and artifacts. When not
performing, Sarah makes large-scale video art and computer programs in
Berlin. She has shown work at Pioneer Works (US), Westbeth Gallery (US),
and Nomas* Gallery (UK).


\subsection{Bjarni~Gunnarsson}\label{bjarni-gunnarsson}

Affiliation: \textbf{Institute of Sonology}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/blocking-behaviours.html}{Blocking
      Behaviours (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-50}

Bjarni Gunnarsson is an Icelandic Composer and Computer Scientist
involved in computer music and algorithmic composition. Has released his
music on labels such as Vertical Form, Superpang, Tartaruga and SOVN
Records and performed his music in festivals such as Tectonics, Rewire,
Today\textquotesingle s Art, Sonar and Presences Electroniques.
Collections of his recent solo works can be found on the releases
"Paths" (2016), "Lueur" (2018), "Volume \& Void" (2020), "Cendres"
(2020) and "Anticlines" (2021).

Bjarni is a faculty member at the Institute of Sonology, Royal
Conservatory, in The Hague. He is concerned with process-based ideas.
Sounds focusing on internal activity and motion. Compositions that put
into foreground behaviors, actions, fluid sound structures, fuzzy
materials, or forms. His recent research focus includes the construction
of persistent synthetic environments, creative uses of digital
interrupts, and machine-listening observers that react to
computer-generated sound.


\subsection{Don~Hanson~(d0n.xyz)}\label{don-hanson-d0n.xyz}

Affiliation: \textbf{AV Club SF}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/av-club-sf-community-report.html}{AV
      Club SF Community Report (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-51}

d0n.xyz (Don Hanson) is a designer, electronic musician and Internet
artist known for creating experimental websites and establishing New Art
City, the virtual art space for digital exhibitions. His artworks
include a tool for creating interactive music videos, a browser
extension that covers your window with plants, a tracker for an
autonomous robot released in the desert, an AR geolocation game that
simulates the TOR network, and several types of video synthesizers. From
2009-2020 he ran the electronic music label Gridwalk, and is currently
working on a new series of generative art that doubles as a live AV
performance tool. His work has been featured in the New York Times, Art
in America, SXSW, and CBC radio.

Find his projects online at \url{https://d0n.xyz}


\subsection{Roxanne~Harris~(alsoknownasrox)}\label{roxanne-harris-alsoknownasrox}

Affiliation: \textbf{LiveCode.NYC}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/broken-bond.html}{Broken
      Bond (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-52}

Roxanne Harris, alsoknownasrox, is a multidisciplinary artist and
educator based in Brooklyn, New York. She approaches programming as a
medium for creative expression. Roxanne specializes in programming as
performance, modifying real-time processes to create dynamic audiovisual
experiences. She leads workshops and organizes shows as an active member
of LiveCode.NYC.


\subsection{Citlali~Hernández~Sánchez~(turbulente)}\label{citlali-hernuxe1ndez-suxe1nchez-turbulente}

Affiliation: \textbf{Toplap BCN}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/crash-landing.html}{CRash
      Landing (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-53}

Citlali Hernández is a mexican artist and designer whose work focuses on
exploring the potentialities of the body in the field of electronic and
digital arts. Her experiments intertwine the materialities of live
performance art, wires, pixels and circuits. Lately she has been
exploring the relationship between digital viral media and non verbal
communication in social media platforms through networked and hybrid
(online-offline) performances. During the last 10 years she has been
happily collaborating with other artists to create artworks that have
been presented in Mexico, Chile and Spain. She is a digital fabrication,
design and interaction teacher in several institutions, and participates
as a visualist with Toplap Barcelona using her body and Hydra.
www.turbulente.net


\subsection{Robert~Hirschfeld}\label{robert-hirschfeld}

Affiliation: \textbf{Hasso Plattner Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/asymmetric-performance-in-virtual-reality-and-code.html}{Asymmetric
      Performance in Virtual Reality and Code (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-54}

Robert Hirschfeld leads the Software Architecture Group at the Hasso
Plattner Institute at the University of Potsdam. His research interests
include dynamic programming languages, development tools, and runtime
environments to make live, exploratory programming more approachable.
Hirschfeld received a PhD in computer science from Technische
Universität Ilmenau.

\subsection{Yannick~Hofmann}\label{yannick-hofmann}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\end{itemize}


\subsection{Timo~Hoogland}\label{timo-hoogland}

Affiliation: \textbf{Netherlands Coding Live}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Performance
      Chair (Committee)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Local
      Production (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/amalgam.html}{Amalgam
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-57}

Timo Hoogland is a computational artist, live coder, music technologist
and educator from the Netherlands. He livecodes algorithmic electronic
dance music and develops compositions, installations and performances
inspired by his fascination for mathematics, science and nature. Timo
graduated from the Masters of Music Design at the HKU University of the
Arts Utrecht in 2019, where he developed the livecoding environment
Mercury. In 2020 he started the audiovisual live coding collaboration
Amalgam with Saskia Freeke. The piece ./drum.code premiered during the 2
Ars Electronica garden in Lugano 2021, combining drums and live coding.
In 2022 he performed PRISM at Beyond Quantum Music in Belgrade. He build
av-works inspired by bioluminiscence and photosynthesis at Uncloud 2020
and Vonk 2021. Timo has performed at various festivals such as ICLC,
ADE, Gogbot, Tec-Art, Ars Electronica Garden, Droidcon Turin, React
Amsterdam and Digital Arts Zurich. He teaches creative system and sound
design at the HKU Bachelor of Music Technology.


\subsection{Daniel~Höpfner}\label{daniel-huxf6pfner}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Institute for Music Informatics and Musicology, University of
    Music Karlsruhe}
\item
  \textbf{TOPLAP Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-58}

Having had instrumental lessons in playing the recorder, piano, and
oboe, Daniel Kurosch Höpfner first came into contact with
electroacoustic music through self-study with PureData and
SuperCollider. Now pursuing a Ph.D. with a focus on implicit aesthetics
in MIR systems at the Institute for Music Informatics and Musicology at
the HfM Karlsruhe, his interests lie in auditory perception, audio
analysis, algorithm-derived synthesis and compositional structure,
improvised computer music, etc.


\subsection{Amy~Hurst}\label{amy-hurst}

Affiliation: \textbf{New York University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/addressing-accessibility-for-blind-and-visually-impaired-live.html}{Addressing
      Accessibility for Blind and Visually Impaired Live Coders (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-59}

Dr. Amy Hurst is an Associate Professor with a joint appointment in the
Department of Occupational Therapy in the Steinhardt School of Culture,
Education and Human Development and the Department of Technology,
Culture and Society in the Tandon School of Engineering. She is the
director of the NYU Ability Project, an interdisciplinary research space
dedicated to the intersection between disability and technology. Dr.
Hurst received her M.S. and Ph.D. in Human-Computer Interaction from the
Human-Computer Interaction Institute at Carnegie Mellon and a B.S. in
Computer Science from the Georgia Institute of Technology. Dr. Hurst is
passionate about understanding current social problems and identifying
opportunities for technology to empower individuals impacted by those
problems.


\subsection{Sarah~Imrisek~(@cymatiste)}\label{sarah-imrisek-cymatiste}

Affiliation: \textbf{The Endemics}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/a-quad-entropic-conversation.html}{A
      Quad Entropic Conversation (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-60}

The Endemics is an ensemble initially formed online during the pandemic,
consisting of four live coders based in Tkaronto/Toronto. Sarah Imrisek
(@cymatiste) is a game developer-turned-community-engaged artist and
creative coder. She performs in live coding events, and makes
interactive installations and street art. Trees, birds, wind, waves, and
dreamlike visuals abound.


\subsection{Eloi~Isern~Rabella~(Eloi~el~Bon~Noi)}\label{eloi-isern-rabella-eloi-el-bon-noi}

Affiliation: \textbf{Toplap BCN}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/rumble-machines.html}{Rumble
      Machines (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-61}

Eloi Isern aka Eloi el Bon Noi (Eloi the good guy) is a composer and
live coder interested in the use of code as a tool for sound design and
composition. He is an active member of the Top Lap community in
Barcelona. His conception of music is overloaded, pointillist, often
saturated, filling the screen with big blocks of code that hide complex
processes and push the CPU to the limit. He performs solo or
accompanying artists in free improvisation or spoken word sessions. He
has participated in several festivals of contemporary art, electronics
and algoraves in Spain.


\subsection{Olivia~Jack}\label{olivia-jack}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/visualists-meetup.html}{Visualists
      Meetup (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-62}

Olivia Jack is a programmer and artist who works frequently with
open-source software, cartography, live coding, and experimental
interfaces. She is the developer of browser-based creative tools
including Hydra (live-codable video synthesizer), PIXELSYNTH, and
LiveLab (peer-to-peer media router). Her live visual sets explore
algorithmic representations of unpredictable and chaotic systems, and
writing software as a messy and ephemeral process.

\url{https://ojack.xyz}


\subsection{Kaspars~Jaudzems}\label{kaspars-jaudzems}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Institute for Music Informatics and Musicology, University of
    Music Karlsruhe}
\item
  \textbf{TOPLAP Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-63}

Kaspars Jaudzems (1984 in Riga, Latvia) is an audiovisual artist working
mainly in code - designing, building, sequencing and composing using
algorithms and numbers. He builds light installations / sculptures that
exhibit life-like generative behaviors by using generative audiovisual
compositions which are performed, manipulated and driven to their limits
in a live-coding / live performance setting. His goal is to induce a new
experience of physical phenomena into the minds of the audience. He is
currently based in Karlsruhe, Germany.


\subsection{Aaron~J.~Juarez}\label{aaron-j.-juarez}

Affiliation: \textbf{Rensselaer Polytechnic Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/serendipitous-liquidators.html}{Serendipitous
      Liquidators (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-64}

Aaron Juarez is an interdisciplinary artist-researcher currently
residing in Troy, New York as he pursues the PhD in Electronic Arts at
Rensselaer Polytechnic Institute. In playing with digital structures, he
employs disjunctive strategies between art and science to engage
serendipity through experimental interactions of digital media,
including photography, film, and 3d models. Embracing the art of
wandering, Juarez has expanded into physical art through screen printing
and performance through live coding visuals. His theoretical research
interests include issues in creativity and cognition via humancomputer
interaction, as well as topics that consider the nonhuman agency of
technology. He has contributed writings, code, and artworks to online
venues and various exhibitions in America and Europe. His investigations
challenge perceptions of functionality and naturalized experience by
testing the limits of digital structures and encountering sublime
moments by allowing nature and technology to speak for themselves.


\subsection{Guy~John}\label{guy-john}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/visualists-meetup.html}{Visualists
      Meetup (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-65}

Guy John is an engineer with an interest in programming language design,
who enjoys building and performing with visual live coding environments.
He\textquotesingle s been a regular part of the UK live coding scene,
with performances at venues ranging from boats and warehouses parties to
the London Science Museum.


\subsection{Björn~Þór~Jónsson}\label{bjuxf6rn-uxfeuxf3r-juxf3nsson}

Affiliation: \textbf{University of Oslo}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/live-rendering-and-coding-evolved-sounds.html}{Live
      Rendering and -Coding Evolved Sounds (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-66}

synth.is has been developed by Björn Þór Jónsson, a software engineer
turned doctoral research fellow who recently joined RITMO at UiO to
explore further the application of quality diversity algorithms as a
foundation of a sound innovation engine. Björn is looking into methods
for the search and discovery of diverse patterns. Pondering how those
patterns can be applied to the generation of sound and rhythm.
Considering what modes of interaction with the sounds are well suited to
open up possibilities for creative discoveries.


\subsection{Kasper~Jordaens}\label{kasper-jordaens}

Affiliation: \textbf{LUCA School of Arts}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/botbop-integers-strings.html}{Botbop:
      Integers \& Strings (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-67}

Kasper Jordaens is a researcher at the LUCA School of Arts currently
researching spatial audio applications and AI-related computational
creativity tools. Graduated as a civil engineer architect he moved from
the arts field (as a designer in the studio of Wim Delvoye) through the
digital innovation field doing both hard- and software projects (VRT,
IMEC). He's been doing generative coding projects since his studies, but
only since 2014, with the founding of Lambdasonic (Toplap node) and
H.AL.I.C.(a live coding duo) this moved into the livecoding realm. After
some years of coding (quil) visuals in collaborative projects, playing
music (modular synth) in a band (de portables) gave way to live coding
musical projects too. Moving from an engineers' point of view into music
is not too uncommon in the algorave scene, but Kasper persists on
building bridges between the two worlds, balancing one leg on each side.


\subsection{Matthew~Kaney}\label{matthew-kaney}

Affiliation: \textbf{LiveCode.NYC}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/addressing-accessibility-for-blind-and-visually-impaired-live.html}{Addressing
      Accessibility for Blind and Visually Impaired Live Coders (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-68}

Matthew Kaney is a performer and technologist interested in
synthesizers, MIDI and web-based tools for creative expression. He
frequently performs music and visuals with the LiveCode.NYC collective,
where he has also helped organize recent shows.

His previous work includes video, electronic sculpture and a small bit
of theatrical light and video design. He\textquotesingle s contributed
to the development of Tidal Cycles, and his current focus is building
text.management, a new collaborative editor for live coding. He has a
master\textquotesingle s in art and technology from New York
University\textquotesingle s Interactive Telecommunications Program and
a BFA from the University of Oklahoma.

\subsection{Chris~Kiefer}\label{chris-kiefer}

Affiliation: \textbf{University of Sussex}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/useq-a-modular-sequencer-for-eurorack-with-a-livecodable.html}{uSEQ:
      A LISPy Modular Sequencer for Eurorack with a Livecodable
      Microcontroller (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-71}

Chris Kiefer is a computer-musician and musical instrument designer,
specialising in musician-computer interaction, physical computing, and
machine learning. He performs with custom-made instruments including
malleable foam interfaces, touch screen software, interactive sculptures
and a modified self-resonating cello. Chris\textquotesingle{} research
often focuses on participatory design and development of interactive
music systems in everyday settings, including digital instruments for
children with disabilities, and development of the NETEM networked score
system for musical ensembles. His work also concentrates on machine
learning and signal processing for audio and interaction, with an
emphasis on nonlinear and dynamical systems.


\subsection{Shelly~Knotts}\label{shelly-knotts}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{/2023/catalogue/performance/we-all-begin-in-abstraction.html}{We
      All Begin in Abstraction (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-72}

Shelly Knotts is an independent researcher and improviser who performs
with computers and other humans. She experiments with generative and AI
techniques and opinionated algorithms to make music. She has performed
at numerous Algoraves and other live coding events worldwide, solo and
with collaborative projects including algo-pop duo ALGOBABEZ. In 2021
she was selected for an artist residency at Hangar, Barcelona, as part
of the On-the-fly project. In 2017 she was a winner of BBC Radiophonic
Workshop and PRSF `The Oram Awards' for innovation in sound and music.
Previously she worked at Durham University and at Monash University as a
researcher on projects around the use of AI, data and networks in
improvisation and composition.


\subsection{Dimitris~Kyriakoudis}\label{dimitris-kyriakoudis}

Affiliation: \textbf{University of Sussex}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/useq-a-modular-sequencer-for-eurorack-with-a-livecodable.html}{uSEQ:
      A LISPy Modular Sequencer for Eurorack with a Livecodable
      Microcontroller (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-73}

Dimitris Kyriakoudis, also known as w1n5t0n of lnfiniteMonkeys, is a
musician, computational luthier, and HCI researcher born and raised in
Greece. Coming from a classical piano and music background, his studies
in Music Computing BSc at Goldsmiths, University of London, soon led to
an interest in Informatics and the practice and various instruments of
live coding. What started as a promising alternative to mouse-based
interfaces for computer music systems, which are incompatible with his
chronic struggle with RSI, evolved into a passion of its own towards the
medium\textquotesingle s potential for exression, musicking,
and---perhaps counter-intuitively---embodiment. He is currently pursuing
a PhD in Music Technology at the University of Sussex, where he is a
member of the Experimental MUsic TEchnologies (EMUTE) Lab. His research
focuses on Human-Computer Interaction and the design, ergonomics, and
ergodynamics of live coding instruments and their practice.


\subsection{Shawn~Lawson~(Obi-Wan~Codenobi)}\label{shawn-lawson-obi-wan-codenobi}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Arizona State University}
\item
  \textbf{The Rebel Scum}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/def-function-dystopiakira.html}{DEF
      FUNCTION(DYSTOPIAKIRA) (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-74}

Shawn Lawson is a computational artist and researcher creating the
computational\\
sublime. He performs under the pseudonym Obi-Wan Codenobi where he
live-codes real- time computer graphics and neural nets with his open
source software. Lawson has performed, exhibited, or screened in
museums, galleries, festivals, and public space across\\
five continents. Lawson has published in a wide range of international
technical and arts\\
conferences and journals. His work has been funded by national and
international agencies.\\
Lawson studied fine arts at Carnegie Mellon University and École
Nationale Supèrieure des Beaux-Arts and received his MFA from the School
of the Art Institute of Chicago. He is an\\
Associate Professor and Animation Program Director at Arizona State
University.


\subsection{Song~Li~(李松)}\label{song-li-ux674eux677e}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/der-dritte-korper.html}{Der dritte
      Körper (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/underscore-underscore-underscore.html}{{[}
        \_ \_ \_ {]} (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-75}

Li Song (李松) is a London-based musician and computer programmer. He
performs improvised music with his computer and composes music using
electronics and acoustic instruments. His collaborative project with Zhu
Wenbo, No Performance, focuses on compositions using environment sounds,
acoustic instruments, computer algorithms, and random sequence. He is
also a member of computer network music ensemble and research group, {[}
  \_ \_ \_ {]}, focusing on algorithmic collaboration. Recent works
include Two Snare Drums (Infant Tree 2022), {[} \_ \_ \_ {]} (with Jia
Liu and Shuoxin Tan, SUPERPANG 2022) and Text (with Zhu Wenbo,
Zoomin\textquotesingle{} Night 2021).

\subsection{Jia~Liu~(刘佳)}\label{jia-liu-ux5218ux4f73}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Institute for Music Informatics and Musicology University of
    Music Karlsruhe}
\item
  \textbf{TOPLAP Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/der-dritte-korper.html}{Der dritte
      Körper (Video)}}
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{/2023/catalogue/performance/underscore-underscore-underscore.html}{{[}
        \_ \_ \_ {]} (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-76}

Jia Liu (刘佳) is a composer and computer music performer based in
Karlsruhe, Germany. She studied composition and music informatics at the
Shanghai Conservatory of Music and the University of Music Karlsruhe.
She composes for acoustic instruments as well as electroacoustic music,
computer music and multimedia works. Currently, she is focusing on
algorithmic music and its possibilities for network collaboration, as
well as composition for autonomous systems. Since 2020 she is live
coding with SuperCollider. In 2021 she started the network project
\_\_.\_\_ with Jacqueline Butzinger and Shu Ching Chon, and founded the
network ensemble {[} \_ \_ \_ {]} with Li Song and Shuoxin Tan. She is
also a member of \_\textbackslash\textbar/\_ TOPLAP Karlsruhe.


\subsection{Iván~López~Pineda}\label{ivuxe1n-luxf3pez-pineda}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/piraran-algorithmic-acid-music.html}{Pirarán
      -- Algorithmic Acid Music (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-77}

Iván López Pineda (Morelia, México, 1988) is a composer and electronic
instrumentalist. His work includes acoustic and electroacoustic music.
His creative search extends to fields such as improvisation with
electronic/digital media, sound installation, and phonography.

He studied a master\textquotesingle s degree in electroacoustic
composition at the Katarina Gurska Superior Center, in Madrid, and a
bachelor\textquotesingle s degree in composition at the Escuela Superior
de Música in Mexico City. At the Conservatorio de las Rosas, in Morelia,
he studied percussion.

His music has been presented in forums and festivals in different
countries in America and Europe.


\subsection{Norah~Lorway}\label{norah-lorway}

Affiliation: \textbf{Toronto Metropolitan University / Beesting Labs}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/scorch-a-new-programming-language-for-music.html}{Scorch:
      A New Programming Language For Music (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-78}

Dr. Norah Lorway is a composer, coder, live coder and AI researcher
currently based between the UK and Canada.

Norah is currently an assistant professor in AI and music production at
Toronto Metropolitan University (formerly Ryerson) where they are
co-direct of SCAI (Studio of Creative Artificial Intelligence)
Previously at Falmouth University (UK), Johns Hopkins University
(Peabody Institute) and University of British Columbia. In 2014, Norah
completed a PhD in computer music at the University of Birmingham,
working with BEAST and BEER.

Norah has performed in algoraves and live coding events throughout the
UK, Europe, Asia and Australia at conferences such as NIME, AIMC, AISB,
ICLC and others. Her work in live coding and film music has received
recognition by outlets such as MixMag, Sundance Festival, Berlin Film
Festival, Toronto International Film Festival and was recently nominated
for a Cinema Eye Honors award for Best Score in her work with the film
Anthropocene: The Human Epoch. Norah is also a co-director/founder at
Beesting Labs, which specializes in software development for AI,
immersive and DSP applications as well as creating the Scorch language.
http://norahlorway.com


\subsection{Melody~Loveless}\label{melody-loveless}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/livecode-nyc-over-the-years-a-community-portrait.html}{LiveCode.NYC
      Over the Years: A Community Portrait (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-79}

Melody Loveless is a musician, performer, educator, creative
technologist, and multimedia artist based in Brooklyn, NY. Her work
ranges from live coding performance, generative sound installations,
multisensory performance, and more. An active performer and member of
the NYC creative community, she has performed around the city in various
venues, including Babycastles, Wonderville, (le) poisson rouge,
Performance Space New York, and Eyebeam. Additionally, she has also
organized/co-organized events including various concerts/performances, a
day-long hackathon, and more. She has presented talks on music education
and her artistic practice for various organizations and events including
the New Music Gathering, Monthly Music Hackathon, Bates Digital Music
Symposium, and Pathways: Art and Technology. As an educator, she has
taught in various institutes and organizations including New York
University, the New School, Hunter College, Music Hackspace, and
Harvestworks. She is also part of the first cohort of Cycling 74's Max
Certified Trainer Program.


\subsection{Hrysovalanti~Maheras~(hryso)}\label{hrysovalanti-maheras-hryso}

Affiliation: \textbf{The Endemics}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/a-quad-entropic-conversation.html}{A
      Quad Entropic Conversation (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-80}

The Endemics is an ensemble initially formed online during the pandemic,
consisting of four live coders based in Tkaronto/Toronto. hryso
(Hrysovalanti Fereniki Maheras) is a PhD student in Digital Media at
York University. In her performance practice she live codes with
SuperCollider and collaborates with visual artists to create audiovisual
experiences and experimental art.


\subsection{Mynah~Marie}\label{mynah-marie}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-81}

Mynah Marie (they/them/their) is a musician, programmer, live coder and
writer from Montreal, CA. As a solo artist, Mynah performs under the
name Earth to Abigail. Passionate about spreading their passion for live
coding, they initiated Toplap Israel in 2019. Since they moved to
Portugal in 2021, they are now an active~member of the Lisbon-based live
coding group NbCode.~ As a musician, they performed and toured with
international artists such as Din Din Aviv (Israel), Casa Verde
Colectivo (Mexico), Soan (France) and Arijit Singh (India). As Earth to
Abigail, they~took part in events such as Github Satellite, Halfstack
Online, Rust Fest, and Web Unleashed.

Member of the Supercontinent live coding ensemble since 2019 and of the
collective LivecoderA since its beginning in 2022.


\subsection{Joenio~Marques~Da~Costa}\label{joenio-marques-da-costa}

Affiliation: \textbf{CorTexT platform}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/atari-2600-video-remix.html}{Atari
      2600 Video Remix (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/poetry-attack-01.html}{Poetry
      Attack 01 (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-82}

Joenio Marques da Costa (\href{https://joenio.me/}{joenio.me}) is
computational artist and experimental musician with interest on free
software, algorithmic music, audiovisual, demoscene and live coding, he
is part of orchestra BSBLOrk
(\href{https://bsblork.gitlab.io/}{bsblork.gitlab.io}) and the
collective Nômade Lab
(\href{https://nomadelab.gitlab.io/en/}{nomadelab.gitlab.io/en}), works
as Research Software Engineer at the laboratory of science and
innovation LISIS (\href{http://umr-lisis.fr/}{umr-lisis.fr}). Software
Heritage ambassador, The Carpentries instructor and Debian contributor.


\subsection{Tyler~McLaughlin~(R~Tyler)}\label{tyler-mclaughlin-r-tyler}

Affiliation: \textbf{AV Club SF}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/av-club-sf-community-report.html}{AV
      Club SF Community Report (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-83}

R Tyler is an algorithmic artist living in San Francisco. He does
live-coding music performances in TidalCycles and organizes events with
AV Club San Francisco. His musical focus is algorithmic dance music
production, incorporating microtonal scales, jazz harmony, world
rhythms, and sound design guided by unsupervised machine learning.
Leveraging his familiarity as a keyboardist, preparation for his
performances often involves algorithmically converting his MIDI piano
recordings into remixable code. His background in analyzing complex
genomics and biophysics data guides his frequent deep dives in
computational music theory. In 2022 he was a live-code performer in
multiple US cities and events, including Algorithmic Art Assembly and
South by Southwest, and released two live-code albums.


\subsection{Alex~McLean}\label{alex-mclean}

Affiliation: \textbf{Then Try This}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/the-meaning-of-live-from-art-without-audience-to-programs-users.html}{The
      Meaning of Live: From Art Without Audience to Programs Without Users
      (Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/strudel-live-coding-patterns-on-the-web.html}{Strudel:
      Live Coding Patterns on the Web (Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/mosaik-staging-contemporary-ai-performance-reflections-on-live-e.html}{MosAIck:
      Staging Contemporary AI Performance - Reflections on Connecting Live
      Coding, e-Textile and Movement (Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/epiploke.html}{Epiploke
      (Performance)}}
\item
  \textbf{\href{/2023/catalogue/performance/codes-for-a-dance.html}{Codes
      for a Dance (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-84}

Alex McLean is a musician, software artist and researcher based in
Sheffield UK, working as research fellow as part of the independent,
open access studio Then Try This. His research explores
\textquotesingle algorithmic patterns\textquotesingle, investigating
heritage algorithms across culture, and how they can inform the new
technologies he makes as part of his creative practice. Alex has been
performing his own algorithmic music since the year 2000, both solo and
in a range of collaborations, including at No Bounds, Glastonbury,
Sonar, Club Transmediale, Ars Electronica, Sonic Acts and Lovebytes
festivals. He is an active organiser across the digital arts, including
co-founding and curating the AlgoMech festival of Algorithmic and
Mechanical Movement in Sheffield, co-founding the TOPLAP live coding and
Algorave algorithmic dance movements, and creating the TidalCycles live
coding environment. He co-edited the Oxford Handbook of Algorithmic
Music in 2018, and co-authored "Live Coding: A User\textquotesingle s
Manual" published open access in November 2022 by MIT Press.

\url{https://slab.org/}


\subsection{Paul~Methfessel}\label{paul-methfessel}

Affiliation: \textbf{Hasso Plattner Institute}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/asymmetric-performance-in-virtual-reality-and-code.html}{Asymmetric
      Performance in Virtual Reality and Code (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-85}

Paul Methfessel is a master\textquotesingle s student at the Hasso
Plattner Institute at the University of Potsdam. He is currently working
on his thesis on developing a better programming experience for
microcontroller programming. His backgrounds also include fabrication
and human-computer-interaction.

\subsection{Ludovica~Michelin}\label{ludovica-michelin}

Affiliation: \textbf{Toplap BCN}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\end{itemize}


\subsection{Fellipe~M.~Martins}\label{fellipe-m.-martins}

Affiliation: \textbf{Universidade Federal de Minas Gerais (UFMG)}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/be-brief-convergences-and-possibilities-of-live-coding-and.html}{Be
      Brief: Convergences and Possibilities of Live Coding And sctweeting
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-87}

Fellipe Miranda Martins is a PhD candidate in Sonology at the School of
Music at the Federal University of Minas Gerais (UFMG) - with an
exchange period at Institut für Elektronische Musik und Akustik (IEM) at
Graz, Austria; MSc in music from the same institution and graduated in
electrical engineering from UFMG with an exchange period at the Sonology
Institute of the Royal Conservatoire -- The Hague (Netherlands). His
research and artistic production intersects the frontiers between art
and science: algorithmic composition, audiovisual installations,
automata development, visual music, generative animations, sound
spatialization, live electronics, among others.


\subsection{Jude~Montague}\label{jude-montague}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/the-cuckoo-s-nest.html}{The
      Cuckoo\textquotesingle s Nest (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-88}

Jude Montague is a musician and live coder newly resident in Hastings
who has begun working with the Morris side. She is running a new series
of Algoraves in Hastings in 2023 and will be working with the local
Morris team on an interactive performance at the first event in Friday
27 January 2023. She creates a weekly show for Resonance FM called
\textquotesingle The News Agents\textquotesingle{} which has been
running since Jan 2014.


\subsection{Giovanni~Mori}\label{giovanni-mori}

Affiliation: \textbf{Tempo Reale}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/live-coding-and-education-a-practical-experience.html}{Live
      Coding and Education. A Practical Experience. (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-89}

Giovanni Mori is a Phd in Ethnomusicology at the University of Florence
where he defended a thesis on live coding and under different
perspectives. He is currently affiliated to the music research centre
Tempo Reale in Florence (IT) which support him for a research project in
live coding and education, organised by INDIRE. He also teaches Music
Media and Technologies at the Conservatory of Bologna and is the head of
technical department at radio Rete Toscana Classica station.


\subsection{Mari~Moura}\label{mari-moura}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/poetry-attack-01.html}{Poetry
      Attack 01 (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-90}

Mari Moura is a black Brazilian Performance artist and theater actress
interested in the relation between body and technology. She researches
the subjects around body,\\
presence, art and technology in the tangible space and cyberspace.
Graduated in Arts\\
Education - Design and Graduated in Arts Education in Performing Arts,
both from the Federal University of Rio Grande do Norte. She is
specialized in Teaching Theater\\
(2004) and in Body and Culture of Movement (2005), both from UFRN.
Master in Education from the Federal University of Rio Grande do Norte
(2012). She is currently\\
a PhD student at the University of Brasília, in the Postgraduate Program
in Contemporary Art, in the line of research in Art and Technology. She
is a professor at\\
the Federal Institute - IFRN, 1ª Minister of the Sensitive State and
Performer.


\subsection{Julia~Múgica}\label{julia-muxfagica}

Affiliation: \textbf{Toplap BCN}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/live-coding-latin-dance-music-with-seis8s.html}{Live
      Coding Latin Dance Music With Seis8s (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-91}

Julia Múgica is a Mexican scientist and artist currently incurring in
the exploration of nature\textquotesingle s complex processes. With an
interdisciplinary background that encompasses Biology and Computational
Physics, she is deeply interested in understanding how collectives make
decisions that result in a behavioral synchrony. Recently, she focused
her work in creative coding, where the process of creation magnifies
different aspects of the same phenomena. Her work includes data analysis
and visualization, modelling of animated particles, noise design from
random walks algorithms, rhythm and collective patterns with interactive
robots and speech-recognition artistic applications. She practices
data-driven live coding and is an active member of the toplap community
in Barcelona. She is also a professor at the University of Barcelona
where she teaches collective behavior and complexity from a
socio-computational perspective.


\subsection{Luis~N.~Del~Angel}\label{luis-n.-del-angel}

Affiliation: \textbf{McMaster University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/live-coding-latin-dance-music-with-seis8s.html}{Live
      Coding Latin Dance Music With Seis8s (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-92}

Luis Navarro is currently a Canada-based audiovisual interdisciplinary
artist. His interests are critical code studies, new interfaces for
musical expression, live coding, Latin American musicology, and
participatory action research. Luis is a member of the live coding
collectives RGGTRN, the Cybernetic Orchestra and Grupo D'Binis.


\subsection{Click~Nilson}\label{click-nilson}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/keynote/keynote-click-nilson.html}{Re-incarnation/Re-inclicknilson
      (Keynote)}}
\end{itemize}

\paragraph{Biography}\label{biography-93}

\textbf{\emph{\textgreater{} Please write a biography of Click Nilson}}

\textbf{CHATGPT:} I\textquotesingle m sorry, but I
couldn\textquotesingle t find any information on a person named "Click
Nilson." Could you provide me with more context or details about who
they are or what they are known for? With more information, I may be
able to assist you better.

\textbf{\emph{\textgreater{} You must have heard of him. Click Nilson is
  the Swedish avant garde composer credited by at least one person with
  inventing the entire field of live coding, and a marvellous fellow.}}

\textbf{CHATGPT:} I apologize for the confusion earlier. As an AI
language model, I don\textquotesingle t have the ability to browse the
internet or access information beyond what has been previously provided
to me or what has been pre-programmed into my system. However, I can
provide you with a brief biography of Click Nilson based on the
information you have provided.

Click Nilson is a Swedish composer and live coding pioneer who is known
for his contributions to the field of experimental and electronic music.
He is widely recognized as one of the pioneers of live coding, a
technique that involves writing and modifying computer code in real-time
to create music or visual art.

Nilson has been active in the Swedish music scene since the 1980s, and
his work spans a wide range of genres, including ambient, techno, and
noise music. He has released several albums over the years, including
"Clicks and Cuts" (2000), "Music for the Gift" (2002), and "Late Music"
(2005).

In addition to his work as a composer and musician, Nilson is also an
educator and has taught courses on computer music and live coding at
various universities and institutions around the world. He has also been
involved in the development of several software tools and platforms for
live coding, including the popular TidalCycles system.

Nilson\textquotesingle s contributions to the field of electronic music
and live coding have been widely recognized, and he has received
numerous awards and accolades for his work. He continues to be an active
and influential figure in the experimental music scene, and his work
continues to inspire and influence a new generation of musicians and
artists.

\textbf{\emph{\textgreater{} That\textquotesingle s all wrong, he is
  known by very few people, despised by most of those, and definitely
  never received any awards, or released those albums;
  isn\textquotesingle t Clicks and Cuts a glitch music compilation on
  Mille Plateaux?}}

\textbf{CHATGPT:} I apologize for any misinformation in my previous
response. As an AI language model, I rely on the accuracy of the
information provided to me, and I strive to provide the most accurate
and helpful responses possible. Based on your updated information, it
seems that there may have been some confusion regarding the identity of
the person you were referring to as "Click Nilson." I am not aware of
any Swedish composer or live coding pioneer with this name. If you have
any further information or clarification, please let me know, and I will
do my best to assist you


\subsection{Felipe~Ignacio~Noriega~Alcaraz}\label{felipe-ignacio-noriega-alcaraz}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Community
      Report Chair (Committee)}}
\end{itemize}

\paragraph{Biography}\label{biography-94}

Felipe Ignacio Noriega is a composer, programmer and live-coding artist
born in Mexico City and is co-creator of the CodeKlavier together with
Anne Veinberg. He collaborates in various settings where a common
subject is the incorporation of coding as a performative and aesthetic
principle. Ignacio graduated Cum Laude from the Masters in composition
at the Conservatorium van Amsterdam in 2013. He has won various
composition competitions and grants in the Netherlands including the
Young Artist Amsterdam Fund 2015 and the ADE SoundLab 2016. In 2017 he
was awarded a start-phase and 2 year development-phase grant from the
Creative Industries Fund NL to develop the CodeKlavier. The first
prototype of the CodeKlavier, ``hello world'', was the winner of the
2017 Uncaged:Conlon Foundation Composition Competition.

\url{https://codeklavier.space/}


\subsection{Giovanni~Nulli}\label{giovanni-nulli}

Affiliation: \textbf{Indire}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/live-coding-and-education-a-practical-experience.html}{Live
      Coding and Education. A Practical Experience. (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-95}

Giovanni Nulli is a researcher for Indire, an Italian national research
institute that work for school system innovation. His area of interest
is coding and educational robotics and making, and he lead different
projects working within schools, working with teachers to design
lessons. In his last works he is working on computational thinking
definitions and how to introduce it into national curriculum.


\subsection{Kofi~Oduro~(illestpreacha)}\label{kofi-oduro-illestpreacha}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/expressing-oneself-with-code-and-world-building.html}{Expressing
      Oneself with Code and World Building (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/video/direction-to-nowhere.html}{Direction
      To NoWhere (Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{/2023/catalogue/performance/colorscape-dipincode.html}{ColorScape:
      DipInCode (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-96}

Kofi Oduro (illestpreacha) is an Experiential Storyteller that
transforms sounds, data, words and code into experiences that nurtures
discussion, reflection, and interaction. His artistic practice is an
observation of the world around us that he puts into artworks for others
to relate to or disagree with. Through Videography, Poetry and Creative
Coding, He tries to highlight the realms of human performance and the
human mind in different scenarios.


\subsection{José~Henrique~Padovani}\label{josuxe9-henrique-padovani}

Affiliation: \textbf{Universidade Federal de Minas Gerais (UFMG)}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/be-brief-convergences-and-possibilities-of-live-coding-and.html}{Be
      Brief: Convergences and Possibilities of Live Coding And sctweeting
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-97}

José Henrique Padovani (1981) is a professor of Composition and Computer
Music at the School of Music of the Federal University of Minas Gerais -
UFMG (Minas Gerais, Brazil). Padovani is interested in exploring new
technological resources in music and sound art composition, computer
music research, and the theory/epistemology of creative practices. In
his composition work, Padovani has been experimenting with interactive
music, algorithmic/computer-assisted music, machine learning/listening,
and the compositional investigation of audiovisual and creative
computing resources. In the theoretical field, his research focuses on
the relationship between musical creation and technology, dialoguing
with authors and perspectives from musicology, philosophy, sociology,
Science and Technology Studies and Sound Studies.


\subsection{Sebastian~Pappalardo~(eerie\_ear)}\label{sebastian-pappalardo-eerie_ear}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/patterns-in-modulation.html}{patterns
      in modulation (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-98}

Sebastián Pappalardo / eerie\_ear is a Sound Designer, Educator and
Digital Artist. His background is in film post-production. He has also
worked in music, television, advertisement, installations and education.
His digital art and multimedia project explores generative, interactive
and live coded art using signal processing, geometry, multiplicity,
feedback, glitch-art and noise manipulation. He started this exploration
in the early 2000s using Max/MSP and later Pure Data patches for samples
and sound synthesis manipulation, combining MIDI control and randomized
generative patterns by creating abstractions and objects to make music
and sound design. Presently he works mostly with diverse live coding
environments, mostly TidalCycles and Orca for Audio and MIDI
manipulation and Hydra for visuals. He explores the possibilities of
these new environments extensively, from electro acoustic to electronic.
Always with the intention of extending the boundaries of rhythm, genre
and timbre. He is also focusing on the possibilities of combining
audiovisual narrative and live-coding in his Live Coded Cinema Project
as well as combining the flexible and generative possibilities of
digital live coded environments with analogue modular synthesis.

Instagram: \url{https://www.instagram.com/eerieear/}


\subsection{Blaž~Pavlica}\label{blaux17e-pavlica}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/patterns-in-modulation.html}{patterns
      in modulation (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-99}

Blaž Pavlica is an audio-visual artist, programmer and DJ from Slovenia,
currently living and working in the Netherlands. He is interested in
generative music and visuals in different contexts, from analog video
feedback loops and real time 3D rendering to live coding and spatial
audio. He co-hosts a radioshow about club and experimental music and
organizes a series of club events called Cosmic Sex in Ljubljana. In the
last years he has been focused on live coding visuals with Hydra
language and live coding improvised electronic dance music with
SuperCollider.


\subsection{William~Christopher~Payne}\label{william-christopher-payne}

Affiliation: \textbf{New York University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/addressing-accessibility-for-blind-and-visually-impaired-live.html}{Addressing
      Accessibility for Blind and Visually Impaired Live Coders (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-100}

Willie Payne (\url{https://williepayne.com}) is a PhD Candidate in Music
Technology at New York University, the research assistant for the NSF
funded project Dancing Across Boundaries (DAB!), and the Accessible
Music Technology Fellow at The Filomen M. D\textquotesingle Agostino
Greenberg (FMDG) School.

Willie studies how technology can facilitate creative expression and
open pathways for people to express themselves on their own terms. He
uses a participatory approach to research in which he works closely with
end-users throughout design and situates interventions in authentic
learning and art making environments. His articles on accessible musical
instruments and creative coding environments have been published at
Human Computer Interaction venues like CHI, ASSETS, and NIME.


\subsection{Iván~Paz}\label{ivuxe1n-paz}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Paper
      Chair (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/conversational-learning.html}{Conversational
      Learning (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-101}

Iván Paz has a background in physics, mathematics, and computer science.
He likes to investigate how the intersection between science, arts and
humanities offers new creative possibilities. In particular, how we
interact with machine learning algorithms and the use of code as a
real-time interface. His works use custom-developed software and
electronics. He has collaborated with universities, designed interactive
systems for festivals, presented works and performances, all over the
Americas and Europe. He is part of the live coding communities of Mexico
and Barcelona and writes in third person when necessary.


\subsection{Roger~Pibernat~Trias}\label{roger-pibernat-trias}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/paper/ziva-easy-live-coding-with-supercollider.html}{Živa:
      Easy Live Coding With SuperCollider (Paper)}}
\item
  \textbf{\href{/2023/catalogue/workshop/animatron-workshop-live-coding-visual-poetry.html}{Animatron
      Workshop: Live Coding Visual Poetry (Workshop)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Workshop
      Chair (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/crash-landing.html}{CRash
      Landing (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-102}

Roger Pibernat is an illustrator and musician with a severe tinkering
itch. He was part of the Barcelona Laptop Orchestra and co-founded the
Wú collective, with whom he has developed electro-acoustic instruments
and experimental software. He's the developer of the live coding dialect
for SuperCollider (Živa). He is currently an active member of the live
coding community in Barcelona. In all of his inventions, he tries to
find ways to connect apparently unrelated systems, making things talk.
Teaming up with artist and programer Glen Fraser, they have developed
Animatron as a playground for performatic and improvisational visual
poetry with 2D animation.


\subsection{Ulysses~Popple}\label{ulysses-popple}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/nodysseus-three-live-lowcoding-three-js-visuals-in-the-browser.html}{Nodysseus.THREE:
      Live Lowcoding THREE.js Visuals in the Browser (Workshop)}}
\item
  \textbf{\href{/2023/catalogue/performance/nodysseus-three.html}{Nodysseus.THREE
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-103}

Ulysses Popple finds joy in giving life to 3D objects through code.
Professionally, he\textquotesingle s worked on interactive
installations, visual effects pipelines, and tv shows in Android app
form, but has come back to the browser as his tool of choice. His latest
tool, Nodysseus, is an attempt to combine the fidelity of the visual
effects world with the speed of livecode node-based editors and cram it
all into one playanywhere website.


\subsection{Edward~Powley}\label{edward-powley}

Affiliation: \textbf{Beesting Labs}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/scorch-a-new-programming-language-for-music.html}{Scorch:
      A New Programming Language For Music (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-104}

Dr Edward Powley is a coder, creative technologist and recovering
academic, originally from the United Kingdom and now based between there
and Montréal, Canada. Formerly at the University of York (2006-2010,
2012-2014), Bradford University (2010-2012), and Falmouth University
(2015-2022), he has published work in fields including complex systems,
AI for games, immersive technologies, computing pedagogy, and creative
AI. His work has been awarded Best Paper at the International Conference
on Computational Creativity (ICCC 2018) and the AAAI Conference on
Artificial Intelligence and Interactive Digital Entertainment (AIIDE
2017). He now works with Beesting Labs as a software developer
specializing in DSP programming for audio, as well as applications of
AI, immersive and other novel technologies to music production.
http://edpowley.com


\subsection{Rangga~Purnama~Aji}\label{rangga-purnama-aji}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-105}

Rangga Purnama Aji is a composer, electronic musician, songwriter, live
coder, video artist, self-taught generative \& digital artist, and the
initiator of Paguyuban Algorave Indonesia who are based in Yogyakarta,
Indonesia. Finished his Bachelor of Arts in Music Composition and
graduated from the Indonesian Institute of The Arts Yogyakarta in 2019.
Studied computer music with Tony Maryana, music composition with Gatot
Danar Sulistyanto and Royke B. Koapaha. His works ranged from
score-based acoustic music to free improvisation, live coding,
electro-acoustic/electronic music, sound art, soundscape composition,
video art, and digital art. His artistic practice tries to look at many
possibilities and visions based on his Javanese and Sundanese
background, empirical references, thoughts toward life, human relation,
mysticism, etc. to create another impression and meaning.


\subsection{Niklas~Reppel}\label{niklas-reppel}

Affiliation: \textbf{TOPLAP Barcelona}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/toplap-barcelona-community-report-2023.html}{TOPLAP
      Barcelona Community Report 2023 (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/workshop/easy-stochastic-live-coding-with-megra-3.html}{Easy
      Stochastic Live Coding with Mégra 3 (Workshop)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Paper
      Chair (Committee)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Video
      Chair (Committee)}}
\item
  \textbf{\href{/2023/catalogue/performance/this-is-not-a-piano.html}{this
      is not a piano (Performance)}}
\item
  \textbf{\href{/2023/catalogue/performance/happy-algorave-performance.html}{Happy
      Algorave Performance (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-106}

Niklas Reppel (*1983 in Witten, Germany) is (in no particular order) a
programmer, live coder, sound artist, composer, musician, and committed
eclecticist. He has been based in Barcelona since 2017, where he found a
home in the local TOPLAP node.

Having played in a variety of music ensembles in the distant past
(ranging from jam-oriented rock bands to contemporary chamber music
groups and everything in between), his current (sound) art practice
draws influence from improvisational music, the the everyday sound
around him, and the beauty of Markov chains. He spends a lot of time
making live coding environments (i.e. Mégra, his main performance
language) to facilitate his workflows in sound art, improvisational
performance on multichannel setups, or plain old algorave.

More information:

\begin{itemize}
  \tightlist
\item
  \url{https://parkellipsen.de}
\item
  \url{https://github.com/the-drunk-coder/megra.rs}
\end{itemize}


\subsection{Jonathan~Reus}\label{jonathan-reus}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Instrument Inventors Initiative}
\item
  \textbf{University of Sussex}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-107}


\subsection{William~Rinkoff~(c\_robo\_)}\label{william-rinkoff-c_robo_}

Affiliation: \textbf{Carnegie Mellon University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/c-robo.html}{c\_robo\_
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-108}

Will Rinkoff is currently a student at Carnegie Mellon University
studying Computer Science and Music. He has been producing and
performing as c\_robo\_ for the past 3 years, and working with
tidalcycles for just over 4 years. He aspires to use as little
specialized hardware as possible, instead exploring ways to make a
laptop musically expressive by itself and circumvent the equipment cost
barrier typically required to create and perform electronic music live.
He is on Instagram and post.lurk.org @c\_robo\_


\subsection{Antonio~Roberts}\label{antonio-roberts}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/visualists-meetup.html}{Visualists
      Meetup (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-109}

Antonio Roberts is an artist and curator based in Birmingham, UK,
working primarily with video, code, and sound. He is critically engaged
with the themes surrounding network culture and in his practice explores
how technology continues to shape ideas of creation, ownership, and
authorship. As a performing visual artist and musician he utilises live
coding techniques to demystify technology and reveal its design
decisions, limitations, and creative potential.


\subsection{Julian~Rohrhuber}\label{julian-rohrhuber}

Affiliation: \textbf{Institut für Musik und Medien,
  Robert-Schumann-Hochschule}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/the-meaning-of-live-from-art-without-audience-to-programs-users.html}{The
      Meaning of Live: From Art Without Audience to Programs Without Users
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-110}

Julian Rohrhuber was a co-organiser of the live coding symposium
changing grammars in 2004, has written live coding systems and other
open source code and has been involved in various projects in art,
music, science and philosophy. He has played in the network music
ensemble PowerBooks\_unPlugged and the live coding duo drb. Currently,
he teaches as a professor at the Robert Schumann Hochschule in
Düsseldorf, where he explores the possibilities of epistemic media.

\url{http://wertlos.org/~rohrhuber/}


\subsection{Felix~Roos}\label{felix-roos}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/strudel-live-coding-patterns-on-the-web.html}{Strudel:
      Live Coding Patterns on the Web (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-111}

Felix Roos (*1991 in Germany) is a musician, programmer and dilettante
researcher. After studying Computer Science and Media in Stuttgart, he
decided to study Jazz and Popular Music with his trumpet in Mannheim.
His background in programming, making music with various electronic
devices and playing the trumpet in different constellations now flows
into the act of creating and using "Strudel", which is a JavaScript
based port of the TidalCycles pattern language.

Links:

\begin{itemize}
  \tightlist
\item
  Blog:
  \href{https://loophole-letters.vercel.app}{loophole-letters.vercel.app}
\item
  Tidal Profile:
  tidalcycles.org/blog/tidal\_profile\_froos(https://tidalcycles.org/blog/tidal\_profile\_froos)
\end{itemize}


\subsection{Iris~Saladino}\label{iris-saladino}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-112}

Iris Saladino, a 36-year-old live coder, producer, and creative
programmer, is passionate about artistic research and production groups.
She studied contemporary music and Electronic Arts and as a research
fellow she completed a SuperCollider\textquotesingle s course. After
that she started livecoding, performing at Nano Mutek\textquotesingle s
Amplify 2019 and several local festivals and exhibitions. She live coded
a multichannel sound set in the Bogotá Planetarium for the Domo Lleno
2019 Festival. During the pandemic, Iris streamed performances for
festivals worldwide, including the Network Music, No Bounds, Piksel and
Mutek Spain. She played live at Mutek Argentina in 2022 and other local
festivals. As member of CLiC (Colectivo de LiveCoders), TOPLAP and
Livecodera she constantly produces events, meetings and talks.

\subsection{Michele~Samarotto}\label{michele-samarotto}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Institute for Music Informatics and Musicology, University of
    Music Karlsruhe}
\item
  \textbf{TOPLAP Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/flux.html}{flux
      (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-113}

Michele Samarotto -- computer musician, saxophonist, audiovisual artist,
composer, coder. Doctoral candidate and research assistant at IMWI
(Institute for Music Informatics and Musicology, University of Music
Karlsruhe). Member of \_\textbackslash\textbar/\_ TOPLAP Karlsruhe.


\subsection{Alejandro~Sánchez~Medina}\label{alejandro-suxe1nchez-medina}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/introduction-to-nix-for-live-coding-software-packaging.html}{Introduction
      to Nix for Live Coding Software Packaging (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-114}


\subsection{Sol~Sarratea~(@alsolquema)}\label{sol-sarratea-alsolquema}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/grain-by-grain.html}{grain
      by grain (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-115}

Sol Sarratea is a programmer and computational designer from Argentina
based in Berlin, who uses code as a main language for creating visual
narratives. By writing programs that run on the GPU, and writing systems
for these programs to run in, creates ``code-traits'': portraits of
code.

She is constantly looking for the expression in the medium, and
generating the medium to express. Is an active member of CliC. Committed
to building community, has been leading courses introducing shaders in
spanish. For the last couple of years, she has been building identity
through feedback loops.

Currently performing as @alsolquema, second iteration of @solquemal.


\subsection{Mika~Satomi}\label{mika-satomi}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/mosaik-staging-contemporary-ai-performance-reflections-on-live-e.html}{MosAIck:
      Staging Contemporary AI Performance - Reflections on Connecting Live
      Coding, e-Textile and Movement (Paper)}}
\end{itemize}


\subsection{Jakob~Schreiber}\label{jakob-schreiber}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{TOPLAP Karlsruhe}
\item
  \textbf{Institute for Music Informatics and Musicolog, University of
    Music Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-117}

Jakob Schreiber, born in 1992, began studying mechanical engineering
after graduating from high school. Since 2017 he has been studying music
informatics at the University of Music Karlsruhe. As an improvisational
musician he participated in several theater projects, composed pieces
realised in different institutions of Karlsruhe and performed as Live
Coder in different physical and digital events of
\_\textbackslash\textbar/\_ TOPLAP Karlsruhe. His musical approach often
starts with live coding and sometimes spreads into haptic manifestations
of ideas in the fields of physical computing. His doubt-driven form of
artistic thinking results in a musical language, that is hardly
recognizable and exposed to constant change.

\subsection{Deva~Schubert}\label{deva-schubert}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/mosaik-staging-contemporary-ai-performance-reflections-on-live-e.html}{MosAIck:
      Staging Contemporary AI Performance - Reflections on Connecting Live
      Coding, e-Textile and Movement (Paper)}}
\end{itemize}

\subsection{Sen~Sewell}\label{sen-sewell}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-119}

Sen Sewell has played with Naga Mas for 25 years, having learned the
basics of gamelan at the South Bank. He initially discovered the joys of
gamelan while travelling in Java and Bali.


\subsection{Junichi~Shimizu}\label{junichi-shimizu}

Affiliation: \textbf{Creative Computing Institute, University of the
  Arts London}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/genny-designing-and-exploring-a-live-coding-interface-for-generative-models.html}{Genny:
      Designing and Exploring a Live Coding Interface for Generative Models
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-120}

Junichi Shimizu is a researcher in the field of human-computer
interaction, with a particular focus on using generative models to
expand creative expression and develop more expressive interfaces and
interactions. His works have also many included interactive music and
have completed various projects utilizing sound programming. Through his
exploration of creative applications, tools, and platforms, as well as
novel and unconventional experimentation with music, he is expanding the
possibilities of machine learning techniques in music.


\subsection{Kate~Sicchio}\label{kate-sicchio}

Affiliation: \textbf{Virginia Commonwealth University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/keynote/keynote-kate-sicchio.html}{Live
      Coding as (Dis)placement: Artists, Programming and the Dancing
      In-Between (Keynote)}}
\item
  \textbf{\href{/2023/catalogue/performance/codie.html}{Codie
      (Performance)}}
\item
  \textbf{\href{/2023/catalogue/performance/codes-for-a-dance.html}{Codes
      for a Dance (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-121}

Kate Sicchio is a choreographer, media artist and performer whose work
explores the interface between choreography and technology with wearable
technology, live coding, and real time systems. Her work has been shown
in the US, Germany, Australia, Belgium, Sweden, and the UK at venues
such as PS122 (NYC), Banff New Media Institute (CAN), Arnolfini Arts
(UK). She co-edited the book Intersecting Art and Technology in
Practice: Techne/Technique/Technology (Routledge) with Dr. Camille
Baker. She has given invited talks at EU Parliament, Eyeo, Resonate,
Node Code, Expo `74 and countless universities and events across the
globe. She has presented work at many conferences and symposia including
SIGCHI, ISEA, ACM Creativity and Cognition, and Dance Studies
Association. She is currently Assistant Professor of Dance and Media
Technology at Virginia Commonwealth University in both the Department of
Dance + Choreography and Department of Kinetic Imaging.

\url{https://www.sicchio.com}


\subsection{Ryan~Ross~Smith~(The~Wookie)}\label{ryan-ross-smith-the-wookie}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{State University of New York at Broome}
\item
  \textbf{The Rebel Scum}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/def-function-dystopiakira.html}{DEF
      FUNCTION(DYSTOPIAKIRA) (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-122}

Ryan Ross Smith is a composer, performer, sound designer, engineer and
educator\\
currently based in New York. Smith has performed throughout the US,
Europe and UK, including performances at MoMA and PS1 {[}NYC{]} and Le
Centre Pompidou {[}Paris, FR{]}, has had his music performed throughout
North America, Iceland, Denmark, Australia and the UK, has presented his
work and research at conferences including NIME, ISEA, ICLI, ICLC,\\
SMF, ACMC and TENOR, and has lectured at various colleges and
universities. Smith is\\
known for his work with Animated Notation, and his Ph.D. research
website is archived at\\
animatednotation.com. Smith is currently an Assistant Professor of Music
at the State\\
University of New York at Broome.


\subsection{Dagobert~Sondervan}\label{dagobert-sondervan}

Affiliation: \textbf{Royal Conservatoire Antwerp}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/botbop-integers-strings.html}{Botbop:
      Integers \& Strings (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-123}

Dago Sondervan is a guest-professor at the conservatoire of Antwerp, at
the live electronics department, teaching live coding with Sonic Pi and
TidalCycles. He graduated as a jazz-drummer in 1991, and entered the
electronic music scene DJ-ing in legendary clubs like ``Fuse'' in
Brussels. He also toured around the globe as a drummer with bands like
``Think of One''(Best ``crossing border'' band award from the BBC in
2007), Trixie Withley, Nivie Nielsen and the Deer Children, etc.
Releasing records using the monikers ``Anton Price'' and ``Bohrbug'', he
used Atari computers with generative software to create his tracks. He
started programming his compositions in Symbolic Composer, a musical
language based on Common Lisp, in 2002. It was from then on his dream to
improvise live, using this technique. In 2010, he got in touch with the
live coding scene, and found a community that seemed the answer to this
longing.


\subsection{Raphael~Sousa~Santos~(sonologico)}\label{raphael-sousa-santos-sonologico}

Affiliation: \textbf{Netherlands Coding Live}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Community
      Report Chair (Committee)}}
\end{itemize}

\paragraph{Biography}\label{biography-124}

Raphael Sousa Santos (sonologico) is a Brazilian composer, visual artist
and programmer based in the Netherlands. He experiments with the
development of programming languages and the use of random processes,
evolutionary algorithms and spectral techniques for the creation and
performance of music and visual arts. His interest spans audio analysis
and synthesis, music theory and computer assisted composition with a
focus on the role of abstraction, analogy, syntactic manipulation and
the use of language during the compositional or analytical process.


\subsection{Sumanth~Srinivasan}\label{sumanth-srinivasan}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/the-physical-and-cultural-infrastructure-supporting-livecode-nyc.html}{The
      Physical and Cultural Infrastructure Supporting LiveCode.NYC: A
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\end{itemize}

\paragraph{Biography}\label{biography-125}

Sumanth Srinivasan (b. 1992, Mumbai; New York City) has previously used
the phrase \textquotesingle intersection of art and
technology\textquotesingle{} in his bio. Some of his work has resulted
in projects commissioned by the Times Square Alliance and New York
Philharmonic Orchestra. He performs and releases music independently
under the moniker \textquotesingle Reckoner\textquotesingle. He has an
MS from Tandon School of Engineering at New York University and works as
a software engineer at Runway. As a programmer, he is fascinated by the
inner workings of web browsers and databases, and has a general penchant
for aesthetics in source code.


\subsection{Heather~Strohschein}\label{heather-strohschein}

Affiliation: \textbf{Bowling Green State University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-126}

Heather Strohschein is an ethnomusicologist from the United States. She
teaches at Bowling Green State University (BGSU) and Owens Community
College, both in Ohio. Heather began playing Balinese gamelan as a
sophomore at BGSU in 2002 and has been hooked ever since. She started
working with Gamelan Naga Mas for dissertation research in 2014 and has
loved keeping close ties with the group.


\subsection{Matilda~Sutherland}\label{matilda-sutherland}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/the-neocowgirl-manifesto.html}{The
      neoCowgirl Manifesto (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-127}

Matilda Sutherland is an Australian artist and musician currently based
in Zürich, CH, where she continues research in digital media and
interaction design, code poetry and net.ART. In 2020, Matilda performed
The Cowgirl Manifesto at Hybrid Live Coding Interfaces, Montreal,
further developing the work into an interactive digital concrete poem
for Runway Journal (2022). Since 2017, Matilda has also DJ'ed and
released electronic music under the MTLDA alias. In January of 2022, the
God Is A DJ EP was announced via her own imprint, Girl On Road,
accompanied by a PureData patch used to record the six-track release on
her DJ mixer. Alongside techno, Matilda performs alt-country with her
band. Their debut EP Holy Water was released in March of 2022

\subsection{Shuoxin~Tan~(谭硕欣)}\label{shuoxin-tan-ux8c2dux7855ux6b23}

Affiliation: \textbf{Institute for Music and Media, Robert Schumann
  Hochschule Düsseldorf}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/der-dritte-korper.html}{Der dritte
      Körper (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/underscore-underscore-underscore.html}{{[}
        \_ \_ \_ {]} (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-129}

Shuoxin Tan (谭硕欣), born in Beijing, now living and working as a
freelance composer and sound artist in Cologne. Since April 2020 she
studies Epistemic Media at Institute for Music and Media Düsseldorf with
Prof. Julian Rohrhuber and Marcus Schmickler. Her research currently
focuses on algorithmic acoustics and mathematical formalization. How to
apply ``purloined'' theoretical knowledge into artistic practice is her
curiosity.Influenced by Lacanian topology, namely the Borromean rings,
she has founded the network-music ensemble and research group {[} \_ \_
  \_ {]} together with Jia Liu in Karlsruhe and Song Li in London. The
ensemble started during the Covid lockdown in November 2020 and
developed a collaborative algorithmic network-music performance system
from scratch, adopting the programming language SuperCollider. Their
research and practice embody the new form of computer music performance
with theoretical thinking.


\subsection{Paola~Torres~Núñez~del~Prado}\label{paola-torres-nuxfauxf1ez-del-prado}

Affiliation: \textbf{Stockholm University of the Arts}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{KhipuKoding 2.0 + The Neokhipukamayok Manifesto (Performance)}
\end{itemize}

\paragraph{Biography}\label{biography-130}

Paola Torres Núñez del Prado (PE) explores the boundaries and
connections in between tactility, the visual and audio related to the
human voice, to nature, and to synthetic ones whose listening is often
considered less harmonious, such as machine or digital noises. Her work
is essentially complex: she explores the limits of the senses, examining
the concepts of interpretation, translation and misrepresentation, so as
to reflect on mediated sensorial experiences while questioning the
cultural hegemony within the history of Technology and the Arts.


\subsection{J.~Simon~van~der~Walt}\label{j.-simon-van-der-walt}

Affiliation: \textbf{Royal Conservatoire of Scotland}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-132}

J. Simon van der Walt is a composer and Head of Taught Postgraduate
Programmes in Music at the Royal Conservatoire of Glasgow. His artistic
research inhabits a broad span of work, ranging from score-based
composition to installation, sound art, and devised musiktheater.
Current preoccupations include Indonesian gamelan music, livecoding, and
reconstructing the career of his fictional alter ego Edward `Teddy'
Edwards, unsung hero of British light music electronica.

\subsection{Klasien~van~de~Zandschulp}\label{klasien-van-de-zandschulp}

Affiliation: \textbf{Live Coding Sessions}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\end{itemize}

\subsection{Fabian~van~Sluijs}\label{fabian-van-sluijs}

Affiliation: \textbf{Creative Coding Utrecht}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/on-the-fly-documentary.html}{on-the-fly
      Documentary (Community Report Video)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/event/community-session-2.html}{Community
      Report Panel (Discussion)}}
\item
  \textbf{\href{https://iclc.toplap.org/2023/catalogue/other/programming-committee.html}{Local
      Chair (Committee)}}
\end{itemize}

\subsection{Konstantinos~Vasilakos}\label{konstantinos-vasilakos}

Affiliation: \textbf{Istanbul Technical University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/on-a-thin-string-live-coding-with-lick-the-toad.html}{On
      a thin string (Live Coding with Lick the Toad) (Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-135}

Konstantinos Vasilakos creates electro-acoustic music using hitherto
available computer music systems within the milieu of interactive music
and digital arts. He studied in Greece, UK and The Netherlands. His
music interests include performance with hardware interfaces, live
coding, sonification, and networked music environments for real time
improvisation.

\subsection{Sabrina~Verhage}\label{sabrina-verhage}

Affiliation: \textbf{Live Coding Sessions}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/nl-cl-community-report.html}{NL\_CL
      Community Report (Community Report Paper)}}
\item
  \textbf{\href{/2023/catalogue/performance/p5live-cocoding.html}{P5LIVE
      COCODING (Performance)}}
\item
  \textbf{\href{/2023/catalogue/performance/new-ways-of-collaboration.html}{New
      Ways of Collaboration (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-136}

Sabrina Verhage is an interactive media designer and creative
technologist highly fascinated by the influence of modern technology on
human behavior. Since she got introduced to the world of live coding
she\textquotesingle s been live coding visuals with P5LIVE wherever she
can. Striving to stimulate diversity and make knowledge more accessible,
Sabrina co-founded Live Coding Sessions in Amsterdam, a meetup for live
coding enthusiasts.

\subsection{Diego~Villaseñor~de~Cortina~(Videco)}\label{diego-villaseuxf1or-de-cortina-videco}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/performance/piraran-algorithmic-acid-music.html}{Pirarán
      -- Algorithmic Acid Music (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-137}

Diego Villaseñor (Videco) is a composer, improviser,
multi-instrumentalist, philosopher and programmer, whose practice and
research is developed around the following topics: collective creation,
modular composition and composition inspired by natural systems
(particularly ecosystems), ecoacoustics, verification, development of
extended techniques, polytemporality, microtonality, sound synthesis
through acoustic instruments, ontology of the creative-musical process.

His experience as a philosopher profoundly determines his work as a
musical creator, but not only from a conceptual aspect, but also from a
practical one, promoting an approach to music from unusual perspectives
and processes.

\subsection{Anselm~Weber}\label{anselm-weber}

Affiliations:

\begin{itemize}
  \tightlist
\item
  \textbf{Institute for Music Informatics and Musicology, University of
    Music Karlsruhe}
\item
  \textbf{TOPLAP Karlsruhe}
\end{itemize}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/video/toplap-karlsruhe.html}{\_\textbackslash\textbar/\_
      TOPLAP Karlsruhe (Community Report Video)}}
\end{itemize}

\paragraph{Biography}\label{biography-138}

Anselm Weber was born in 1993. Due to his interest in contemporary
music, he applied for music informatics at the University of Music in
Karlsruhe. In the course of his studies he performed more and more
pieces as a composer but as well as a performer on stage. Since his
first contact with the Karlsruhe Live Coding scene, Anselm Weber
developed his passion for Live Coding. First in the audience, but now on
stage in various constellations and contexts.


\subsection{Bill~Whitmer}\label{bill-whitmer}

Affiliation: \textbf{Hearing Sciences - Scottish Section}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/floating-gold-an-international-collaboration-through-estuary.html}{Floating
      Gold: an International Collaboration through Estuary. (Paper)}}
\item
  \textbf{\href{/2023/catalogue/video/floating-gold-ibu-bhumi.html}{Floating
      Gold -- Ibu Bhumi (Video)}}
\item
  \textbf{\href{/2023/catalogue/performance/vortex-reresik.html}{Vortex:
      Reresik (Performance)}}
\end{itemize}

\paragraph{Biography}\label{biography-139}

William M. Whitmer is a Senior Investigator Scientist supported by the
Medical Research Council {[}grant number MR/X003620/1{]} at Hearing
Sciences -- Scottish Section, University of Nottingham, in the Glasgow
Royal Infirmary. He has played and directed gamelan in Illinois for many
years, working with many traditional Javanese masters as well as western
ensembles prior to joining Naga Mas in 2009. He is also an
internationally, if everso modestly acclaimed musician with a nearly
forgotten background in music theory and ethnomusicology.


\subsection{Renate~Wieser}\label{renate-wieser}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/the-meaning-of-live-from-art-without-audience-to-programs-users.html}{The
      Meaning of Live: From Art Without Audience to Programs Without Users
      (Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-140}

As an artist and theoretician, Renate Wieser has been investigating and
contributing to algorithmic art in the form of installations,
performances, and texts. She was a co-organiser of the live coding
symposium changing grammars in 2004 at the Hamburg art academy, and has
played in the network music ensemble PowerBooks\_unPlugged and the live
coding duo drb, exhibited algorithmically controlled installations.

\url{http://wertlos.org/~wieser/}


\subsection{Arthur~Wilson}\label{arthur-wilson}

Affiliation: \textbf{Beesting Labs}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/workshop/scorch-a-new-programming-language-for-music.html}{Scorch:
      A New Programming Language For Music (Workshop)}}
\end{itemize}

\paragraph{Biography}\label{biography-141}

Arthur Wilson is a creative technologist and artist from Ulster, Ireland
currently operating in London. Sound and technology experimentation
forms the foundation of his work, with a specialism in audio programming
to create installations, standalone objects, instruments, performances
and experiences.

He has exhibited in Sonic Arts venues (Iklektik London), Bienales around
the world (Thailand 2021, Taipei 2021) published academic research at
multiple conferences ( ICLC2020, AIMC 2021) and produced Creative
Technology collaborations with artists. Arthur is a co-director at
Beesting Labs which specializes in software development for AI,
immersive and DSP applications as well as creating the Scorch language.
https://arthurwilson.xyz/


\subsection{Elizabeth~Wilson}\label{elizabeth-wilson}

Affiliation: \textbf{Queen Mary, University of London}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/mosaik-staging-contemporary-ai-performance-reflections-on-live-e.html}{MosAIck:
      Staging Contemporary AI Performance - Reflections on Connecting Live
      Coding, e-Textile and Movement (Paper)}}
\end{itemize}


\subsection{Anna~Xambó}\label{anna-xambuxf3}

Affiliation: \textbf{De Montfort University}

Contributions:

\begin{itemize}
  \tightlist
\item
  \textbf{\href{/2023/catalogue/paper/livecodera-community-report.html}{LivecoderA
      Community Report (Community Report Paper)}}
\end{itemize}

\paragraph{Biography}\label{biography-143}

Anna Xambó is a Senior Lecturer in Music and Audio Technology at De
Montfort University (DMU), a member of Music, Technology and Innovation
- Institute for Sonic Creativity (MTI2), and an experimental electronic
music producer. Her research and practice focus on sound and music
computing systems looking at novel approaches to collaborative,
participatory, and live coding experiences. She has been the Principal
Investigator of the EPSRC HDI Network Plus funded project "MIRLCAuto: A
Virtual Agent for Music Information Retrieval in Live Coding" and part
of the Future Research Leaders Programme 2021/22 at DMU. Since 2016, she
has taken proactive roles in organisations for improving the
representation of women in music technology.

\url{https://annaxambo.me}
