
\subsubsection{Amalgam}\label{amalgam}

\textbf{\href{/2023/catalogue/person/hoogland-timo.html}{Timo~Hoogland},
  \href{/2023/catalogue/person/freeke-saskia.html}{Saskia~Freeke}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes}

Amalgam is an audiovisual live coded performance by Sasj \& Timo of
algorithmic electronic dance music and playful geometry and patterns.
The work is the latest iteration in an ongoing research and
collaboration between Saskia Freeke and Timo Hoogland where they explore
the possible relationships between image and sound. During this piece
the visual output is used as input for sonic transformations, displacing
rhythm, melody and sonic textures based on color, geometry and patterns.


\subsubsection{Arrays of Disarray}\label{arrays-of-disarray}

\textbf{\href{/2023/catalogue/person/garson-jessica.html}{Jessica~Garson~(Messica~Arson)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/alternative-algorithms.html}{\textbf{Alternative
      Algorithms}\\
    Thursday, April 20th, Doors 19:30 / Show: 20:00, \emph{EKKO}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-1}

In her performance "Arrays of Disarray," Brooklyn-based artist Messica
Arson will use live coding in Python with FoxDot and custom scripts to
create a dynamic and electrifying experience. She will also incorporate
live sampling of her own screams, and use Hydra to create a chaotic yet
mesmerizing visual world. This promises to be a one-of-a-kind
performance.


\subsubsection{AUTO\{\}Construcción}\label{autoconstrucciuxf3n}

\textbf{\href{/2023/catalogue/person/abreu-ivan.html}{Iván~Abreu},
  \href{/2023/catalogue/person/cortes-malitzin.html}{Malitzin~Cortés~(CNDSD)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-2}

AUTO\{\}Construcción is an audiovisual concert of live coding and
algorithm-based video game experience that explores the relationship
between speculative architecture and the phenomena of informal housing
executed by "non-architects" in countries such as Mexico, the United
States, Latin America, Asia, India and some European peripheries,
collaboratively creating 3D imaginaries with machine learning. The
audiovisual immersion is guided by text and also by an avatar.


\subsubsection{Title to come
  post-performance}\label{title-to-come-post-performance}

\textbf{\href{/2023/catalogue/person/gorelick-dan.html}{Dan~Gorelick~(dan.dog)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-3}

The piece will be a response to the previous acts and energy in the
room. The musical elements will be live-coded patterns accompanied by
electric cello and vocals.


\subsubsection{Blocking Behaviours}\label{blocking-behaviours}

\textbf{\href{/2023/catalogue/person/gunnarsson-bjarni.html}{Bjarni~Gunnarsson}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/alternative-algorithms.html}{\textbf{Alternative
      Algorithms}\\
    Thursday, April 20th, Doors 19:30 / Show: 20:00, \emph{EKKO}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-4}

`Blocking Behaviours' concerns the real-time interpretation of two
simulations of complex behaviour through an agent-based system. The
simulations enforce a way of thinking that revolves around balancing
behaviours, an attitude that considers musical output as something that
emerges from an interaction with an autonomous system. The simulation
acts as a generative, rule-based system producing output that is subject
to different kinds of observation algorithms. The idea is that evolving
processes are set in motion where the creator/composer becomes an
observer of various developments. The output can not always be
controlled in detail but is instead interpreted and further processed.
The interpretation involves a mapping between different modes of
representations in order to simplify or combine. In `Blocking
Behaviours' the idea is to explore the boundary of generative behaviour,
control and and direct access to computer sound synthesis.


\subsubsection{Botbop: Integers \& Strings}\label{botbop-integers-strings}

\textbf{\href{/2023/catalogue/person/jordaens-kasper.html}{Kasper~Jordaens},
  \href{/2023/catalogue/person/sondervan-dagobert.html}{Dagobert~Sondervan},
  \href{/2023/catalogue/person/claes-andrew.html}{Andrew~Claes}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-5}

The fourth iteration of Bot Bop's exploratory journey into the artistic
potential of combining AI and live coding, will deepen the focus
incorporating real-time string arrangement, its visual representation
and the interaction and creative possibilities of AI.

Three live coders, Dago Sondervan -who uses multiple live coding
environments at the same time-, Andrew Claes -accomplished
wind-controller and patching adept- and Kasper Jordaens -live visual and
data artist- team up creating an interactive environment where
improvisation and computer aided composition can overflow.

Continuing development of BOTBOP's custom software and implementations
using primarily open source software, now enables the creation of
musical scores in real time. Starting from improvisation, MIDI data is
gathered, processed and distributed on stage to a classical string
quartet. Algorithmic strategies are combined with machine learning
techniques to render a sensible musical output, to be played at first
sight by the strings. The focus is on dynamic systems, optimized to
react in real time rather than pre-generated and `offline', giving this
audio-visual performance a distinct edge, blurring lines between
classical composition, electronic music and jazz.

Integers \& Strings premiered at Sònar festival during its `AI \& Music
S+T+ARTS' 2021 festival in Barcelona in co-production with BOZAR
Brussels.


\subsubsection{Brickwork: Destroy}\label{brickwork-destroy}

\textbf{\href{/2023/catalogue/person/genissel-agata.html}{Agata~Genissel}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-6}

This iteration of Brickwork explores destruction as something that has
the potential for regeneration. Live coding using TidalCycles, Hydra,
and incorporating live vocals, this synthesis of the digital and vocal
expands on the relationship between technology and performer as
something that is symbiotic, playful, erroneous and against notions of
rigid control. In exploring the physical space away from the laptop
screen, Brickwork uncovers the potential for performance in-between live
coding and live instrumentation.

Challenging the relationship between artist and tool as one that seeks
to fulfil technological idealism by playing with visual, spatial and
sonic dynamics, \textquotesingle Destroy\textquotesingle{} seeks to
simultaneously build and destroy structures of sound and textures in
attempt to capture a moment that embraces paradox through playfulness.
It is in this frenzy of live improvisation and costume-fueled expression
that Brickwork seeks to destroy the impulse to resist destruction itself
-- please dance!


\subsubsection{Broken Bond}\label{broken-bond}

\textbf{\href{/2023/catalogue/person/harris-roxanne.html}{Roxanne~Harris~(alsoknownasrox)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-7}

"Broken Bond" is a live coding performance exploring the broken
connections between technology and humanity. Through a combination of
live coding and sound manipulation, this performance will explore how
technology has both connected and disconnected us from others. Audience
members will experience an immersive soundscape that will heighten their
senses to the complexities of our modern technological landscape.


\subsubsection{c0l1v3}\label{c0l1v3}

\textbf{\href{/2023/catalogue/person/gola-bruno.html}{Bruno~Gola}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-8}

c0l1v3 is a collaborative live codable open web platform and instrument
created by Bruno Gola. For ICLC 2023 Bruno proposes a collaborative
performance session where the local audience can join him and play with
their mobile phones and laptops, and remote collaborators can join from
home.


\subsubsection{Code must go on!}\label{code-must-go-on}

\textbf{\href{/2023/catalogue/person/alonso-florencia.html}{Florencia~Alonso~(Flor~de~Fuego)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-9}

This performance is based on the theatrical aspect of a stage, how in
this sense code can be used not just for visuals but more as a concept
for a live show. The intention is also to combine physical and digital
aspects with code, like VR spaces, physical DMX lights and robot puppies
performing. Transforming the code into an universal multiplexer device
that is also an actor in the scene.


\subsubsection{Codes for a Dance}\label{codes-for-a-dance}

\textbf{\href{/2023/catalogue/person/sicchio-kate.html}{Kate~Sicchio},
  \href{/2023/catalogue/person/mclean-alex.html}{Alex~McLean}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-10}

This piece explores movement through textual, visual and physical
communication. It focuses on language, patterns and the performance of
gestures as a way to bridge the digital and the physical. Through a
series of live coded actions, connections will be made from humans to
machines and back to humans again.


\subsubsection{Codie}\label{codie}

\textbf{\href{/2023/catalogue/person/sicchio-kate.html}{Kate~Sicchio},
  \href{/2023/catalogue/person/groff-hennigh-palermo-sarah.html}{Sarah~Groff~Hennigh-Palermo}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-11}

We are a live coding duo, making music and visuals. Our performances are
A/V shows will electronic sounds and video projections. We perform by
creating our works live and anew for each performance. Our sounds are
dancey and our graphics are SoCal. Sarah's visuals are coded with her
own Clojurescript-Electron app called La Habra. She creates patterns and
abstract shapes that animate and move to the rhythm. Kate creates sound
in the Ruby-based environment Sonic Pi. She manipulates and layers
samples with algorithms to create the soundtrack. We type and improvise
as we go, reacting to each other's output and the audience's reactions.
In accordance with the Live Coding Draft Manifesto, we project our code
as we go, so the audience can inspect and marvel at the changes and
accumulations.


\subsubsection{ColorScape: DipInCode}\label{colorscape-dipincode}

\textbf{\href{/2023/catalogue/person/oduro-kofi.html}{Kofi~Oduro~(illestpreacha)},
  Renee Jordan}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/lunch-concert-2.html}{\textbf{Lunch \&
      Concert 2}\\
    Friday, April 21st, Doors 12:45 / Show: 13:10, \emph{NAR - Café der
    Kunsten}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-12}

Dip in Code takes up the concept of chromesthesia (i.e. hearing
colour/seeing sound) while allowing the audience the pleasure of tasting
colors and seeing taste while hearing it at the same time. Dip in Code:
Kitchen of Hues, takes colors that happen to be named after food. To
give an audiovisual experience that crosses over to an immersive
culinary setting/dining experience as well. Every track isn't a single
color like its predecessor but will be named after meals that are also
names of colours. The soundtrack of each meal is coded and visualized to
make sure the meal is represented well. Enjoy that colorful byte.


\subsubsection{Commuta: A Cross Adaptive Laptop
  Ensemble}\label{commuta-a-cross-adaptive-laptop-ensemble}

\textbf{\href{/2023/catalogue/person/corvi-francesco.html}{Francesco~Corvi},
  \href{/2023/catalogue/person/ancona-riccardo.html}{Riccardo~Ancona},
  \href{/2023/catalogue/person/francavilla-giulia.html}{Giulia~Francavilla~(Giulia~Rae)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-13}

Commuta is a trio algorithmic performance dealing with the notion of
cross-adaptive sonic relationships. Three performers are entangled in a
network of influences obtained by dynamically relating the expressive
features of each sound stream with the others. In this system, live
coding acts as a form of interaction capable of producing perturbations
and changing on-the-fly the overall structure of the network. The joint
result seeks for an emergent complexity lying at the intersection of the
the three performer's individual practices: the development of adaptive
sonic processes in live coding by Francesco Corvi (nesso.xyz), Giulia
Rae's exploration of machine listening techniques for environmental
synthetic soundscapes, and Riccardo Ancona's study on material
identities in corpus manipulations.


\subsubsection{Conversational Learning}\label{conversational-learning}

\textbf{\href{/2023/catalogue/person/paz-ivan.html}{Iván~Paz}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-14}

Conversational learning explores live coding liveness within the machine
learning process (data collection, training and validation), focusing on
how real-time training of a machine learning algorithm can be sonically
exposed. It is based on a rule-learning algorithm that automatically
produces new synthesizer presets out of a small labeled database. The
algorithm is designed with only two parameters controlling ``how close''
the new created presets can be from those originally present in the
training data. The learning process happens mid-performance, tweaking
the algorithm parameters on-the-fly. Then, the different learned models
unfold the piece in conversation with the performer.


\subsubsection{CRash Landing}\label{crash-landing}

\textbf{\href{/2023/catalogue/person/hernandez-sanchez-citlali.html}{Citlali~Hernández~Sánchez~(turbulente)},
  \href{/2023/catalogue/person/bautista-rodriguez-lina.html}{Lina~Bautista~Rodríguez},
  \href{/2023/catalogue/person/pibernat-trias-roger.html}{Roger~Pibernat~Trias}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-15}

An experimental project where three performers share a common code
expressed in different but interdependent languages: text, gesture,
image, voice and sound recordings. Lina will generate music and sound
textures using Tidal Cycles, Citlali will be recording voice live loops
using body gestures with motion sensors, and Roger will be generating
visuals with his own
\href{https://github.com/loopier/animatron}{\emph{Animatron}} tool
dedicated to live coded animation. «CRash Landing» represents a metaphor
between a plane flight and a live coding performance, starting with a
from scratch and finishing with a crash.


\subsubsection{c\_robo\_}\label{c_robo_}

\textbf{\href{/2023/catalogue/person/rinkoff-william.html}{William~Rinkoff~(c\_robo\_)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-16}

A livecoding performance with one person, one laptop, a digital feedback
patch and hundreds of .wav files (most of which are drum loops). The
audio will be a blend of Algorave, hardcore breaks, industrial hip-hop,
and harsh noise. Feel free both to dance and/or lay on the ground in
front of the subwoofer.


\subsubsection{DEF FUNCTION(DYSTOPIAKIRA)}\label{def-functiondystopiakira}

\textbf{\href{/2023/catalogue/person/smith-ryan-ross.html}{Ryan~Ross~Smith~(The~Wookie)},
  \href{/2023/catalogue/person/lawson-shawn.html}{Shawn~Lawson~(Obi-Wan~Codenobi)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-17}

Neo Tokyo, ca. 2019, 31 years after World War III, Akira awakens. This
homage is an audiovisual, live-coded performance remixing and
re-envisioning the 1988 classic film created in the year of its setting,
2019 and reimagined now in 2022.

The Rebel Scum (aka Shawn Lawson and Ryan Ross Smith aka Codenobi and
The Wookie) use the code editor Jensaarai to collaboratively and
simultaneously live-code TidalCycles and Python, each supported by
SuperCollider and Touch Designer on the backend respectively.


\subsubsection{Epiploke}\label{epiploke}

\textbf{\href{/2023/catalogue/person/cheesman-lucy.html}{Lucy~Cheesman},
  \href{/2023/catalogue/person/mclean-alex.html}{Alex~McLean}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-18}

People have danced to algorithms throughout history, including the
Ancient Greeks. Epiploke is such an algorithm, evident in fragments of
Ancient Greek texts, where metrical short-long structure is shifted in
patterns. In this performance Lucy Cheesman and Alex McLean will explore
Ancient Greek narratives and patterns with live code, bringing together
fragments of structures from different texts, including instances of
epiploke, as well as incorporating audio descriptions from Homer and
reconstructions of Homeric instrumentation.


\subsubsection{flux}\label{flux}

\textbf{\href{/2023/catalogue/person/samarotto-michele.html}{Michele~Samarotto}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-19}

\emph{flux} treats ideas of ``perceptual'' displacement. The piece
involves two apposite elements: the notorious Shepard-Risset glissando
and continuously fluctuating rhythms. Ever-shifting anchor points amidst
the sonic substance blur the lines between movement and stasis. Not
aiming to create a general confusion of the senses nor to deconstruct
4-to-the-floor tropes, I would rather like to suggest immersive
qualities.

As often the case in my live-coding practice, I start from minimal
pre-written code in SuperCollider, constituting the basic skeleton of
the composition/performance, designed to explore certain sonic areas of
interest as well as to afford entering uncharted territory; in this
sense I always liked Xenakis' image of the composer (and here I include
the notions of performer/improviser) as a pilot supervising ``the
controls of a cosmic vessel sailing in the space of sound''
\emph{(Formalized Music)}.


\subsubsection{grain by grain}\label{grain-by-grain}

\textbf{\href{/2023/catalogue/person/sarratea-sol.html}{Sol~Sarratea~(@alsolquema)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-20}

Inspired by concepts from granular synthesis and phase shifting in
sound, \textbf{``Grain by grain''} is a visual performance generated
through the composition of ``visual grains'' at real time using fragment
shaders. Where a ``visual grain'' is defined as a sample of a video
signal, or recording.

It is a displacement loop of the ``frame by frame'' paradigm, in which
the environment for live coding visuals is perceived as an infinite
nested sequence of frames. Mutating frame by grain is introducing a new
generation for visual narratives.

Working with ``visual grains'' lead to building ``visual phrases'',
which can be defined by a finite number of frames, originally from a
recording, and they can be looped, transformed in time and/or space,
mixed, and overlaid.


\subsubsection{Grim! Grim! Grim!}\label{grim-grim-grim}

\textbf{\href{/2023/catalogue/person/ganz-axel.html}{Grimberg}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/alternative-algorithms.html}{\textbf{Alternative
      Algorithms}\\
    Thursday, April 20th, Doors 19:30 / Show: 20:00, \emph{EKKO}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-21}

Grimberg\textquotesingle s music is based on loops of acoustic drum and
percussion, synthesizer and guitar lines. He extracts these loops from
old stuff of the 70s and sometimes he creates them on his own. This
enriches his tunes with a patina, a warm atmosphere of psychedelic
scapes between ambient and progressive rock. Combined with choppy
structures of contemporary pattern based music this turns out a unique
hybrid of a fluent groove based sound which could be named "Algorithmic
Krautrock".


\subsubsection{Happy Algorave
  Performance}\label{happy-algorave-performance}

\textbf{\href{/2023/catalogue/person/reppel-niklas.html}{Niklas~Reppel}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-22}

\emph{``But Algorave is about bringing algorithms a bit more into the
foreground, haunted a bit by rave; some promise of less focus on the
musician and more on each other, and a serious kind of dedication to
having some fun.''} - Alex
McLean.\textsuperscript{\href{/2023/\#fn:1}{1}}

Algoraves were invented, or so live coding lore has it, to take live
coding out of an academic context and make it fun for both audience and
performer. For me, there's not much fun in repeating myself, and as a
result my Algorave performances are somewhat eclectic. Sometimes they
sound a bit like german EBM from the 80s, sometimes like footwork, and
sometimes like a free jazz drummer playing on a TB909. Sometimes they
contain the occasional cover song, and sometimes they have random animal
noises or cartoon quotes sprinkled in (there's no fun in taking the fun
\textbf{too} seriously either).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{enumerate}
\item
  \phantomsection\label{fn:1}
  \url{https://esoteric.codes/blog/interview-with-alex-mclean}~\href{/2023/\#fnref:1}{↩}
\end{enumerate}


\subsubsection{Human-Computer Counter-Choreographies
  (Beta)}\label{human-computer-counter-choreographies-beta}

\textbf{\href{/2023/catalogue/person/chicau-joana.html}{Joana~Chicau}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-23}

This performance is part of a practice-based PhD that comprises embodied
and choreographic techniques to inform the development of methods and
tools for designing of web-interfaces --- driven by transparency and
legibility. Joana Chicau will present early prototypes such as custom
interfaces and plug-ins that aim at responding to the opaque algorithmic
models embedded in pervasive web interfaces. For instance, by exposing
user-tracking and phenomena such as `dark patterns' through live
performance. She will interweave live coding using JavaScript commands
on the web console and custom browser tools with voice narration
following a choreographic perspective.


\subsubsection{KhipuKoding 2.0 + The Neokhipukamayok
  Manifesto}\label{khipukoding-2.0-the-neokhipukamayok-manifesto}

\textbf{\href{/2023/catalogue/person/torres-nunez-del-prado-paola.html}{Paola~Torres~Núñez~del~Prado}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-24}

KhipuKoding 2.0 + The Neokhipukamayok Manifesto is a Sound Performance
thought around the khipu (fiber-based notation device of pre-Hispanic
origin) that combines Machine Learning, Computer Vision, the human act
of knotting, and a hybrid notation method that reads khipu-style knots
in order to generate sound.


\subsubsection{Listening to the (Future)
  Landscape}\label{listening-to-the-future-landscape}

\textbf{\href{/2023/catalogue/person/bouchard-sara.html}{Sara~Bouchard}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-25}

\emph{Listening to the (Future) Landscape} is a quadraphonic, live-coded
sound performance, incorporating found natural objects, local
environmental recordings and voice in an immersive listening space
evocative of our ecological future. The artist has collected objects and
recordings from the local landscape --- the city of Utrecht --- which
become the primary instruments in the piece. With these artifacts, the
artist builds a multi-layered, virtual space that exists in parallel
with --- and in tension with --- the physical environment.


\subsubsection{Neowise 5.8 V/E}\label{neowise-5.8-ve}

\textbf{\href{/2023/catalogue/person/champlin-alicia.html}{Alicia~Champlin}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-26}

Neowise 5.8 V/E is a constructed/deconstructed soundscape, last of a
series of minimalist and ambient improvisations inspired by the
unfathomable orbit of the comet they are named afer. Using just 2 or 3
samples in TidalCycles, it layers the ringing of the spheres, and beams
out harmonics like a prism splitting light into distinct colors. The
samples used are recordings of a bow chime, a very physical instrument
which plays you in return. Recordings of this acoustic behemoth cannot
track the experience of it live, but by manipulating these samples, we
find new means to engage with the tangible shapes of orbits and
conjunctions. In this last scene of the series, the live bow chime also
joins the stage as recompense to the early studies' original
explorations of ebb and return. Dedicated to Matt Samolis in gratitude
for his mentorship.


\subsubsection{New Ways of Collaboration}\label{new-ways-of-collaboration}

\textbf{\href{/2023/catalogue/person/verhage-sabrina.html}{Sabrina~Verhage}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-27}

In this Algorave performance Sabrina is exploring the possibilities of
collaborating with a large machine learning model in a live coding
setting.


\subsubsection{Nodysseus.THREE}\label{nodysseus.three}

\textbf{\href{/2023/catalogue/person/popple-ulysses.html}{Ulysses~Popple}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-28}

This performance will be using Nodysseus, a work-in-progress livecoding
tool. It is a general purpose visual programming language and editor for
the web inspired by a combination of node-based live editors and visual
effects tools. In this algorave set, I\textquotesingle ll be using
THREE.js along with built-in Nodysseus nodes. The majority of the
performance will feature audioreactive 3D objects postprocessed by glsl
shaders. I will use basic 3D shapes, particle simulations, and pre-built
geometry files, all procedurally manipulated, mixed, and textured by
live graph editing. Some of the nodes will be premade, but combining
them and adding audio-reactivity will be done live.


\subsubsection{P5LIVE COCODING}\label{p5live-cocoding}

\textbf{\href{/2023/catalogue/person/davis-ted.html}{Ted~Davis},
  \href{/2023/catalogue/person/verhage-sabrina.html}{Sabrina~Verhage}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-29}

At this participatory performance the barrier between the audience and
the performers will be blurred. Rather than facing the audience, the
performers will join them as multiple machines invite anyone to join the
P5LIVE COCODING session. Starting from scratch, the shared codebase will
extend, break, tweak, grow in complexity, and ideally bring us all to
new unexpected visual territories. So join in and COCODE with us!


\subsubsection{patterns in modulation}\label{patterns-in-modulation}

\textbf{\href{/2023/catalogue/person/pappalardo-sebastian.html}{Sebastian~Pappalardo~(eerie\_ear)},
  \href{/2023/catalogue/person/pavlica-blaz.html}{Blaž~Pavlica}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/hybrid-acoustics.html}{\textbf{Hybrid
      Acoustics}\\
    Sunday, April 23rd, Doors 15:30 / Show: 16:00, \emph{Nicolaïkerk}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-30}

Patterns in modulation is a collaboration between two creative coders,
Sebastián Pappalardo aka. eerie\_ear and Blaž Pavlica. Through code
improvisations, they generate meandering and evolving patterns and
textures that create subtle and interweaved soundscapes and music,
intended to challenge the audience's sense impressions and create a
compelling immersive experience.


\subsubsection{Pirarán -- Algorithmic Acid
  Music}\label{piraruxe1n-algorithmic-acid-music}

\textbf{\href{/2023/catalogue/person/franco-briones-alejandro.html}{Alejandro~Franco~Briones},
  \href{/2023/catalogue/person/villasenor-de-cortina-diego.html}{Diego~Villaseñor~de~Cortina~(Videco)},
  \href{/2023/catalogue/person/lopez-pineda-ivan.html}{Iván~López~Pineda}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/alternative-algorithms.html}{\textbf{Alternative
      Algorithms}\\
    Thursday, April 20th, Doors 19:30 / Show: 20:00, \emph{EKKO}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-31}

Pirarán is a networked ensemble that hallucinates with mad light-ganglia
and one-legged silences. Their algorithmic acid music oscillates between
the aridity and emptiness of the post-end of time. The ensemble is made
up of Iván López (Morelia, MX), Diego Villaseñor (Mexico City, MX) and
Alejandro Franco Briones (Ontario, CA).


\subsubsection{Poetry Attack 01}\label{poetry-attack-01}

\textbf{\href{/2023/catalogue/person/moura-mari.html}{Mari~Moura},
  \href{/2023/catalogue/person/marques-da-costa-joenio.html}{Joenio~Marques~Da~Costa}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-32}

How many women are here? How many black people are here? How many black
women are here? In these times of displacement, it is necessary to think
about it. In this show, artist Mari Moura (1st Minister of the Sensible
State) carries out a poetry attack using live coding and text writing to
questioning the absence of women, black people, and black women at live
coding events and spaces. The absence of women, black people and black
women is not natural, it is part of a systematic racist system that
promotes exclusion. The performance act is a micro-activist action that
invites the live coding community to reflect on the roles and
opportunities to propose a movement of displacement and change regarding
the absence of women, black people and black women. The performance is
composed by sound art and performance art, synthesizers and sound
samples will be manipulated by live coding through the free software
platform Sonic Pi.


\subsubsection{QBRNTHSS hybrid set}\label{qbrnthss-hybrid-set}

\textbf{\href{/2023/catalogue/person/casamajo-ramon.html}{Ramon~Casamajó~(QBRNTHSS)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-33}

QBRNTHSS hybrid set is a performance using live coding and acoustic and
electronic instruments, including trumpet, processed contact mic, and
some effect pedals. In his performances, we can find Ramon Casamajó
(a.k.a. QBRNTHSS) riding the tension between the rhythm and the
abstraction, the melody and the noise, the synthetic and the analogic.
Hardly influenced by avant-garde musicians that have experimented with
the limits of electronic music, like Jon Hassell or Moritz Von Oswald,
Ramon Casamajó tries to use live coding in his musical practice to find
new sounds and his own voice.

\subsubsection{Rumble Machines}\label{rumble-machines}

\textbf{\href{/2023/catalogue/person/isern-rabella-eloi.html}{Eloi~Isern~Rabella~(Eloi~el~Bon~Noi)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-34}

After his death, the heirs of Professor Bad Trip found in his old
mansion the drawings of some machines created with the evil intentions
of annoying as many people as possible. We have recovered these drawings
to program them again and honor the memory of their creator. We have not
managed to resurrect him, but seeing the Rumble Machines live will be
like having Professor Bad Trip right under your nose.

\subsubsection{Sardine X Ziffers: New Tools for Algorithmic
  Expression}\label{sardine-x-ziffers-new-tools-for-algorithmic-expression}

\textbf{\href{/2023/catalogue/person/forment-raphael-maurice.html}{Raphaël~Maurice~Forment~(Bubobubo)},
  \href{/2023/catalogue/person/georges-remi.html}{Rémi~Georges~(Ralt144MI)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-36}

This duo performance by Ralt144MI and Bubobubo aims to highlight recent
developments in Sardine (Raphaël Forment) and Ziffers (Miika Alonen).
These two live coders from Lyon are dynamic members of the French Cookie
Collective. They are, among other things, responsible for the current
dynamism of the French live coding scene! Uniting their respective
styles for ICLC 2023, they wish to engage with the audience in an
algorithmic exploration of their new systems for improvisation.

In anticipation of ICLC 2023, Miika Alonen and Raphaël Forment
(BuboBubo) have joined forces! They have merged their respective tools,
Sardine and Ziffers, into a single live entity! Doing so, they are
hopeful to pave the way for new future experiences in algorithmic
melodic generation. Sardine is a modular environment for live coding in
Python 3.10+. Ziffers is a concise digital music notation system for
algorithmic and generative composition. The two, taken together,
constitute a powerful environment that continues the approach initiated
by TOPLAP long ago, that of exploring musical algorithmic patterns as an
expressive gesture! The more the merrier! Two pattern languages in one
single environment!

During their performances with the Cookie Collective, Ralt144MI and
BuboBubo have felt the need to have at their disposal new extensible and
modular tools that would allow hybridization with analog machines,
synchronization, and the quick exchange of ideas, functions, or code
snippets. It is on this condition that it seemed possible to establish
new interactions with their friends from the demoscene, the DIY music
world or the generative visual world. Their performance will pay tribute
to the energy of the contemporary French scene (the Cookie lives!) and
will introduce the live coders present to a musical use of these new
tools. Expect bricolage, loud rhythms and synchronized computers!


\subsubsection{Serendipitous Liquidators}\label{serendipitous-liquidators}

\textbf{\href{/2023/catalogue/person/giannoutakis-kosmas.html}{Kosmas~Giannoutakis},
  \href{/2023/catalogue/person/j-juarez-aaron.html}{Aaron~J.~Juarez}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/alternative-algorithms.html}{\textbf{Alternative
      Algorithms}\\
    Thursday, April 20th, Doors 19:30 / Show: 20:00, \emph{EKKO}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-37}

Serendipitous Liquidation describes the practice of live coding that
reuses, remixes, and repurposes creative code by various authors in live
performances. The limitless aesthetic possibilities of openly published
code snippets are harnessed in experimental, improvisatory, and playful
modes. This practice paves the way for the development of
commons-centric ecosystems that are supported by Distributed Ledger
Technologies. The performance engages with SuperCollider tweets and
Hydra sketches composed by various creative coders. All the authors are
cited on screen and in the credits.


\subsubsection{The Cuckoo\textquotesingle s Nest}\label{the-cuckoos-nest}

\textbf{\href{/2023/catalogue/person/montague-jude.html}{Jude~Montague},
  \href{/2023/catalogue/person/cullis-amy.html}{Amy~Cullis}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-38}

Morris is a traditional dance in which small teams (six to ten) step and
clap sticks in group formation. In St Leonards-on-Sea, Sussex there is a
new side/team of dancers called \textquotesingle Rheda\textquotesingle s
Dream\textquotesingle{} led by Amy Ruth Cullis. Jude Montague has been
setting up a new series of Algoraves locally and together they are
creating an interweaving of Morris dance and algorithms, inspired by
Alex McClean\textquotesingle s work with patterns and computer code. The
performance will feature dancing by Amy Ruth Cullis and will use code to
interact with the audience as instructions. Those of the audience who
wish can take part in a processional dance. The experience will bring
together early modern and new dance.


\subsubsection{The neoCowgirl Manifesto}\label{the-neocowgirl-manifesto}

\textbf{\href{/2023/catalogue/person/sutherland-matilda.html}{Matilda~Sutherland}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-39}

The neoCowgirl harnesses the web browser‑as‑arena, morphing the
seemingly enclosed window into her Own Personal Wild Wild West. In a
combination of live‑programmed audio, visual, and written media, the
neoCowgirl reimagines a future beyond techno‑libertarian ideals of
AI‑fuelled automation.


\subsubsection{this is not a piano}\label{this-is-not-a-piano}

\textbf{\href{/2023/catalogue/person/reppel-niklas.html}{Niklas~Reppel}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/lunch-concert-1.html}{\textbf{Lunch \&
      Concert 1}\\
    Thursday, April 20th, Doors 12:45 / Show: 13:10, \emph{NAR - Café der
    Kunsten}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-40}

\emph{This is not a piano} is a suite of pieces for sampled piano I
wrote (or generated) from small snippets of text data. Learning a
variable-order Markov chain from the properties of the snippets, I added
variation through layering and manipulating certain aspects of the sound
in an improvisational process, using my live coding environment
\href{https://github.com/the-drunk-coder/megra.rs}{Mégra}.

The results have a slight reminiscence of, though no real connection to,
some piano pieces by Eric Satie. I've always been drawn to the piano as
an instrument, as apart from its pleasant sound it also lends itself
well to reflect structural properties of music.

In the end, it's more about the interaction and dialog with the
algorithm rather than trying to beat benchmarks.


\subsubsection{todødot}\label{toduxf8dot}

\textbf{Florencia~Alonso~(Flor~de~Fuego)}

Will be performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/algorave.html}{\textbf{Algorave}\\
    Saturday, April 22nd, Doors: 21:50 / Show: 22:00,
    \emph{TivoliVredenburg}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-41}

(...)


\subsubsection{{[} \_ \_ \_ {]}}\label{section}

\textbf{\href{/2023/catalogue/person/liu-jia.html}{Jia~Liu~(刘佳)},
  \href{/2023/catalogue/person/li-song.html}{Song~Li~(李松)},
  \href{/2023/catalogue/person/tan-shuoxin.html}{Shuoxin~Tan~(谭硕欣)}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-42}

Can algorithms be collaborative? What happens when the Borromean knot is
applied to network structures? Can we communicate through numbers? In
this performance, the network music ensemble {[} \_ \_ \_ {]} presents
its thoughts on these questions. The members of the ensemble will each
live-code their algorithms on their laptops connected through a
communication mechanism they have created, the algorithms being
live-interpreted into sound in the concert room. The data communication
mechanism was developed from scratch during the Covid lockdown in 2020
using the programming language SuperCollider. Their system is mainly
based on message transmission. Each member plays the role of a node,
sending and receiving messages. They could define and modify the
algorithms to reform message chains and time/frequency intervals
respectively. Writing and changing rules on the fly, they listen to each
other through subtle changes in the sound resulting from their in-time
communication.


\subsubsection{Variations on Kandinsky}\label{variations-on-kandinsky}

\textbf{\href{/2023/catalogue/person/copper-monique.html}{Monique~Copper}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/lunch-concert-1.html}{\textbf{Lunch \&
      Concert 1}\\
    Thursday, April 20th, Doors 12:45 / Show: 13:10, \emph{NAR - Café der
    Kunsten}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-43}

`Variations on Kandinsky' is inspired upon the geometrical forms which
Kandinsky used for his mise-en-scène to Mussorgsky's `Pictures at an
Exhibition'. Monique will improvise with the Codeklavier to be able to
generate code for two purposes: a visual narrative with geometrical
forms on an html canvas, and real-time electronic accompaniment to her
piano playing.

Electronic music always played an important role during Monique Copper's
career. She worked in Ton Bruynèl's electronic studio and has since
performed his piano music with tape.

``With Bruynèl (1934-1998) we often discussed the future of electronic
music. In particular during the transition from analogue to digital. The
computer was seen as a natural continuation of the electronic music but
in particular we foresaw the development into a live musical instrument.
The computer will be one of the next generation of musical instruments
ready for live performances."


\subsubsection{Vortex: Reresik}\label{vortex-reresik}

\textbf{\href{/2023/catalogue/person/candra-rini-peni.html}{Peni~Candra~Rini},
  \href{/2023/catalogue/person/purnama-aji-rangga.html}{Rangga~Purnama~Aji},
  \href{/2023/catalogue/person/sewell-sen.html}{Sen~Sewell},
  \href{/2023/catalogue/person/strohschein-heather.html}{Heather~Strohschein},
  \href{/2023/catalogue/person/van-der-walt-j-simon.html}{J.~Simon~van~der~Walt},
  \href{/2023/catalogue/person/whitmer-bill.html}{Bill~Whitmer}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/immersed-in-code.html}{\textbf{Immersed in
      Code}\\
    Friday, April 21st, Pre-Show 19:30 / Show: 20:00, \emph{Former Pieter
    Baan Centrum}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-44}

This work tries to interpret the existence of garbage that has
accumulated physically and its analogy in the conception of the mind.
The lyrics in this work try to describe the tightness, confusion, and
depression caused by the awareness of the murkiness within the human
mind and how the influence of garbage can strongly impact the saturation
of this condition.

\subsubsection{We All Begin in
  Abstraction}\label{we-all-begin-in-abstraction}

\textbf{\href{/2023/catalogue/person/knotts-shelly.html}{Shelly~Knotts},
  \href{/2023/catalogue/person/bahng-sojung.html}{Sojung~Bahng~(방소정)},
  \href{/2023/catalogue/person/casilli-kirby.html}{Kirby~Casilli}}

Was performed at:

\begin{itemize}
  \tightlist
\item
  \href{/2023/catalogue/event/choreographic-coding.html}{\textbf{Choreographic
      Coding}\\
    Wednesday, April 19th, Doors 19:30 / Show: 20:00, \emph{Het Huis
    Utrecht}}
\end{itemize}

\paragraph{Program Notes}\label{program-notes-45}

``We All Begin in Abstraction\ldots'' is an AV networked live coding
performance for live coding musician (Shelly Knotts), live video (Sojung
Bahng) and movement (Kirby Casilli) which takes inspiration from Legacy
Russell's text Glitch Feminism to explore threads of female embodiment,
error and algorithmically mediated life.

In live coding, error constitutes an embodied form of computing, drawing
attention from the screen and towards the body which is creating a
rupture, a break, in the flow system.

In this work we draw attention to the points of interaction between
body, machine and algorithm and the ruptures and errors that shape the
interaction between artists, code and audience in algorithmically driven
performance. We use machine learning algorithms to track movement and
live video as an input to a live coded performance, forming a feedback
loop between body, algorithm, embodied algorithms and mediated forms.
