\subsubsection{A Quad Entropic Conversation}\label{a-quad-entropic-conversation}

\textbf{\href{imrisek-sarah}{Sarah~Imrisek~(@cymatiste)},
\href{gordon-marcus}{Marcus~Gordon~(magfoto)},
\href{briede-ilze}{Ilze~Briede~(Kavi)},
\href{maheras-hrysovalanti}{Hrysovalanti~Maheras~(hryso)}}

\textbf{\href{https://youtu.be/AttfP19Gnwg}{Watch Video on YouTube}} -- \href{https://youtu.be/AttfP19Gnwg}{https://youtu.be/AttfP19Gnwg}

\paragraph{Description}\label{description}

A Quad Entropic Conversation is a live coding performance by ensemble
The Endemics, that features speech used in various forms to carry on an
audiovisual conversation between the four members and their instruments.
Live coded in Hydra, Orca, and SuperCollider, and ending with a touch of
analog modular sound, a conversation unravels inside a wormhole. The
meaning of the words, the meanings in speech, and everything transmitted
in the form of communication, undergoes a transformation, due to the
entropic forces taking place in black holes. Knowing from the beginning
that parts and pieces of ourselves get lost, and displaced in our
exchanges with others, we find an opportunity to better tackle the
resistance emerging in our conversations and create open ended dialogues
with one another and through the code we share.

\subsubsection{Atari 2600 Video Remix}\label{atari-2600-video-remix}

\textbf{\href{marques-da-costa-joenio}{Joenio~Marques~Da~Costa}}

\textbf{\href{https://youtu.be/4rrxgw--eYU}{Watch Video on YouTube}} -- \href{https://youtu.be/4rrxgw--eYU}{https://youtu.be/4rrxgw--eYU}

\paragraph{Description}\label{description-1}

The video is a series of video remix, sound art and live coding inspired
by the game console Atari 2600, mixed with historical pictures of
Brasília city (Brazil capital federal), and Salvador city (also called:
\emph{The biggest carnival in the world}). The sounds were made by live
coding with Tidal Cycles, using sound samples extracted from the
selected games, including \emph{Pitfall!} (released by Activision in
1982), \emph{Enduro} (released by Activision in 1983), \emph{River Raid}
(published by Activision in 1982), \emph{Keystone Kapers} (developed and
published by Activision in 1983), \emph{Megamania} (released by
Activision in 1982), and \emph{Pac-Man} (developed and published by
Atari, Inc. in 1982).

The series is a work-in-progress and soon new eposodes will be released,
you can find more info and news on the links below.

\begin{itemize}
\tightlist
\item
  Project site: https://atari2600.4two.art
\item
  Source code: https://codeberg.org/joenio/atari2600
\end{itemize}


\subsubsection{AV Club SF Community
Report}\label{av-club-sf-community-report}

\textbf{\href{gorelick-dan}{Dan~Gorelick~(dan.dog)},
\href{mclaughlin-tyler}{Tyler~McLaughlin~(R~Tyler)},
\href{hanson-don}{Don~Hanson~(d0n.xyz)},
\href{folz-rodney}{Rodney~Folz~(haute.rod)}}

\textbf{\href{https://youtu.be/88Z-b-w7kBc}{Watch Video on YouTube}} -- \href{https://youtu.be/88Z-b-w7kBc}{https://youtu.be/88Z-b-w7kBc}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-2}{\textbf{Community
  Report Session 2}\\
  Friday, April 21st, 11:15, \emph{VOGELFREI}}
\end{itemize}

\paragraph{Description}\label{description-2}

Community Report from the San Francisco based artist collective, AV Club
SF. The video documents the different performances that have taken place
since the formation of AV Club in April 2021, through current day. AV
Club has worked in close conjunction with artists from LivecodeNYC to
put on shows at SXSW festival, Gray Area, SyzygySF, and many other
venues throughout the Bay Area.

A lot of the additional effort for the shows goes into documentation so
that we can tell the story and communicate the artform of live-coding.
This video is a demonstration of a lot of the different contexts in
which the art of live-code has been shared on the west coast.


\subsubsection{Der dritte Körper}\label{der-dritte-kuxf6rper}

\textbf{\href{tan-shuoxin}{Shuoxin~Tan~(谭硕欣)},
\href{li-song}{Song~Li~(李松)},
\href{liu-jia}{Jia~Liu~(刘佳)}}

\textbf{\href{https://youtu.be/tjoV9C7QgsI}{Watch Video on YouTube}} -- \href{https://youtu.be/tjoV9C7QgsI}{https://youtu.be/tjoV9C7QgsI}

\paragraph{Description}\label{description-3}

In the tower room of church Sankt Michael Cologne, two small
loudspeakers are suspended from the bell tower with thin wires.

Connected through the network, two members of {[} \_ \_ \_ {]}, Song and
Jia perform live from London and Karlsruhe respectively. The sound
reaches the site through the loudspeakers and is listened to and
recorded by Shuoxin, the third performer and the only person on-site.
The audience is only able to hear through Shuoxin, as she moves through
the room with a binaural microphone in an auditory choreography and
interplays with the small loudspeakers.

Each individual involved in this event becomes ``Der dritte Körper'' -
the 3 performers on-site and remote, the installation and the noise in
the space, as well as the attentively listening ears of the audience and
the spaces they are in. The small tower room turns into a micro-cosmos
of sound, during this 20 minutes performance.


\subsubsection{Direction To NoWhere}\label{direction-to-nowhere}

\textbf{\href{oduro-kofi}{Kofi~Oduro~(illestpreacha)}}

\textbf{\href{https://youtu.be/KNtVOOiCBMY}{Watch Video on YouTube}} -- \href{https://youtu.be/KNtVOOiCBMY}{https://youtu.be/KNtVOOiCBMY}

\paragraph{Description}\label{description-4}

In the tradition of soundwalking, I use livestreaming (through the
livecoding language Hydra and a phone) as a prompt for my
\#DirectionStoNowhere project Part One and the idea of
\textquotesingle the last payphone\textquotesingle, to showcase the
viewpoint of a payphone that is left to just watch nature. What does it
see through its eyes? Does it recognize the changes of time. What occurs
if a human were to stumble upon this footage? What if we live score the
scene, how can that bring the digital realm closer to the physical
realm? Or does this mean, it is its own realm? What if this time, the
phone was remodified to enjoy a walk? Using lines of code to give it
life, what will its circuitry witness? What sounds will flow in its
head? The same sounds from 50,25,10,5 years ago or even yesterday still
prevail?


\subsubsection{Floating Gold -- Ibu Bhumi}\label{floating-gold-ibu-bhumi}

\textbf{\href{candra-rini-peni}{Peni~Candra~Rini},
\href{purnama-aji-rangga}{Rangga~Purnama~Aji},
\href{sewell-sen}{Sen~Sewell},
\href{strohschein-heather}{Heather~Strohschein},
\href{van-der-walt-j-simon}{J.~Simon~van~der~Walt},
\href{whitmer-bill}{Bill~Whitmer}}

\textbf{\href{https://youtu.be/hgBVv400aDY}{Watch Video on YouTube}} -- \href{https://youtu.be/hgBVv400aDY}{https://youtu.be/hgBVv400aDY}

\paragraph{Description}\label{description-5}

`Ibu Bhumi' is one of eight audiovisual pieces created by Floating Gold:
Peni Candra Rini, Rangga Purnama Aji and Gamelan Naga Mas.

Floating Gold was formed to explore the potential of international
collaboration through livecoding. Over a series of improvisatory
workshops in Estuary, Rangga Purnama Aji worked alongside four
livecoding musicians from Gamelan Naga Mas to record a series of musical
backings using gamelan samples recorded from the `Spirit of Hope'
gamelan instruments in Glasgow.

Peni Candra Rini wrote, performed and filmed a series of Javanese texts
based on the musical materials created, exploring themes of motherhood,
the sea, and ancient kingdoms, that themselves drew on the legend of St
Thenue, the `Mother of Glasgow'.

`Ibu Bhumi' means `Mother Earth' -- `Aku ibu, ib bhumi aku', `I am a
Mother, Mother Earth is me.'


\subsubsection{LiveCode.NYC Over the Years: A Community
Portrait}\label{livecode.nyc-over-the-years-a-community-portrait}

\textbf{\href{loveless-melody}{Melody~Loveless}}

\textbf{\href{https://youtu.be/g8_58v8zE9o}{Watch Video on YouTube}} -- \href{https://youtu.be/g8_58v8zE9o}{https://youtu.be/g8\_58v8zE9o}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-2}{\textbf{Community
  Report Session 2}\\
  Friday, April 21st, 11:15, \emph{VOGELFREI}}
\end{itemize}

\paragraph{Description}\label{description-6}

This piece was originally created as a generative site-specific
installation at the cell for a residency awarded to LiveCode.NYC by Flux
Factory, where the video was projection mapped onto panels built-into
the space. I use Max/MSP to mix and blend various images, videos, and
posters of LiveCode.NYC members and events to create a generative video
work. By showcasing past and current events and using materials created
by multiple members, this installation is a homage to the community
andhighlights its\textquotesingle{} collective efforts and visions. It
is a piece that I intend to work on and expand over the years. I am also
interested in exploring this framework for other communities.

\subsubsection{Live Rendering and -Coding Evolved
Sounds}\label{live-rendering-and--coding-evolved-sounds}

\textbf{\href{jonsson-bjorn-thor}{Björn~Þór~Jónsson}}

\textbf{\href{https://youtu.be/Ws_R-0TAD8M}{Watch Video on YouTube}} -- \href{https://youtu.be/Ws_R-0TAD8M}{https://youtu.be/Ws\_R-0TAD8M}

\paragraph{Description}\label{description-7}

synth.is offers sound discovery with evolutionary methods. Discovered
sound genomes can be published and rendered at any duration and pitch
for live coding with the integrated Glicol live coding engine. Steps
from live coding performances can be recorded and published at URLs
like: \url{https://synth.is/live-coding/01G9XMVDSCS65F52CY1X9GXQ6T}

When such an URL is visited, a single JSON file weighing a few kilobytes
is downloaded, containing genomes for all the sounds, which are rendered
in the browser before the performance, and a sequence of all the
recorded "live" coding steps, which are played back in the video.

\subsubsection{On a thin string (Live Coding with Lick the
Toad)}\label{on-a-thin-string-live-coding-with-lick-the-toad}

\textbf{\href{vasilakos-konstantinos}{Konstantinos~Vasilakos}}

\textbf{\href{https://youtu.be/SOuPIZl8DYc}{Watch Video on YouTube}} -- \href{https://youtu.be/SOuPIZl8DYc}{https://youtu.be/SOuPIZl8DYc}

\paragraph{Description}\label{description-8}

Lick the Toad is an online web application that was designed to enable
the collaborative participation of the audience during a live coding
performance. The system allows remote interaction using WebSocket
programming and real-time Open Sound Control communication between
users\textquotesingle{} web browsers and coder\textquotesingle s
personal choice of performance environment (e.g., SuperCollider, Pure
Data, MaxMSP). The system combines a user interface to train a machine
learning system and generates prediction data using a regression
algorithm apropos to the users\textquotesingle{} input. Once training is
done, the application switches to the prediction mode and offers the
visualization of OSC data, sonic events frequency information controlled
by a Markov chain module embedded in the system. This allows one a
hybrid exploration of the performance, affording one to turn the device
into a fully controllable autonomous instrument while at the same time
emitting data to any OSC client system in the network. In addition to
the sound generation, other higher musical characteristics are modulated
by the participants. That is, the tempo of the sequential repetition of
the sonic events is modulated by the number of participants. This
enables establishing an ongoing dialogue between audiences and
performers and influences the decisions of the coding process, affording
the audience to be at the forefront of the performance instead of
observing the live coding process passively while reciprocally
influencing one another.

\url{https://lick-the-toad.herokuapp.com/main/}

\subsubsection{on-the-fly Documentary}\label{on-the-fly-documentary}

\textbf{\href{bautista-rodriguez-lina}{Lina~Bautista~Rodríguez},
\href{noriega-alcaraz-felipe-ignacio}{Felipe~Ignacio~Noriega~Alcaraz},
\href{knotts-shelly}{Shelly~Knotts},
\href{jack-olivia}{Olivia~Jack},
\href{borgeat-patrick}{Patrick~Borgeat},
\href{paz-ivan}{Iván~Paz},
\href{frelih-luka}{Luka~Frelih},
\href{michelin-ludovica}{Ludovica~Michelin},
\href{hofmann-yannick}{Yannick~Hofmann},
\href{van-sluijs-fabian}{Fabian~van~Sluijs}}

\textbf{\href{https://youtu.be/sCkwUldKG50}{Watch Video on YouTube}} -- \href{https://youtu.be/sCkwUldKG50}{https://youtu.be/sCkwUldKG50}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-1}{\textbf{Community
  Report Session 1}\\
  Friday, April 21st, 10:00, \emph{VOGELFREI}}
\end{itemize}

\paragraph{Description}\label{description-9}

On-the-fly was a Creative Europe co-funded project initiated by Hangar
in Barcelona, in cooperation with Creative Coding Utrecht, Ljudmila Art
and Science Laboratory, Ljubljana, and ZKM \textbar{} Center for Art and
Media Karlsruhe. It was focused on supporting local practices and their
exchange among the live coding communities. It was designed with two
main branches: live coding performance and research. In the research
space we discussed, explored, identified, and imagined creative
directions in the live coding practice. On the performative side we
created spaces for live experimentation with new languages, techniques,
and approaches to live coding. We recognized that most of us have spent
extensive hours designing, understanding, or extending numerous
languages or libraries before performing with them. But also it is in
the live performance where the tools and designs are tested and
experimented. By creating these performative spaces across the four
partners in Europe, on-the-fly aimed to professionalize the creative
coding practice, while building new and stronger networks between the
practitioners and institutions interested or related to live coding.
This documentary was conceived to give a voice to the participants of
the on-the-fly project, both the live coders and the institutions. We
think that there is already enough content of live coding performances,
but that a documentary, produced by the community, where live coders
could explain those things that they consider essential in this
practice, was needed.


\subsubsection{\_\textbackslash\textbar/\_ TOPLAP
Karlsruhe}\label{toplap-karlsruhe}

\textbf{\href{weber-anselm}{Anselm~Weber},
\href{hopfner-daniel}{Daniel~Höpfner},
\href{schreiber-jakob}{Jakob~Schreiber},
\href{liu-jia}{Jia~Liu~(刘佳)},
\href{jaudzems-kaspars}{Kaspars~Jaudzems},
\href{samarotto-michele}{Michele~Samarotto},
\href{borgeat-patrick}{Patrick~Borgeat}}

\textbf{\href{https://youtu.be/ncRClTAEBO0}{Watch Video on YouTube}} -- \href{https://youtu.be/ncRClTAEBO0}{https://youtu.be/ncRClTAEBO0}

Was presented at:

\begin{itemize}
\tightlist
\item
  \href{/2023/catalogue/event/community-session-1}{\textbf{Community
  Report Session 1}\\
  Friday, April 21st, 10:00, \emph{VOGELFREI}}
\end{itemize}

\paragraph{Description}\label{description-10}

At the borders of the black forest, the city of Karlsruhe has curiously
been a fertile ground for live coding in the past years, benefiting from
the presence of such institutions as the ZKM (Center for Art and Media
Karlsruhe) and particularly the IMWI (Institute for Music Informatics
and Musicology, University of Music Karlsruhe), birthplace of the
notorious "Benoît and the Mandelbrots", host to the live.code.festival
in 2013 and up until today an international place of study and encounter
of many a fellow TOPLAPer.

Involvement in and awareness of academia, the experimental music scene
and contemporary club culture shapes the community\textquotesingle s
diversity, yielding abstract sonic finesse, dancefloor bangers, noise
pyrotechnics and more conceptual approaches in audiovisual media.

TOPLAP Karlsruhe wants to bundle local forces in live coding, create
spaces of open encounter and exchange, organize workshops, concerts and
connect with other live coding communities all around the globe.
