\subsubsection{Animatron Workshop: Live Coding Visual Poetry}\label{animatron-workshop-live-coding-visual-poetry}

\textbf{\href{pibernat-trias-roger}{Roger~Pibernat~Trias},
  \href{fraser-glen}{Glen~Fraser}}

Animatron is an experimental environment (very much ``work in
progress'') that enables creation of ``visual poetry'' in the form of
animations and images, created in real-time through live coding. It's
implemented using the open-source Godot engine, and communicates with
any ``client'' application or live coding language --- such as
SuperCollider --- via the network, using the Open Sound Control (OSC)
protocol and MIDI. In the workshop the participants will learn:\\

• how to install the software\\
• how to setup the system for playing both solo and collaboratively\\
• the basics of creating and controlling frame-by-frame animations via OSC\\
• how to create new image sequences\\
• how to define custom OSC message definitions\\
• how to set custom MIDI mappings to control the animations\\

No prior experience or software installation is
required, although proficiency in any live coding language that supports
OSC is welcome.

\subsubsection{Easy Stochastic Live Coding with Mégra
  3}\label{easy-stochastic-live-coding-with-muxe9gra-3}

\textbf{\href{champlin-alicia}{Alicia~Champlin},
  \href{reppel-niklas}{Niklas~Reppel}}

Mégra is a mini-language to make music with variable-order markov chains
and some other stochastic shenanigans. This workshop offers a hands-on
tutorial in applying the basics of Mégra 3, with time for exploration
and free play.

Any skill level. Windows/MacOS/Linux. Participants should bring laptops,
headphones, and optionally a small microphone.


\subsubsection{Expressing Oneself with Code and World
  Building}\label{expressing-oneself-with-code-and-world-building}

\textbf{\href{oduro-kofi}{Kofi~Oduro~(illestpreacha)}}

In this workshop, participants will see how coding can be used in
musical, performative and literary arts, by using tools such as
livecoding Youtube, Hydra, Inverse.website and Sonic Pi to name a few.
They will see how expressive and creative code will be with the benefit
of seeing how it can be use in a collaborative setting. Participants
will see how improvised writing and coding can lead to various outcomes,
musically, as well as how to use network elements to your advantage when
writing or producing work.


\subsubsection{Introduction to Nix for Live Coding Software
  Packaging}\label{introduction-to-nix-for-live-coding-software-packaging}

\textbf{\href{sanchez-medina-alejandro}{Alejandro~Sánchez~Medina}}

This workshop will provide a guided introduction to Nix
(https://nixos.org/), a functional package manager for declarative
configuration of general software dependencies. The workshop will
consist of:

\begin{itemize}
  \tightlist
\item
  An introduction to the principles of declarative software dependency
  management.
\item
  A guided tutorial to the Nix language.
\item
  A presentation of common packaging examples and patterns.
\item
  On-site tutoring packaging the live-coding software chosen by the
  participant.
\end{itemize}

Requirements for participation: bring your personal laptop to work
during the practical part of the workshop. Windows users are encouraged
to come with a Linux Virtual Machine. Nix can work from within the
Windows Subsystem for Linux, albeit with some limitations compared to
native *nix systems.

It is highly recommended that participants come with their own project
to package, or a project they already want to use but could not manage
to make it work in a specific setup.


\subsubsection{Live Cinema Coding with Tidal Cycles, Processing and Unreal
  Engine}\label{live-cinema-coding-with-tidal-cycles-processing-and-unreal-engine}

\textbf{\href{abreu-ivan}{Iván~Abreu},
  \href{cortes-malitzin}{Malitzin~Cortés~(CNDSD)}}

We define Live Cinema Coding as a performative practice (heir to Live
cinema) that uses live coding to sequence cinematographic shots,
transform a 3D scene, animate actors, control light, process videos,
etc. We use the pattern strength of Tidal to create sound-visual
synesthesia and sound visualization by refactoring musical patterns into
visual patterns.

The objective of the workshop is to show the authors\textquotesingle{}
workflow, both conceptual and technical: the choice of "what" patterns
to refactor and "how" from listening to our own musical composition. Or
the process of abstracting into custom haskell functions within Tidal
Cycles and converting them to OSC addresses for redirection and flexible
visual consequence in Processing, Unreal Engine or DMX stage lighting.

For the workshop it is necessary to have Tidal Cycles (supercollider),
Processing and Unreal Engine already installed and the student will be
explained the resources that will be available on GitHub.

\href{https://tidalcycles.org/}{Tidal Cycles}

\href{https://processing.org/download}{Processing}

\href{https://www.unrealengine.com/en-US/download}{Unreal Engine}


\subsubsection{Live Coding Latin Dance Music With
  Seis8s}\label{live-coding-latin-dance-music-with-seis8s}

\textbf{\href{n-del-angel-luis}{Luis~N.~Del~Angel},
  \href{mugica-julia}{Julia~Múgica}}

Seis8s is a web-based live coding language that allows real-time
interaction with digital audio and localized music knowledge. Seis8s
revolves around Spanish-language commands that relate to Latin dance
music. During this 4-hour introductory workshop, participants will
access Seis8s at https://seis8s.org/ to learn its basic functions as
well as its context and motivation.

Through this learning process, participants will also engage in
mainstream music styles from Latin America such as Mexican Cumbia and
Cuban Guaguancó. Participants will also learn about instruments commonly
used in this music such as keyboards, bass guitars, congas, claves, and
shakers.

Luis, the instructor, will be present during the workshop
\textbf{\emph{digitally}}, while we have a local instructor, Julia,
present to guide you.


\subsubsection{LiveLily Workshop}\label{livelily-workshop}

\textbf{\href{drymonitis-alexandros}{Drymonitis~Alexandros}}

LiveLily is a workshop on the software with the same name. This is a
Live Sequencing and Live Scoring software through live coding with a
subset of the Lilypond language. Lilypond is a language for sheet music
engraving. With LiveLily the user can create music scores in real time,
and a sequencer based on these score.

The LiveLily sequencer can be as expressive as a Western notation music
score can, capable of transferring dynamics, articulation and arbitrary
information to the instruments it controls. Being a hybrid system,
combining Live Scoring and Live Sequencing, LiveLily can be used for
both Live Scoring with acoustic instruments, and Live Sequencing
electronic music, or even a combination of these two.


\subsubsection{Nodysseus.THREE: Live Lowcoding THREE.js Visuals in the
  Browser}\label{nodysseus.three-live-lowcoding-three.js-visuals-in-the-browser}

\textbf{\href{popple-ulysses}{Ulysses~Popple}}

Using Nodysseus, a node-editor for the browser, we\textquotesingle ll
explore creating and using reusable node networks with 3D objects. This
is a hands on tutorial quite literally - participants can use their
touch device of choice or their laptops, it works well on both. By the
end of the workshop, participants will be more comfortable thinking in
node networks and have a spiffy live(low)code party trick they can
revisit at any time.


\subsubsection{P5LIVE: A p5.js Collaborative Live Coding VJ
  Environment}\label{p5live-a-p5.js-collaborative-live-coding-vj-environment}

\textbf{\href{davis-ted}{Ted~Davis}}

This workshop will introduce participants to P5LIVE, a collaborative
live-coding vj environment for p5.js. Hosted by the
tool\textquotesingle s creator, we\textquotesingle ll walk through the
many features geared for both live-coding performance, remote
collaboration, and how it can be useful in a teaching environment.


\subsubsection{Scorch: A New Programming Language For
  Music}\label{scorch-a-new-programming-language-for-music}

\textbf{\href{lorway-norah}{Norah~Lorway},
  \href{powley-edward}{Edward~Powley},
  \href{wilson-arthur}{Arthur~Wilson}}

Scorch is a new domain specific music programming language designed by
Norah Lorway, Edward Powley and Arthur Wilson with the intention of
being an accessible entry point for those not experienced in traditional
programming languages (Lorway et al 2022). Initially used for
algorithmic composition as a MIDI generating VST plugin, Scorch is also
being used for live coding and a variety of media computing
applications.

Scorch incorporates various AI implementations meant to assist users
with various musical and computing tasks. Amongst these include an AI
collaborator called Autopia (Lorway et al 2021) which allows for
collaboration with AI and human performers in live coding contexts.
Autopia was designed by the present authors to explore the three-way
interaction between AI, human performer and audience --- the AI uses an
evolutionary algorithm seeded with human-written code and guided by live
audience feedback. Originally developed for use with SuperCollider, this
workshop will be the debut of the version of Autopia developed for use
with Scorch.

\subsubsection{The Craft of (Algorave)
  Documentation}\label{the-craft-of-algorave-documentation}

\textbf{\href{gorelick-dan}{Dan~Gorelick~(dan.dog)}}

On top of all of the chaos that goes into organizing a show, the
logistics involved in documenting can feel like an expendable effort.
However, time and time again I thank myself and my co-organizers for
investing the energy in documenting.

Having good documentation means the performers have quality assets for
their portfolios. It means we have promotion assets for the next shows.
It means we can apply for grants for future shows. It means we can tell
the story for future audiences.

Documentation is a life-long practice. It can breathe new life into the
work. When it is treated like a craft more than an afterthought, so much
can be possible.

The workshop is a theoretical and practical session on the craft of
documenting art, specifically through the lens of live-code
performances.

\subsubsection{Visualists Meetup}\label{visualists-meetup}

\textbf{\href{groff-hennigh-palermo-sarah}{Sarah~Groff~Hennigh-Palermo},
  \href{jack-olivia}{Olivia~Jack},
  \href{john-guy}{Guy~John},
  \href{roberts-antonio}{Antonio~Roberts}}

Are you the person at the alogorave asking for the HDMI cable? (Do you
secretly have a 10m one in your bag already?) Are you sick of everyone
talking about sounds when you want to be talking about throwing shapes?
Meet up with other visualists and share your questions, suggestions,
works, and make new friends. Maybe commiserate a little. This workshop
will be led by four visualists and tool-makers --- Antonio Roberts, Guy
John, Olivia Jack, and Sarah Groff Hennigh-Palermo --- but its format
will be determined by the needs of the attendees. It might take the form
of an open projector, informal group discussion, breakout groups, or
some other improvisation.
